### 2017-01-12 doc/paper/cogsci_template.tex
Start writing paper.

% 
% Annual Cognitive Science Conference
% Sample LaTeX Paper -- Proceedings Format
%

% Original : Ashwin Ram (ashwin@cc.gatech.edu)       04/01/1994
% Modified : Johanna Moore (jmoore@cs.pitt.edu)      03/17/1995
% Modified : David Noelle (noelle@ucsd.edu)          03/15/1996
% Modified : Pat Langley (langley@cs.stanford.edu)   01/26/1997
% Latex2e corrections by Ramin Charles Nakisa        01/28/1997 
% Modified : Tina Eliassi-Rad (eliassi@cs.wisc.edu)  01/31/1998
% Modified : Trisha Yannuzzi (trisha@ircs.upenn.edu) 12/28/1999 (in process)
% Modified : Mary Ellen Foster (M.E.Foster@ed.ac.uk) 12/11/2000
% Modified : Ken Forbus                              01/23/2004
% Modified : Eli M. Silk (esilk@pitt.edu)            05/24/2005
% Modified : Niels Taatgen (taatgen@cmu.edu)         10/24/2006
% Modified : David Noelle (dnoelle@ucmerced.edu)     11/19/2014

%% Change "letterpaper" in the following line to "a4paper" if you must.

\documentclass[10pt,letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}

\title{How to Make a Proceedings Paper Submission}

\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\
  Department of Psychology, 1202 W. Johnson Street \\
  Madison, WI 53706 USA
  \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\
  Department of Educational Psychology, 1025 W. Johnson Street \\
  Madison, WI 53706 USA}

\begin{document}

\maketitle

\begin{abstract}
The abstract should be one paragraph, indented 1/8~inch on both sides,
in 9~point font with single spacing. The heading ``{\bf Abstract}''
should be 10~point, bold, centered, with one line of space below
it. This one-paragraph abstract section is required only for standard
six page proceedings papers. Following the abstract should be a blank
line, followed by the header ``{\bf Keywords:}'' and a list of
descriptive keywords separated by semicolons, all in 9~point font, as
shown below.

\textbf{Keywords:} 
add your choice of indexing terms or keywords; kindly use a
semicolon; between each term
\end{abstract}

\section{General Formatting Instructions}

The entire contribution of a proceedings paper (including figures,
references, and anything else) can be no longer than six pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
  U.S. letter or A4 paper, so you must be sure to measure the width of
  the printed text.} Use 10~point Times Roman with 12~point vertical
spacing, unless otherwise specified.

The title should be in 14~point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11~point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10~point type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

\section{First Level Headings}

First level headings should be in 12~point, initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

\subsection{Second Level Headings}

Second level headings should be 11~point, initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~line
space below the heading.

\subsubsection{Third Level Headings}

Third level headings should be 10~point, initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

\section{Formalities, Footnotes, and Floats}

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
\citeA{NewellSimon1972a}, but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
\cite{NewellSimon1972a}. List multiple references alphabetically and
separate them by semicolons
\cite{ChalnickBillman1988a,NewellSimon1972a}. Use the
``et~al.'' construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9~point type at the
bottom of the column on which they appear. Precede the footnote block
with a horizontal rule.\footnote{Sample of the second footnote.}

\subsection{Tables}

Number tables consecutively. Place the table number and title (in
10~point) above the table with one line space above the caption and
one line space below it, as in Table~\ref{sample-table}. You may float
tables to the top or bottom of a column, or set wide tables across
both columns.

\begin{table}[!ht]
\begin{center} 
\caption{Sample table title.} 
\label{sample-table} 
\vskip 0.12in
\begin{tabular}{ll} 
\hline
Error type    &  Example \\
\hline
Take smaller        &   63 - 44 = 21 \\
Always borrow~~~~   &   96 - 42 = 34 \\
0 - N = N           &   70 - 47 = 37 \\
0 - N = 0           &   70 - 47 = 30 \\
\hline
\end{tabular} 
\end{center} 
\end{table}

\subsection{Figures}

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10~point, after the figure with one line space
above the caption and one line space below it, as in
Figure~\ref{sample-figure}. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

\begin{figure}[ht]
\begin{center}
\fbox{CoGNiTiVe ScIeNcE}
\end{center}
\caption{This is a figure.} 
\label{sample-figure}
\end{figure}

\section{Acknowledgments}

Place acknowledgments (including funding information) in a section at
the end of the paper.

\section{References Instructions}

Follow the APA Publication Manual for citation format, both within the
text and in the reference list, with the following exceptions: (a) do
not cite the page numbers of any book, including chapters in edited
volumes; (b) use the same format for unpublished references as for
published ones. Alphabetize references by the surnames of the authors,
with single author entries preceding multiple author entries. Order
references by the same authors by the year of publication, with the
earliest first.

Use a first level section heading, ``{\bf References}'', as shown
below. Use a hanging indent style, with the first line of the
reference flush against the left margin and subsequent lines indented
by 1/8~inch. Below are example references for a conference paper, book
chapter, journal article, dissertation, book, technical report, and
edited volume, respectively.

\nocite{ChalnickBillman1988a}
\nocite{Feigenbaum1963a}
\nocite{Hill1983a}
\nocite{OhlssonLangley1985a}
% \nocite{Lewis1978a}
\nocite{Matlock2001}
\nocite{NewellSimon1972a}
\nocite{ShragerLangley1990a}

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{CogSci_Template}

\end{document}

### 2017-01-12 doc/paper/paper.tex
Start writing paper.

--- 2017-01-12 doc/paper/cogsci_template.tex
@@
 
-\title{How to Make a Proceedings Paper Submission}
+\title{TODO title}
 
-\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\
-  Department of Psychology, 1202 W. Johnson Street \\
-  Madison, WI 53706 USA
-  \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\
-  Department of Educational Psychology, 1025 W. Johnson Street \\
-  Madison, WI 53706 USA}
+\author{{\large \bf Jan Gosmann (jgosmann@uwaterloo.ca)} \\
+  %Department of Psychology, 1202 W. Johnson Street \\
+  %Madison, WI 53706 USA
+  \AND{\large \bf Aaron Voelker (TODO)} \\
+  \AND{\large \bf Chris Eliasmith (TODO)}
+  %Department of Educational Psychology, 1025 W. Johnson Street \\
+  %Madison, WI 53706 USA}
+  }
 
@@
 
-\section{General Formatting Instructions}
+\section{Introduction}
+Winner-take-all (WTA) mechanisms are often employed in cognitive models. For 
+example, TODO O'Reilly, Nengo cleanup, TCM\@. A WTA mechanism receives 
+a $d$-dimensional input of utility values for $d$ different choices. The output 
+is supposed to be larger than zero for the dimension with highest utility and 
+zero for all other inputs.
 
-The entire contribution of a proceedings paper (including figures,
-references, and anything else) can be no longer than six pages.
+A large body of literature exists examining how well different WTA mechanisms 
+can fit different data from decision experiments (TODO references). Here, 
+however, we will investigate the suitability of two different WTA mechanisms in 
+the context of large-scale cognitive modelling with spiking neurons on a set of 
+benchmarks that are more normative in nature.  The first mechanism is an 
+implementation of the classic Usher-McClelland (TODO ref) leaky, competing 
+accumulator model.  It has been widely used, for example in versions of the TCM 
+model (TODO ref), and TODO some of our models. We will compare this to an 
+independent accumulator model with a second thresholding layer with recurrent 
+connections to the first layer. In both cases we are especially interested in 
+situations with more than two ($d > 2$) choices.
 
-The text of the paper should be formatted in two columns with an
-overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
-cm), with 0.25 inches between the columns. Leave two line spaces
-between the last author listed and the text of the paper. The left
-margin should be 0.75 inches and the top margin should be 1 inch.
-\textbf{The right and bottom margins will depend on whether you use
-  U.S. letter or A4 paper, so you must be sure to measure the width of
-  the printed text.} Use 10~point Times Roman with 12~point vertical
-spacing, unless otherwise specified.
+For the implementation of these models we use the Neural Engineering Framework 
+(NEF) which allows us to directly implement the prescribed dynamics with spiking 
+neurons. The NEF has been used in a wide range of models TODO, including the 
+largest functional brain model Spaun (TODO ref). We will give a short 
+introduction to the NEF first, then describe the implementation of the two WTA 
+mechanisms. In section TODO, we give the results on a number of metrics, 
+followed by a discussion in section TODO\@.
 
-The title should be in 14~point, bold, and centered. The title should
-be formatted with initial caps (the first letter of content words
-capitalized and the rest lower case). Each author's name should appear
-on a separate line, 11~point bold, and centered, with the author's
-email address in parentheses. Under each author's name list the
-author's affiliation and postal address in ordinary 10~point type.
+\section{Methods}
 
-Indent the first line of each paragraph by 1/8~inch (except for the
-first paragraph of a new section). Do not add extra vertical space
-between paragraphs.
+\subsection{The Neural Engineering Framework}
 
-\section{First Level Headings}
+\subsection{Leaky, competing accumulator model}
 
-First level headings should be in 12~point, initial caps, bold and
-centered. Leave one line space above the heading and 1/4~line space
-below the heading.
+\subsection{Independent accumulator model}
 
-\subsection{Second Level Headings}
-
-Second level headings should be 11~point, initial caps, bold, and
-flush left. Leave one line space above the heading and 1/4~line
-space below the heading.
-
-\subsubsection{Third Level Headings}
-
-Third level headings should be 10~point, initial caps, bold, and flush
-left. Leave one line space above the heading, but no space after the
-heading.
-
-\section{Formalities, Footnotes, and Floats}
-
-Use standard APA citation format. Citations within the text should
-include the author's last name and year. If the authors' names are
-included in the sentence, place only the year in parentheses, as in
-\citeA{NewellSimon1972a}, but otherwise place the entire reference in
-parentheses with the authors and year separated by a comma
-\cite{NewellSimon1972a}. List multiple references alphabetically and
-separate them by semicolons
-\cite{ChalnickBillman1988a,NewellSimon1972a}. Use the
-``et~al.'' construction only after listing all the authors to a
-publication in an earlier reference and for citations with four or
-more authors.
-
-\subsection{Footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. Place the footnotes in 9~point type at the
-bottom of the column on which they appear. Precede the footnote block
-with a horizontal rule.\footnote{Sample of the second footnote.}
-
-\subsection{Tables}
-
-Number tables consecutively. Place the table number and title (in
-10~point) above the table with one line space above the caption and
-one line space below it, as in Table~\ref{sample-table}. You may float
-tables to the top or bottom of a column, or set wide tables across
-both columns.
-
-\begin{table}[!ht]
-\begin{center} 
-\caption{Sample table title.} 
-\label{sample-table} 
-\vskip 0.12in
-\begin{tabular}{ll} 
-\hline
-Error type    &  Example \\
-\hline
-Take smaller        &   63 - 44 = 21 \\
-Always borrow~~~~   &   96 - 42 = 34 \\
-0 - N = N           &   70 - 47 = 37 \\
-0 - N = 0           &   70 - 47 = 30 \\
-\hline
-\end{tabular} 
-\end{center} 
-\end{table}
-
-\subsection{Figures}
-
-All artwork must be very dark for purposes of reproduction and should
-not be hand drawn. Number figures sequentially, placing the figure
-number and caption, in 10~point, after the figure with one line space
-above the caption and one line space below it, as in
-Figure~\ref{sample-figure}. If necessary, leave extra white space at
-the bottom of the page to avoid splitting the figure and figure
-caption. You may float figures to the top or bottom of a column, or
-set wide figures across both columns.
-
-\begin{figure}[ht]
-\begin{center}
-\fbox{CoGNiTiVe ScIeNcE}
-\end{center}
-\caption{This is a figure.} 
-\label{sample-figure}
-\end{figure}
+* ever increasing evidence
 

### 2017-01-12 doc/paper/paper.tex
Drafting methods section.

@@
 \usepackage{cogsci}
+\usepackage{commath}
 \usepackage{pslatex}
@@
 \subsection{The Neural Engineering Framework}
+We employ the Neural Engineering Framework (NEF, TODO cite) which allows us to 
+implement mathematical model descriptions in spiking neural networks based on 
+three principles: \emph{representation}, \emph{transformation}, and 
+\emph{dynamics}.
+
+\subsubsection{Principle 1: Representation}
+The representation of a value $x(t)$ with a population of spiking neurons is 
+defined by the encoding and decoding. The encoding converting the value $x$ into 
+a spike train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
+\begin{equation}
+    a_i(t) = G_i\left[\alpha_i x(t) + J_i^{\mathrm{bias}}\right]
+\end{equation}
+where $\alpha_i$ is a gain factor, $J_i^{mathrm{bias}}$ a bias current and $G_i$ 
+is the neuron linearity. Here, we use spiking leaky integrate-and-fire neurons 
+for $G_i$.
+
+Decoding weights $d_i$ are used to decode a value $\hat x(t)$ from such 
+a population of neurons with
+\begin{equation}
+    \hat x(t) = \sum_i d_i \left[a_i(t) * h(t)\right]
+\end{equation}
+where $h(t) = \tau^{-1}\exp(1/\tau)$ is the synaptic filter. The decoding 
+weights are obtained with a least-squares optimization of the error $E^x 
+= \abs{x - \hat x}$.
+
+For the transmission of a value from one population to another, the connection 
+weights are given by
+\begin{equation}
+    W_{ij} = \alpha_j d_i \text{.}
+\end{equation}
+
+\subsubsection{Principle 2: Transformation}
+By finding alternate decoding weights $d^f_i$ with the error given by $E^{f(x)} 
+= \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be 
+approximated in the connections between neural populations.
+
+\subsubsection{Principle 3: Dynamics}
+TODO
 
 \subsection{Leaky, competing accumulator model}
+We implement the widely used, leaky, competing accumulator model proposed by 
+TODO\@. The dynamics for the state variables $x_i, i < N$, where $N$ is the 
+number of choices, are given by
+\begin{equation}\label{eqn:usher-mcclelland}
+    \begin{split}
+    dx_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
+    \frac{dt}{\tau'} \\
+    x_i &\rightarrow \max(x_i, 0)
+    \end{split}
+\end{equation}
+where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
+inhibition, and $tau'$ the time constant. Note that one usually wants to set $k 
+= \beta$ because TODO\@. Here, we chose $k = \beta = 1$. TODO what does changing 
+this control? Why can we fix it at 1?
+
+Equation~\ref{eqn:usher-mcclelland} can easily be implemented with the NEF by 
+using one population of neurons for each $x_i$.  We believe this implementation 
+to be novel as it it does not treat the $x_i$ as neural firing rates, rather the 
+neural firing rates are weighted by the decoding weights to precisely implement 
+the stated dynamics. As such the model equations do not impose restrictions on 
+the neuron model or requires to lump the neurons into a single population firing 
+rate. This allows us to use biologically more realistic neurons while at the 
+same time adhering to the dynamics prescribed by the model.
+
+TODO figure with dynamics
 
 \subsection{Independent accumulator model}
+The other Winner-take-all mechanism is related to the Usher-McClelland model and 
+even more closely to independent accumulator models (TODO refs), but has some 
+fine and important distinctions. It consists of two layers of neural 
+populations. The first layer are independent accumulators obtained from 
+Equation~\ref{eqn:usher-mcclelland} by setting $k = \beta = 0$ resulting in
+\begin{equation}
+    \begin{split}
+    dx^1_i &= \lambda \rho_i \frac{dt}{\tau} \\
+    x^1_i &\rightarrow \max(x^1_i, 0) \text{.}
+    \end{split}
+\end{equation}
+The parameter $\lambda$ scales this input and is introduced because it is more 
+convenient to manipulate than then the threshold parameter $\vartheta$ 
+introduced below.
 
+The second layer consists of independent non-recurrent populations that get 
+input from the first layer in a one to one projection. We decode the shifted 
+Heaviside function $\Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ 
+is a threshold value controlling how much evidence needs to be accumulated to 
+produce an output. Instead of controlling this threshold, it is more convenient 
+to scale the input with $\lambda$ in the context of the NEF, though 
+mathematically both approaches are equivalent. As the Usher-McClelland does not 
+have a threshold parameter, we do not introduce the input scaling $\lambda$ in 
+that model.
+
+The Heaviside decoded output of layer 2 projects back to layer 1 to add $x^2_i 
+- 2\sum_{j \neq i} x^2_j$ to the input of $x^1_i$. As effect the choice will be 
+stabilized while all other state variables will be suppressed once one of the 
+accumulators reaches the threshold $\vartheta$.
+
+TODO figure with dynamics
+
+\section{Results}
+
+\section{Discussion}
 * ever increasing evidence

### 2017-01-13 doc/paper/paper.tex
Finish rough draft of the paper.

@@
 \section{Results}
+To test and compare the two WTA mechanisms we provide an input of $\rho_i 
+= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
+$s$ the separation to all other inputs, $\delta$ the Kronecker delta, and 
+$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
+loss of generality, the first state variable receives the strongest input and 
+all other state variables receive input that is $s$ less. We chose this input as 
+it it represents the worse case for picking out the strongest input as $s 
+\rightarrow 0$ and as one input $\rho_i \rightarrow 0$ it will have less 
+influence on the overall dynamics of the two WTA mechanisms.
+
+To evaluate the two mechanisms we use a number of metrics. First we determine 
+whether the model is able to form a clear decision at all within a second of 
+simulated time. To count as a clear decision at least one output needs to stay 
+above 0.2 for a second after the initial second of simulation time. This ensures 
+that the output is different from a 0 output which could slightly be above 
+0 due to noise. Furthermore, we require that the largest output will be the 
+  largest output for all of that second of simulation time because otherwise the 
+  decision would switch.
+
+This does not take into account whether the winning output actually corresponds 
+to the strongest input, but sometimes it can be more desirable to form a clear 
+decision at all than finding the actual strongest input. In other situations, 
+though, the correctness of the decision might be important. So this is our next 
+metric. A trial is considered correct if the model forms a clear decision and 
+the largest output corresponds to the largest input.
+
+The time it takes to form a decision can be relevant too. We define the decision 
+time as how long it takes to fulfill the conditions of a clear decision.
+
+These metrics cover the basic performance of the WTA mechanims. When using a WTA 
+mechanism within larger cognitive models, the exact magnitude of the outputs can 
+be important. Ideally, the output would be 1 for the winner and 0 for all other 
+outputs.\footnote{Technically, the winner output could be scaled to any 
+    magnitude. We use 1 here as it is most convenient to work with.} We define 
+the \emph{winner error} $E_1$ as the difference of the winner output from 1 and 
+the \emph{runner-up error} $E_2$ as the difference of second largest output from 
+0 (negative values treated as 0). We use the average output values of the second 
+  second in the simulation as the value can fluctuate over time.
+
+These two metrics only look at the final output, but the model can produce 
+transient outputs before the final decision is achieved. Within the context of 
+a larger model, this can be a problem as the transient output could already be 
+interpreted as a decision. Thus, we define $E_{2,\max}$ as the highest output of 
+a non-winning output during the whole simulation.
+
+We find that the ability to reach a clear decision depends on the magnitude of 
+the highest input for both networks. This is not surprising. In the 
+Usher-McClelland the output magnitude will be determined by the input magnitude 
+of the largest input. As such the largest input needs to be above 0.2 to fulfill 
+the requirements. For the independent accumulator model the input has to be 
+large enough to reach the integration threshold within the time limit. By 
+increasing the input scaling $\lambda$ or the time limit one could get a clear 
+decision for smaller inputs within the time limit. We further find that the 
+independent accumulator model is independent of the input noise and target 
+separation for all tested parameters. This is not the case for the 
+Usher-McClelland model as shown in Figure~TODO where the fraction of trials 
+without a clear decision increases with noise and smaller target separation.
+
+However, when considering the correctness of the decisions (Figure~TODO) the 
+Usher-McClelland model is doing better. We can alleviate that difference to some 
+degree by reducing the input scaling to $\lambda = TODO$, but perform still 
+worse for small target separations when staying in the time limit.
+
+The time required to reach a decision in the Usher-McClelland model depend 
+mostly on the target separation and amount of noise on the input (Figure~TODO), 
+the magnitude of the largest input is of minor influence. In contrast to that, 
+in the independent accumulator model the scaled magnitude of the largest input 
+is the most important factor. Depending on this magnitude the network can either 
+be faster or slower than the Usher-McClelland network, but it will need more 
+time to achieve the same corectness of responses. There is also a slight 
+influence of target separation and input noise with an interaction of these two 
+parameters (Figure~TODO).
+
+The output of the independent accumulator model matches almost perfectly the 
+specifications. This is not the case for the Usher-McClelland model 
+(Figure~TODO).  For small target separations the output of the winner will stay 
+below 1 and this will get worse with increased noise. As the winner output will 
+try to match the largest input TODO explanation. Furthermore, the 
+Usher-McClelland model will have residual outputs of non-winning choices under 
+noisy conditions and with small target separations.
+
+Finally, looking at the transient responses both models might produce outputs of 
+non-winning choices. For the Usher-McClelland model these increase with noise on 
+the input and, for small target separation, can approach the final output of the 
+winning dimensions. For the independent accumulator model, transient output are 
+smaller in noisy conditions, but can be higher than for the Usher-McClelland 
+model in less noisy conditions. The magnitude of such transient responses is 
+reduced by decreasing the input scaling.
 
 \section{Discussion}
-* ever increasing evidence
+We do not find either one of the networks to perform better on all metrics, but 
+rather they excel at slightly different things. The Usher-McClelland network is 
+better suited to quickly determine the correct winner. However, under noisy 
+conditions it can end up not producing a clear output at all and basically not 
+making a decision at all. The independent accumulator model might not be as 
+quick or find the correct winner as often, but given enough time it will 
+eventually arrive at a decision and produce a clear output.
+
+The Usher-McClelland network is especially suited for situations where 
+a decision needs to be continuously adjusted. The prescribed dynamics 
+essentially try to output what the currently largest input is considering some 
+smoothing over time. This makes it quick to respond to changes of the input, but 
+can also lead randomly switching outputs due to noise. In comparison, the 
+independent accumulator model is more suited in situations where a discrete 
+sequence of decisions is required. During the initial phase the model will just 
+integrate evidence without any output and after making a decision, it is 
+necessary to reset the model by inhibiting all layer 1 neurons. This limits the 
+how quickly successive decisions can be made, but at the same time once 
+a decision is made the network provides a stable output.
+
+There are also certain considerations to be made when integrating these networks 
+in larger neural or cognitive models. This integration is easy for the 
+independent accumulator model as it provides a clear output. The output of the 
+winning choice is also close to one which makes it easy to detect when the 
+decision has been made and processing can continue. This is problematic in the 
+Usher-McClelland model where we get a fluctuating output before the final 
+decision and as this output can get close to the final output we cannot 
+necessarily use the crossing of a threshold. Moreover, the magnitude of the 
+final output depends on the magnitude of the input which is also a problem for 
+using a fixed threshold.
+
+Part of the reason why the independent accumulator model produces less correct 
+responses is a systematic bias introduced in the second layer. Usually the 
+neural properties are selected randomly in the NEF and this will result in 
+slightly different thresholds for each of the populations before it will fire.  
+It is possible to select the neural parameters in a way that all of these 
+populations will have the same threshold which improves the correctness 
+(Figure~TODO). However, this would require a very precise tuning of the neurons 
+that might not be biologically plausible.
+
+One critique of non-leaky accumulator models is that their ability to 
+discriminate the largest input increases indefinitely with time (TODO~ref) and 
+that there is no sensible stopping criterion. However, this assumes that the 
+time to reach a decision has no cost. If that time has a cost, the cost of 
+spending more time on the decision will at some point exceed the gain by making 
+a correct decision. Furthermore, this argument assumes integration with perfect 
+accuracy. But in a neural network resources are limited, as such the range and 
+accuracy of values that can be represented in a neural population is limited.  
+At some point this would counterbalance any additional evidence.
+
+We did not investigate the biological plausibility here because there is 
+evidence to be found for both networks (TODO references). Also, the 
+implementation is spiking neurons ensures a certain level of biological 
+plausibility.
+
+TODO\@: distribution of neurons in network, looking only at cases where 
+a decision could be made within the results.
 

### 2017-01-13 doc/paper/paper.tex
Start creating figures.

@@
 \usepackage{commath}
+\usepackage{graphicx}
 \usepackage{pslatex}
@@
 TODO figure with dynamics
+\begin{figure}
+    \centering
+    \includegraphics{figures/usher-mcclelland}
+    \caption{TODO}\label{fig:usher-mcclelland}
+\end{figure}
 
@@
 TODO figure with dynamics
+\begin{figure}
+    \centering
+    \includegraphics{figures/indacc}
+    \caption{TODO}\label{fig:indacc}
+\end{figure}
 
@@
 without a clear decision increases with noise and smaller target separation.
+\begin{figure}
+    \centering
+    \includegraphics{figures/decisions}
+    \caption{TODO}\label{fig:decisions}
+\end{figure}
 
@@
 worse for small target separations when staying in the time limit.
+\begin{figure*}
+    \centering
+    \includegraphics{figures/correct}
+    \caption{TODO}\label{fig:correct}
+\end{figure*}
 
@@
 TODO\@: distribution of neurons in network, looking only at cases where 
-a decision could be made within the results.
+a decision could be made within the results, what about more choices, include 
+a number of parameters and github url.
 

### 2017-01-13 cogsci17_decide/networks.py

@@ -66,6 +66,7 @@ def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
             eval_points=nengo.dists.Uniform(0., 1.),
             intercepts=nengo.dists.Uniform(0., 1.),
             encoders=nengo.dists.Choice([[1.]]))
+        net.x = x
         nengo.Connection(x.output, x.input, transform=(A - a * I) / (1. - a),
                          synapse=tau_actual)
 

### 2017-01-13 cogsci17_decide/trial.py
Adjust metrics.

@@ -11,7 +11,7 @@ class DecisionTrial(pytry.NengoTrial):
         self.param("# choices", d=10)
         self.param("# neurons per choice", N=200)
 
-        self.param("input baseline", baseline=0.1)
+        self.param("input baseline", baseline=0.3)
         self.param("target separation", target_sep=0.2)
         self.param("noise std", noise=0.)
         self.param("input scaling", scale=1.)
@@ -27,7 +27,7 @@ class DecisionTrial(pytry.NengoTrial):
             decide = getattr(cogsci17_decide.networks, p.network)(**net_args)
 
             stimulus = p.baseline * np.ones(p.d)
-            stimulus[0] += p.target_sep
+            stimulus[1:] -= p.target_sep
             stimulus_node = nengo.Node(stimulus)
             nengo.Connection(stimulus_node, decide.input, synapse=None,
                              transform=p.scale)
@@ -66,7 +66,7 @@ class DecisionTrial(pytry.NengoTrial):
         t = np.nan
         if decided:
             risen = np.flatnonzero(
-                sim.data[self.probe][:, winner] > .2)
+                sim.data[self.probe][:, winner] > .15)
             if len(risen) > 0:
                 fall = np.flatnonzero(
                     sim.data[self.probe][:, winner] -

### 2017-01-13 doc/paper/paper.tex
Minor fixes in paper.

@@
 simulated time. To count as a clear decision at least one output needs to stay 
-above 0.2 for a second after the initial second of simulation time. This ensures 
-that the output is different from a 0 output which could slightly be above 
+above 0.15 for a second after the initial second of simulation time. This 
+ensures that the output is different from a 0 output which could slightly be 
+above 
 0 due to noise. Furthermore, we require that the largest output will be the 
@@
 be faster or slower than the Usher-McClelland network, but it will need more 
-time to achieve the same corectness of responses. There is also a slight 
+time to achieve the same correctness of responses. There is also a slight 
 influence of target separation and input noise with an interaction of these two 

### 2017-01-16 doc/paper/paper.tex
Add references.

@@
 \section{Introduction}
-Winner-take-all (WTA) mechanisms are often employed in cognitive models. For 
-example, TODO O'Reilly, Nengo cleanup, TCM\@. A WTA mechanism receives 
-a $d$-dimensional input of utility values for $d$ different choices. The output 
-is supposed to be larger than zero for the dimension with highest utility and 
-zero for all other inputs.
+Winner-take-all (WTA) mechanisms are often employed in cognitive 
+models~\cite<e.g.,>{oreilly1998}.  A WTA mechanism receives a $d$-dimensional 
+input of utility values for $d$ different choices. The output is supposed to be 
+larger than zero for the dimension with highest utility and zero for all other 
+inputs.
 
-A large body of literature exists examining how well different WTA mechanisms 
-can fit different data from decision experiments (TODO references). Here, 
-however, we will investigate the suitability of two different WTA mechanisms in 
-the context of large-scale cognitive modelling with spiking neurons on a set of 
-benchmarks that are more normative in nature.  The first mechanism is an 
-implementation of the classic Usher-McClelland (TODO ref) leaky, competing 
-accumulator model.  It has been widely used, for example in versions of the TCM 
-model (TODO ref), and TODO some of our models. We will compare this to an 
-independent accumulator model with a second thresholding layer with recurrent 
-connections to the first layer. In both cases we are especially interested in 
-situations with more than two ($d > 2$) choices.
+A large body of literature exists examining the optimality of WTA mechanisms and 
+their consistency with neurobiological and psychological 
+data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.  Here, however, we will 
+investigate the suitability of two different WTA mechanisms in the context of 
+large-scale cognitive modelling with spiking neurons on a set of benchmarks that 
+are more normative in nature.  The first mechanism is an implementation of the 
+classic leaky, competing accumulator model by~\citeA{usher2001}.  It has been 
+widely used, for example in versions of the Temporal Context 
+Model~\cite{sederberg2008}, and some of our models~\cite<e.g.,>{kajic2017}. We 
+will compare this to an independent accumulator model with a second thresholding 
+layer with recurrent connections to the first layer.  In both cases we are 
+especially interested in situations with more than two ($d > 2$) choices.
 
-For the implementation of these models we use the Neural Engineering Framework 
-(NEF) which allows us to directly implement the prescribed dynamics with spiking 
-neurons. The NEF has been used in a wide range of models TODO, including the 
-largest functional brain model Spaun (TODO ref). We will give a short 
-introduction to the NEF first, then describe the implementation of the two WTA 
-mechanisms. In section TODO, we give the results on a number of metrics, 
-followed by a discussion in section TODO\@.
+For the implementation of these models we use the Neural Engineering 
+Framework~\cite<NEF;>{eliasmith2003} which allows us to directly implement the 
+prescribed dynamics with spiking neurons. The NEF has been used in a wide range 
+of models, including the largest functional brain model 
+Spaun~\cite{eliasmith2012}.  We will give a short introduction to the NEF first, 
+then describe the implementation of the two WTA mechanisms. In 
+Section~\ref{sec:results}, we give the results on a number of metrics, followed 
+by a discussion in Section~\ref{sec:discussion}.
 
@@
 \subsection{The Neural Engineering Framework}
-We employ the Neural Engineering Framework (NEF, TODO cite) which allows us to 
-implement mathematical model descriptions in spiking neural networks based on 
-three principles: \emph{representation}, \emph{transformation}, and 
-\emph{dynamics}.
+We employ the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} which 
+allows us to implement mathematical model descriptions in spiking neural 
+networks based on three principles: \emph{representation}, 
+\emph{transformation}, and \emph{dynamics}.
 
@@
 \subsection{Leaky, competing accumulator model}
-We implement the widely used, leaky, competing accumulator model proposed by 
-TODO\@. The dynamics for the state variables $x_i, i < N$, where $N$ is the 
-number of choices, are given by
+We implement the widely used, leaky, competing accumulator model proposed 
+by~\citeA{usher2001}.  The dynamics for the state variables $x_i, i < N$, where 
+$N$ is the number of choices, are given by
 \begin{equation}\label{eqn:usher-mcclelland}
@@
 
-\section{Results}
+\section{Results}\label{sec:results}
 To test and compare the two WTA mechanisms we provide an input of $\rho_i 
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 We do not find either one of the networks to perform better on all metrics, but 
@@
 
-\nocite{ChalnickBillman1988a}
-\nocite{Feigenbaum1963a}
-\nocite{Hill1983a}
-\nocite{OhlssonLangley1985a}
-% \nocite{Lewis1978a}
-\nocite{Matlock2001}
-\nocite{NewellSimon1972a}
-\nocite{ShragerLangley1990a}
-
 \bibliographystyle{apacite}
@@
 
-\bibliography{CogSci_Template}
+\bibliography{references}
 

### 2017-01-17 doc/paper/paper.tex
Update paper, add figures.

@@
 \usepackage{pslatex}
+\usepackage{siunitx}
 \usepackage{apacite}
@@
 \begin{abstract}
-The abstract should be one paragraph, indented 1/8~inch on both sides,
-in 9~point font with single spacing. The heading ``{\bf Abstract}''
-should be 10~point, bold, centered, with one line of space below
-it. This one-paragraph abstract section is required only for standard
-six page proceedings papers. Following the abstract should be a blank
-line, followed by the header ``{\bf Keywords:}'' and a list of
-descriptive keywords separated by semicolons, all in 9~point font, as
-shown below.
+    TODO
 
-\textbf{Keywords:} 
-add your choice of indexing terms or keywords; kindly use a
+\textbf{Keywords:} TODO add your choice of indexing terms or keywords; kindly 
+use a
 semicolon; between each term
@@
 are more normative in nature.  The first mechanism is an implementation of the 
-classic leaky, competing accumulator model by~\citeA{usher2001}.  It has been 
-widely used, for example in versions of the Temporal Context 
+leaky, competing accumulator model by~\citeA{usher2001}.  It has been widely 
+used, for example in versions of the Temporal Context 
 Model~\cite{sederberg2008}, and some of our models~\cite<e.g.,>{kajic2017}. We 
@@
 layer with recurrent connections to the first layer.  In both cases we are 
-especially interested in situations with more than two ($d > 2$) choices.
+especially interested in situations with more than two choices ($d > 2$).
 
@@
 Spaun~\cite{eliasmith2012}.  We will give a short introduction to the NEF first, 
-then describe the implementation of the two WTA mechanisms. In 
-Section~\ref{sec:results}, we give the results on a number of metrics, followed 
-by a discussion in Section~\ref{sec:discussion}.
+then describe the implementation of the two WTA mechanisms. Then we give the 
+results on a number of metrics, followed by a discussion.
 
@@
 We employ the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} which 
-allows us to implement mathematical model descriptions in spiking neural 
+allows us to implement equations describing the model dynamics in spiking neural 
 networks based on three principles: \emph{representation}, 
@@
 \subsubsection{Principle 1: Representation}
-The representation of a value $x(t)$ with a population of spiking neurons is 
-defined by the encoding and decoding. The encoding converting the value $x$ into 
-a spike train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
+The representation of a value $x(t)$ with a population of neurons is defined by 
+the encoding and decoding. The encoding converting the value $x$ into a spike 
+train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
 \begin{equation}
@@
 \end{equation}
-where $\alpha_i$ is a gain factor, $J_i^{mathrm{bias}}$ a bias current and $G_i$ 
-is the neuron linearity. Here, we use spiking leaky integrate-and-fire neurons 
-for $G_i$.
+where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current and 
+$G_i$ is the neuron non-linearity. Here, we use spiking, leaky 
+integrate-and-fire neurons as $G_i$.
 
@@
 \end{equation}
-where $h(t) = \tau^{-1}\exp(1/\tau)$ is the synaptic filter. The decoding 
-weights are obtained with a least-squares optimization of the error $E^x 
-= \abs{x - \hat x}$.
+where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(1/\tau_{\mathrm{s}})$ is an exponential 
+synaptic filter with time constant $\tau_{\mathrm{s}}$.  The decoding weights 
+are obtained with a least-squares optimization of the error $E_x = \abs{x 
+    - \hat{x}}$.
 
@@
 \subsubsection{Principle 2: Transformation}
-By finding alternate decoding weights $d^f_i$ with the error given by $E^{f(x)} 
+By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} 
 = \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be 
@@
 \subsection{Leaky, competing accumulator model}
-We implement the widely used, leaky, competing accumulator model proposed 
-by~\citeA{usher2001}.  The dynamics for the state variables $x_i, i < N$, where 
+We implement the widely used, leaky, competing accumulator (LCA) model proposed 
+by~\citeA{usher2001}.  The dynamics for the state variables $x_i,\ i < N$, where 
 $N$ is the number of choices, are given by
@@
     \begin{split}
-    dx_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
-    \frac{dt}{\tau'} \\
+        \dif x_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
+        \frac{\dif t}{\tau} \\
     x_i &\rightarrow \max(x_i, 0)
@@
 where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
-inhibition, and $tau'$ the time constant. Note that one usually wants to set $k 
+inhibition, and $\tau$ the time constant. Note that one usually wants to set $k 
 = \beta$ because TODO\@. Here, we chose $k = \beta = 1$. TODO what does changing 
-this control? Why can we fix it at 1?
+this control? Why can we fix it at 1? (Or at least why is it convenient?)
 
@@
 same time adhering to the dynamics prescribed by the model.  
-
-TODO figure with dynamics
+Figure~\ref{fig:usher-mcclelland} shows an example output.
 \begin{figure}
@@
     \includegraphics{figures/usher-mcclelland}
-    \caption{TODO}\label{fig:usher-mcclelland}
+    \caption{Example time course of the state variables in the leaky, competing 
+        accumulator model with three dimensions. The vector of inputs is given 
+        by $(0.8, 0.7, 0.6)$.}\label{fig:usher-mcclelland}
 \end{figure}
@@
 \subsection{Independent accumulator model}
-The other Winner-take-all mechanism is related to the Usher-McClelland model and 
-even more closely to independent accumulator models (TODO refs), but has some 
-fine and important distinctions. It consists of two layers of neural 
-populations. The first layer are independent accumulators obtained from 
-Equation~\ref{eqn:usher-mcclelland} by setting $k = \beta = 0$ resulting in
+The other investigated winner-take-all mechanism is an independent accumulator 
+(IA) model, i.e.~there is no interaction like mutual inhibition among the 
+accumulators. Compared to prior similar models (TODO refs), however, we add 
+a second layer of independent, non-recurrent populations that get input from the 
+first layer in a one to one projection. We decode the shifted Heaviside function 
+$\bar{x}_{2,i} = \Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ is 
+a threshold value controlling how much evidence needs to be accumulated to 
+produce an output.
+The Heaviside decoded output of layer 2 projects back to layer 1 to add 
+$\bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$. As 
+effect the choice will be stabilized while all other state variables will be 
+suppressed once one of the accumulators reaches the threshold $\vartheta$.  The 
+dynamics are described by the following equations.
 \begin{equation}
     \begin{split}
-    dx^1_i &= \lambda \rho_i \frac{dt}{\tau} \\
-    x^1_i &\rightarrow \max(x^1_i, 0) \text{.}
+        \dif x_{1,i} &= \lambda \rho_i \frac{\dif t}{\tau_1} + \left( 
+            \bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j} \right) \frac{\dif 
+            t}{\tau_2} \\
+    x_{1,i} &\rightarrow \max(x_{1,i}, 0) \text{.}
     \end{split}
 \end{equation}
-The parameter $\lambda$ scales this input and is introduced because it is more 
-convenient to manipulate than then the threshold parameter $\vartheta$ 
-introduced below.
 
-The second layer consists of independent non-recurrent populations that get 
-input from the first layer in a one to one projection. We decode the shifted 
-Heaviside function $\Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ 
-is a threshold value controlling how much evidence needs to be accumulated to 
-produce an output. Instead of controlling this threshold, it is more convenient 
-to scale the input with $\lambda$ in the context of the NEF, though 
-mathematically both approaches are equivalent. As the Usher-McClelland does not 
-have a threshold parameter, we do not introduce the input scaling $\lambda$ in 
-that model.
-
-The Heaviside decoded output of layer 2 projects back to layer 1 to add $x^2_i 
-- 2\sum_{j \neq i} x^2_j$ to the input of $x^1_i$. As effect the choice will be 
-stabilized while all other state variables will be suppressed once one of the 
-accumulators reaches the threshold $\vartheta$.
-
-TODO figure with dynamics
+Instead of controlling the threshold $\vartheta$, in the context of the NEF, it 
+is more convenient to keep $\vartheta$ fixed and scale the input with the 
+$\lambda$ parameter. Mathematically both approaches are equivalent. We set 
+$\lambda = 1$ where not noted otherwise. As the LCA model does not have 
+a threshold parameter, we do not introduce the input scaling $\lambda$ in that 
+model.  Figure~\ref{fig:indacc} shows an example of the model dynamics.
 \begin{figure}
@@
     \includegraphics{figures/indacc}
-    \caption{TODO}\label{fig:indacc}
+    \caption{Example time course of the state variables $x_{1,i}$ and decoded 
+        output $\bar{x}_{2,i}$ in the independent accumulator model with three 
+        dimensions. The vector of inputs is given by (0.8, 0.7, 0.6).
+    }\label{fig:indacc}
 \end{figure}
 
-\section{Results}\label{sec:results}
+\subsection{Metrics}
 To test and compare the two WTA mechanisms we provide an input of $\rho_i 
 = u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
-$s$ the separation to all other inputs, $\delta$ the Kronecker delta, and 
+$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
 $\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
 loss of generality, the first state variable receives the strongest input and 
-all other state variables receive input that is $s$ less. We chose this input as 
-it it represents the worse case for picking out the strongest input as $s 
-\rightarrow 0$ and as one input $\rho_i \rightarrow 0$ it will have less 
-influence on the overall dynamics of the two WTA mechanisms.
+all other state variables receive input that is smaller by $s$. We chose this 
+input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
+decrease and the effective number of choices to decide between would decrease  
+As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
+long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
+both WTA models we use 200 neurons for each dimensions. In the IA network this 
+are split as 150 neurons for each layer 1 population and 50 neurons for each 
+layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
+\begin{table}
+    \caption{Summary of parameter values.}\label{tbl:params}
+    \begin{tabular}{ll}
+        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
+        LCA recurrency parameters & $k = \beta = 1$ \\
+        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
+        IA feed-back time constant & $\tau_2 = \SI{100}{\second}$ \\
+        IA threshold & $\vartheta = 0.8$ \\
+        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
+        = \SI{0.1}{\second}$ \\
+        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
+        = \SI{5}{\milli\second}$ \\
+        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
+        = \SI{10}{\milli\second}$
+    \end{tabular}
+\end{table}
 
-To evaluate the two mechanisms we use a number of metrics. First we determine 
-whether the model is able to form a clear decision at all within a second of 
-simulated time. To count as a clear decision at least one output needs to stay 
-above 0.15 for a second after the initial second of simulation time. This 
-ensures that the output is different from a 0 output which could slightly be 
-above 
-0 due to noise. Furthermore, we require that the largest output will be the 
-  largest output for all of that second of simulation time because otherwise the 
-  decision would switch.
+To evaluate the two mechanisms on this input, we use a number of metrics. First 
+we determine whether the model is able to form a clear decision at all within 
+a second of simulated time. To count as a clear decision, at least one output 
+needs to stay above 0.15 for the time interval
+$]\SI{1}{\second}, \SI{2}{\second}]$. % chktex 10
+This lower bound was chosen to ensure that noise on a zero output is not 
+mistaken as a non-zero output.  Furthermore, we require that the largest output 
+will be the largest output for all of the time interval or in other words the 
+decision does not change during that time interval.
 
 This does not take into account whether the winning output actually corresponds 
-to the strongest input, but sometimes it can be more desirable to form a clear 
-decision at all than finding the actual strongest input. In other situations, 
-though, the correctness of the decision might be important. So this is our next 
-metric. A trial is considered correct if the model forms a clear decision and 
-the largest output corresponds to the largest input.
+to the strongest input, but sometimes it can be more desirable to produce 
+a clear decision than actually finding the strongest input in all instances. In 
+other situations, though, the correctness of the decision might be of higher 
+importance. We consider a trial correct if the model forms a clear decision and 
+the largest output corresponds to the largest input. All remaining metrics will 
+be calculated on the subset of trials with a clear decision.
 
-The time it takes to form a decision can be relevant too. We define the decision 
-time as how long it takes to fulfill the conditions of a clear decision.
+The time it takes to form a decision can be relevant too.  We define the 
+decision time as how long it takes to fulfill the conditions of a clear 
+decision.
 
-These metrics cover the basic performance of the WTA mechanims. When using a WTA 
-mechanism within larger cognitive models, the exact magnitude of the outputs can 
-be important. Ideally, the output would be 1 for the winner and 0 for all other 
-outputs.\footnote{Technically, the winner output could be scaled to any 
-    magnitude. We use 1 here as it is most convenient to work with.} We define 
-the \emph{winner error} $E_1$ as the difference of the winner output from 1 and 
-the \emph{runner-up error} $E_2$ as the difference of second largest output from 
-0 (negative values treated as 0). We use the average output values of the second 
-  second in the simulation as the value can fluctuate over time.
+These metrics cover the basic performance of the WTA mechanisms. When using 
+a WTA mechanism within larger cognitive models, the exact magnitude of the 
+outputs can be important. Ideally, the output would be 1 for the winner and zero 
+for all other outputs.\footnote{Technically, the winner output could be scaled 
+    to any magnitude. We use 1 here as it is most convenient to work with.} The 
+LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being 
+the largest input. We define the \emph{winner error} $E_1$ as the difference of 
+the winner output from $u$ for the LCA model, as the difference from 1 for the 
+IA model and, for both models, the \emph{runner-up error} $E_2$ as the 
+difference of second largest output from 
+0 (negative values treated as 0). We use the average output values of the time 
+  interval
+ $]\SI{1}{\second}, \SI{2}{\second}]$ % chktex 10
+to calculate these error values as the values fluctuate over time.
 
-These two metrics only look at the final output, but the model can produce 
-transient outputs before the final decision is achieved. Within the context of 
-a larger model, this can be a problem as the transient output could already be 
-interpreted as a decision. Thus, we define $E_{2,\max}$ as the highest output of 
-a non-winning output during the whole simulation.
+These two metrics only look at the final output averaged over time, but the 
+model can produce transient outputs before the final decision is achieved.  
+Within the context of a larger model, this can be a problem as the transient 
+output could already be interpreted as a decision. Thus, we define $E_{2,\max}$ 
+as the highest output of a non-winning output during the whole simulation.
 
+\section{Results}
 We find that the ability to reach a clear decision depends on the magnitude of 
-the highest input for both networks. This is not surprising. In the 
-Usher-McClelland the output magnitude will be determined by the input magnitude 
-of the largest input. As such the largest input needs to be above 0.2 to fulfill 
-the requirements. For the independent accumulator model the input has to be 
-large enough to reach the integration threshold within the time limit. By 
-increasing the input scaling $\lambda$ or the time limit one could get a clear 
-decision for smaller inputs within the time limit. We further find that the 
-independent accumulator model is independent of the input noise and target 
-separation for all tested parameters. This is not the case for the 
-Usher-McClelland model as shown in Figure~TODO where the fraction of trials 
-without a clear decision increases with noise and smaller target separation.
+the highest input for both networks. This is not surprising. In the LCA model 
+the output magnitude will be determined by the input magnitude of the largest 
+input.  As such the largest input needs to be above 0.15 to fulfill the 
+requirements. For the independent accumulator model the input has to be large 
+enough to reach the integration threshold within the time limit. By increasing 
+the input scaling $\lambda$ or the time limit one could get a clear decision for 
+smaller inputs within the time limit. We further find that the IA model is 
+independent of the input noise and target separation for all tested parameters.  
+This is not the case for the LCA model as shown in Figure~\ref{fig:decisions} 
+where the fraction of trials without a clear decision increases with noise and 
+smaller target separation.
 \begin{figure}
@@
     \includegraphics{figures/decisions}
-    \caption{TODO}\label{fig:decisions}
+    \caption{Fraction of trials with a clear decision for different input noise 
+        standard deviations $\sigma$ and target separations $s$ for the LCA 
+        model. Error bars denote bootstrapped 95\% confidence intervals.  The 
+        grey horizontal line shows the optimum.}\label{fig:decisions}
 \end{figure}
 
-However, when considering the correctness of the decisions (Figure~TODO) the 
-Usher-McClelland model is doing better. We can alleviate that difference to some 
-degree by reducing the input scaling to $\lambda = TODO$, but perform still 
-worse for small target separations when staying in the time limit.
+However, when considering the correctness of the decisions (see 
+Fig.~\ref{fig:correct}) the LCA model is doing better. We can alleviate that 
+difference to some degree by reducing the input scaling to $\lambda = 0.2$, but 
+perform still worse for some combinations of input noise and target separation 
+when staying below the time limit. This in some part due to a systematic bias 
+for certain dimensions introduced in the second layer of the IA model. In the 
+NEF the neuron gain and bias parameters are usually picked from random 
+distributions. As such the layer 2 populations will become active at slightly 
+different thresholds. By using identical layer 2 populations, i.e.~identical 
+gain and bias parameters for each population, this bias can be eliminated and 
+the IA model performs better than the LCA model in most instances.
 \begin{figure*}
@@
     \includegraphics{figures/correct}
-    \caption{TODO}\label{fig:correct}
+    \caption{Fraction of correct trials for different input noise standard 
+        deviations $\sigma$, target separations $s$, and models.  Error bars 
+        denote bootstrapped 95\% confidence intervals. The grey horizontal line 
+        shows the optimum.}\label{fig:correct}
 \end{figure*}
 
-The time required to reach a decision in the Usher-McClelland model depend 
-mostly on the target separation and amount of noise on the input (Figure~TODO), 
-the magnitude of the largest input is of minor influence. In contrast to that, 
-in the independent accumulator model the scaled magnitude of the largest input 
-is the most important factor. Depending on this magnitude the network can either 
-be faster or slower than the Usher-McClelland network, but it will need more 
-time to achieve the same correctness of responses. There is also a slight 
-influence of target separation and input noise with an interaction of these two 
-parameters (Figure~TODO).
+The time required to reach a decision in the LCA model depends mostly on the 
+target separation and amount of noise on the input (see Fig.~\ref{fig:time}), 
+the magnitude of the largest input is of minor influence. Also, the confidence 
+intervals indicate a larger variance in the decision times with less target 
+separation and more input noise. In contrast to that, in the IA model the scaled 
+magnitude of the largest input is the most important factor.  Depending on this 
+magnitude the network can either be faster or slower than the LCA network, but 
+it will need more time to achieve the same fraction of correct responses.  There 
+is also a slight influence of target separation and input noise with an 
+interaction of these two parameters.
+\begin{figure*}
+    \centering
+    \includegraphics{figures/time}
+    \caption{Mean decision times for different input noise standard deviations 
+        $\sigma$ and target separations $s$ for the LCA and IA model. For the IA 
+        model $u = 0.2$ is shown which shows the interaction of target 
+        separation and input noise most clearly. Error bars denote bootstrapped 
+        95\% confidence intervals.  The grey horizontal lines show the 
+        optimum.}\label{fig:time}
+\end{figure*}
 
-The output of the independent accumulator model matches almost perfectly the 
-specifications. This is not the case for the Usher-McClelland model 
-(Figure~TODO).  For small target separations the output of the winner will stay 
-below 1 and this will get worse with increased noise. As the winner output will 
-try to match the largest input TODO explanation. Furthermore, the 
-Usher-McClelland model will have residual outputs of non-winning choices under 
-noisy conditions and with small target separations.
+The output of the IA model matches almost perfectly the specifications of 
+producing an output of 1 for the winner and 0 for all other dimensions.  This is 
+not the case for the LCA model (see Fig.~\ref{fig:error}).  For small target 
+separations the output of the winner will stay below $u$ and this will get worse 
+with increased noise. Furthermore, the LCA model will have residual outputs of 
+non-winning choices under noisy conditions and with small target separations.
+\begin{figure*}
+    \centering
+    \includegraphics{figures/error}
+    \caption{Error on outputs for different input noise standard deviations 
+        $\sigma$ and target separations $s$ for the LCA model.  Error bars 
+        denote bootstrapped 95\% confidence intervals. The grey horizontal lines 
+        show the optimum.}\label{fig:error}
+\end{figure*}
 
 Finally, looking at the transient responses both models might produce outputs of 
-non-winning choices. For the Usher-McClelland model these increase with noise on 
-the input and, for small target separation, can approach the final output of the 
-winning dimensions. For the independent accumulator model, transient output are 
-smaller in noisy conditions, but can be higher than for the Usher-McClelland 
-model in less noisy conditions. The magnitude of such transient responses is 
-reduced by decreasing the input scaling.
+non-winning choices (see Fig.~\ref{fig:transient}). For the LCA model these 
+increase with noise on the input and, for small target separation, can approach 
+the final output of the winning dimensions. For the IA model, transient outputs 
+are smaller in noisy conditions, but can be higher than for the LCA model in 
+less noisy conditions.  The magnitude of such transient responses is reduced by 
+decreasing the input scaling.
+\begin{figure*}
+    \centering
+    \includegraphics{figures/transient}
+    \caption{Highest transient response of non-winning dimensions for different 
+        input noise standard deviations $\sigma$ and target separations $s$ for 
+        the LCA and IA model. Error bars denote bootstrapped 95\% confidence 
+        intervals. The grey horizontal lines show the 
+        optimum.}\label{fig:transient}
+\end{figure*}
 
-\section{Discussion}\label{sec:discussion}
-We do not find either one of the networks to perform better on all metrics, but 
-rather they excel at slightly different things. The Usher-McClelland network is 
-better suited to quickly determine the correct winner. However, under noisy 
-conditions it can end up not producing a clear output at all and basically not 
-making a decision at all. The independent accumulator model might not be as 
-quick or find the correct winner as often, but given enough time it will 
-eventually arrive at a decision and produce a clear output.
+\section{Discussion}
+We find neither of the two networks to perform better on all metrics, but rather 
+they are suited for slightly different things. The leaky, competing accumulator 
+model is better at quickly determining the correct winner. However, under noisy 
+conditions it can end up not producing a clear output at all and thus failing to 
+produce a decision.  The independent accumulator model might not be as quick or 
+find the correct winner as often, but given enough time it will eventually 
+arrive at a decision and produce a clear output.
 
-The Usher-McClelland network is especially suited for situations where 
-a decision needs to be continuously adjusted. The prescribed dynamics 
-essentially try to output what the currently largest input is considering some 
-smoothing over time. This makes it quick to respond to changes of the input, but 
-can also lead randomly switching outputs due to noise. In comparison, the 
-independent accumulator model is more suited in situations where a discrete 
-sequence of decisions is required. During the initial phase the model will just 
-integrate evidence without any output and after making a decision, it is 
-necessary to reset the model by inhibiting all layer 1 neurons. This limits the 
-how quickly successive decisions can be made, but at the same time once 
-a decision is made the network provides a stable output.
+The LCA network is especially suited for situations where a decision needs to be 
+continuously adjusted. The prescribed dynamics essentially try to output what 
+the currently largest input is considering some smoothing over time. This makes 
+it quick to respond to changes of the input, but can also lead to random 
+switching outputs due to noise. In comparison, the IA model is more suited in 
+situations where a discrete sequence of decisions is required.  During the 
+initial phase the model will just integrate evidence without any output and 
+after making a decision, it is necessary to reset the model by inhibiting all 
+layer 1 neurons. This limits the how quickly successive decisions can be made, 
+but at the same time, once a decision is made, the network provides a stable 
+output.
 
 There are also certain considerations to be made when integrating these networks 
-in larger neural or cognitive models. This integration is easy for the 
-independent accumulator model as it provides a clear output. The output of the 
-winning choice is also close to one which makes it easy to detect when the 
-decision has been made and processing can continue. This is problematic in the 
-Usher-McClelland model where we get a fluctuating output before the final 
-decision and as this output can get close to the final output we cannot 
-necessarily use the crossing of a threshold. Moreover, the magnitude of the 
-final output depends on the magnitude of the input which is also a problem for 
-using a fixed threshold.
+into larger neural or cognitive models. This integration is easy for the IA 
+model as it provides a clear output. The output of the winning choice is also 
+always close to one, independent of the input, which makes it easy to detect 
+when the decision has been made and processing can continue. This is problematic 
+in the LCA model where we get a fluctuating output before the final decision and 
+the magnitude of the output depends on the input magnitude. This makes it 
+problematic to use a fixed threshold to detect the decision. Furthermore, 
+transient responses of non-winning dimensions can get close to the final output 
+of the winning dimension in the LCA model.
 
 Part of the reason why the independent accumulator model produces less correct 
-responses is a systematic bias introduced in the second layer. Usually the 
-neural properties are selected randomly in the NEF and this will result in 
-slightly different thresholds for each of the populations before it will fire.  
-It is possible to select the neural parameters in a way that all of these 
-populations will have the same threshold which improves the correctness 
-(Figure~TODO). However, this would require a very precise tuning of the neurons 
+responses is the systematic bias introduced in the second layer. By eliminating 
+this bias through identical ensembles the correctness of the model is increased 
+considerably. However, this would require a very precise tuning of the neurons 
 that might not be biologically plausible.
@@
 
-We did not investigate the biological plausibility here because there is 
-evidence to be found for both networks (TODO references). Also, the 
-implementation is spiking neurons ensures a certain level of biological 
-plausibility.
+We did not investigate the biological plausibility here because this has been 
+done before for different WTA networks.  Also, the implementation in spiking 
+neurons ensures a certain level of biological plausibility. We also did not look 
+at at the influence of the number of dimensions $d$ in detail, but qualitatively 
+the results will stay the same. For higher $d$, we expect less correct responses 
+as each additional dimensions adds a chance that this dimension will win out due 
+to noise.
 
-TODO\@: distribution of neurons in network, looking only at cases where 
-a decision could be made within the results, what about more choices, include 
-a number of parameters and github url.
+TODO\@: looking only at cases where a decision could be made within the results, 
+include a number of parameters and github url.
+
+\section{Notes}
+Simulation source code and additional analysis results are available at 
+\url{https://github.com/ctn-waterloo/cogsci17-decide}.  These have not been peer 
+reviewed.
 
 \section{Acknowledgments}
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
-
-\section{References Instructions}
-
-Follow the APA Publication Manual for citation format, both within the
-text and in the reference list, with the following exceptions: (a) do
-not cite the page numbers of any book, including chapters in edited
-volumes; (b) use the same format for unpublished references as for
-published ones. Alphabetize references by the surnames of the authors,
-with single author entries preceding multiple author entries. Order
-references by the same authors by the year of publication, with the
-earliest first.
-
-Use a first level section heading, ``{\bf References}'', as shown
-below. Use a hanging indent style, with the first line of the
-reference flush against the left margin and subsequent lines indented
-by 1/8~inch. Below are example references for a conference paper, book
-chapter, journal article, dissertation, book, technical report, and
-edited volume, respectively.
+TODO anything missing here?
+This work was supported by the Canada Research Chairs program,
+the NSERC Discovery grant 261453, Air Force Office of Scientific Research grant 
+FA8655-13-1-3084, CFI and OIT\@.  % chktex 8
 
@@
 
-\end{document}
+\end{document} % chktex 17

### 2017-01-18 cogsci17_decide/networks.py
Do not use discrete version of principle 3.

@@ -8,15 +8,14 @@ def UsherMcClelland(d, n_neurons, dt):
     tau_model = 0.1
 
     tau_actual = 0.1
-    a = np.exp(-dt / tau_actual)
 
     # eqn (4) ignoring truncation, put into the canonical form:
     #   x[t+dt] = Ax[t] + Bu
     inhibit = np.ones((d, d))
     inhibit[np.diag_indices(d)] = 0.
     I = np.eye(d)
-    B = dt / tau_model
-    A = (-k * I - beta * inhibit) * dt / tau_model + I
+    B = 1. / tau_model
+    A = (-k * I - beta * inhibit) / tau_model
 
     with nengo.Network() as net:
         net.input = nengo.Node(size_in=d)
@@ -25,12 +24,12 @@ def UsherMcClelland(d, n_neurons, dt):
             eval_points=nengo.dists.Uniform(0., 1.),
             intercepts=nengo.dists.Uniform(0., 1.),
             encoders=nengo.dists.Choice([[1.]]))
-        nengo.Connection(x.output, x.input, transform=(A - a * I) / (1. - a),
+        nengo.Connection(x.output, x.input, transform=tau_actual * A + I,
                          synapse=tau_actual)
 
         nengo.Connection(
             net.input, x.input,
-            transform=B / (1 - a),  # discrete principle 3
+            transform=tau_actual * B,
             synapse=tau_actual)
 
         net.output = x.output
@@ -44,15 +43,14 @@ def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
     tau_model = 0.1
 
     tau_actual = 0.1
-    a = np.exp(-dt / tau_actual)
 
     # eqn (4) ignoring truncation, put into the canonical form:
     #   x[t+dt] = Ax[t] + Bu
     inhibit = np.ones((d, d))
     inhibit[np.diag_indices(d)] = 0.
     I = np.eye(d)
-    B = 1.0 * dt / tau_model
-    A = (-k * I - beta * inhibit) * dt / tau_model + I
+    B = 1.0 / tau_model
+    A = (-k * I - beta * inhibit) / tau_model
 
     n_neurons_threshold = 50
     n_neurons_x = n_neurons - n_neurons_threshold
@@ -67,12 +65,12 @@ def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
             intercepts=nengo.dists.Uniform(0., 1.),
             encoders=nengo.dists.Choice([[1.]]))
         net.x = x
[…]

### 2017-01-18 cogsci17_decide/networks.py
Added tau1 and tau2 to IA model code

@@ -6,14 +6,12 @@ def UsherMcClelland(d, n_neurons, dt):
     k = 1.
     beta = 1.
     tau_model = 0.1
-
     tau_actual = 0.1
 
-    # eqn (4) ignoring truncation, put into the canonical form:
-    #   x[t+dt] = Ax[t] + Bu
-    inhibit = np.ones((d, d))
-    inhibit[np.diag_indices(d)] = 0.
+    # eqn (4) ignoring truncation, put into continuous LTI form:
+    #   dot{x} = Ax + Bu
     I = np.eye(d)
+    inhibit = 1 - I
     B = 1. / tau_model
     A = (-k * I - beta * inhibit) / tau_model
 
@@ -38,19 +36,22 @@ def UsherMcClelland(d, n_neurons, dt):
 
 
 def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
-    k = 0.
-    beta = 0.
-    tau_model = 0.1
-
+    bar_beta = 2.  # should be >= 1 + max_input * tau2 / tau1
+    tau_model1 = 0.1
+    tau_model2 = 0.1
     tau_actual = 0.1
 
-    # eqn (4) ignoring truncation, put into the canonical form:
-    #   x[t+dt] = Ax[t] + Bu
-    inhibit = np.ones((d, d))
-    inhibit[np.diag_indices(d)] = 0.
+    # dynamics put into continuous LTI form:
+    #   dot{x1} = A1x1 + A2x2 + Bu
+    # where x1 is the state variable for layer 1 and
+    #       x2 is the state variable for layer 2
+    # note that from the perspective of Principle 3, A2x2 is treated
+    # as an "input" similar to u
     I = np.eye(d)
-    B = 1.0 / tau_model
-    A = (-k * I - beta * inhibit) / tau_model
+    inhibit = 1 - I
+    B = 1. / tau_model1  # input -> layer 1
+    A1 = 0  # (integrator) layer1 -> layer1
+    A2 = (I - bar_beta * inhibit) / tau_model2  # layer 2 -> layer 1
 
     n_neurons_threshold = 50
     n_neurons_x = n_neurons - n_neurons_threshold
@@ -65,7 +66,7 @@ def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
             intercepts=nengo.dists.Uniform(0., 1.),
             encoders=nengo.dists.Choice([[1.]]))
         net.x = x
[…]

### 2017-01-19 psy-tasks/task_decision.py
Update simulation parameters.

@@ -10,12 +10,12 @@ pspace = (
             share_thresholding_intercepts=[False]) +
         Param(network=['DriftDiffusion']) *
         Param(share_thresholding_intercepts=[False, True]) *
-        Param(scale=[0.15, 1.])
+        Param(scale=[0.2, 1.])
     ) *
-    Param(baseline=[0.1, 0.5, 0.8]) *
+    Param(baseline=[0.2, 0.6, 1.0]) *
     Param(target_sep=[0.05, 0.1, 0.15, 0.2]) *
     Param(noise=[0.0, 0.01, 0.02, 0.03, 0.04, 0.05]) *
-    Param(seed=range(10))
+    Param(seed=range(50))
 )
 
 min_items = 1

### 2017-01-20 doc/paper/paper.tex
Supplementary analysis and bar-beta

@@
 by~\citeA{usher2001}.  The dynamics for the state variables $x_i,\ i < N$, where 
-$N$ is the number of choices, are given by
-\begin{equation}\label{eqn:usher-mcclelland}
+$N$ is the number of choices, are given by:
+\begin{equation} \label{eqn:usher-mcclelland}
     \begin{split}
-        \dif x_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
-        \frac{\dif t}{\tau} \\
-    x_i &\rightarrow \max(x_i, 0)
+        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
+        x_i &\rightarrow \max(x_i, 0) ,
     \end{split}
@@
 where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
-inhibition, and $\tau$ the time constant. Note that one usually wants to set $k 
-= \beta$ because TODO\@. Here, we chose $k = \beta = 1$. TODO what does changing 
-this control? Why can we fix it at 1? (Or at least why is it convenient?)
+inhibition, and $\tau$ the time constant.
+We set $k = \beta = 1$, since this will guarantee that the winning state converges to the value of its input, while the losing states converge to zero.
+Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).
 
@@
 The Heaviside decoded output of layer 2 projects back to layer 1 to add 
-$\bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$. As 
-effect the choice will be stabilized while all other state variables will be 
+$\bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$.
+For $\bar{\beta} = 2$ (see supplementary analysis), the correct choice will self-excite while all other state variables will be 
 suppressed once one of the accumulators reaches the threshold $\vartheta$.  The 
-dynamics are described by the following equations.
+dynamics are described by the following equations:
 \begin{equation}
     \begin{split}
-        \dif x_{1,i} &= \lambda \rho_i \frac{\dif t}{\tau_1} + \left( 
-            \bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j} \right) \frac{\dif 
-            t}{\tau_2} \\
-    x_{1,i} &\rightarrow \max(x_{1,i}, 0) \text{.}
+        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
+            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
+        x_{1,i} &\rightarrow \max(x_{1,i}, 0) .
     \end{split}
@@
         IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
-        IA feed-back time constant & $\tau_2 = \SI{100}{\second}$ \\
+        IA feed-back time constant & $\tau_2 = \SI{0.1}{\second}$ \\
         IA threshold & $\vartheta = 0.8$ \\
@@
         Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
-        = \SI{5}{\milli\second}$ \\
+        = \SI{0.005}{\second}$ \\
         Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
-        = \SI{10}{\milli\second}$
+        = \SI{0.01}{\second}$
     \end{tabular}

### 2017-01-20 doc/paper/supplementary.tex
Supplementary analysis and bar-beta

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{commath}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}

\title{Supplementary Analysis}
\author{Jan Gosmann, Aaron R. Voelker, and Chris Eliasmith}

\begin{document}
\maketitle

%\begin{abstract}
%\end{abstract}

\section{Leaky, Competing Accumulator Model Analysis}

The model dynamics for the leaky, competing accumulator (LCA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
        x_i &\rightarrow \max(x_i, 0) .
    \end{split}
\end{equation}
We now justify our choice of $k = \beta = 1$ from the text.
This guarantees that the winning state will converge to its input value, and each losing state will converge to zero.

\subsection{Effect of $k = 1$}

To isolate the `role' of $k$, we consider the case where $\beta \sum_{j \ne i} x_j = 0$. 
% it suffices to consider the case where $\beta = 0$ and ignore the rectification of $x_i$.
% Note that this is equivalent to assuming $x_j = 0$ for all $j \ne i$.
This situation obeys the dynamics:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i\right) 
        \frac{1}{\tau}
    \end{split}.
\end{equation}
We then take the Laplace transform of both sides, and rearrange to obtain:
\begin{equation}
s\mathcal{L}\{x_i\} = \left( \mathcal{L}\{\rho_i\} - k\mathcal{L}\{x_i\} \right) \frac{1}{\tau} \quad \iff \quad \frac{\mathcal{L}\{x_i\}}{\mathcal{L}\{\rho_i\}} = \frac{1}{\tau s + k}.
\end{equation}
When $k = 1$, this is commonly referred to as a first-order lowpass filter with time-constant $\tau$.
This effect of this filter in the time-domain is a convolution with the exponentially decaying function $h(t) := \tau^{-1} \exp\left( -t / \tau \right)$.
More generally, when $k > 0$, this has the transfer function:
\begin{equation}
\frac{1}{\tau s + k} = \frac{k^{-1}}{(\tau k^{-1})s + 1}
\end{equation}
which is the same lowpass with an effective time-constant of $(\tau k^{-1})$ and a multiplicative gain of $k^{-1}$.
In plain words, different values of $k > 0$ do nothing but alter the effective time-constant and the effective gain on the input.
%,which are already free parameters in the NEF.
%Setting $k = 1$ is most convenient since this yields the time-constant $\tau$ with unit gain.

Therefore, by setting $k = 1$, we have $x_i = \rho_i \ast h$ provided that $\beta \sum_{j \ne i} x_j = 0$.
% Since the NEF gives us freedom to vary such gains and time-constants (at the representational level) independently of the underlying neural and synaptic model parameters (via principles 1 and 3, respectively), it suffices to fix $k = 1$ for simplicity.
Below we prove that the latter assumption eventually holds whenever $i$ is the index of the winner and $\beta = 1$, and so the winner $x_i$ will converge to the value of its input $\rho_i$.

\newpage

\subsection{Effect of $\beta = 1$}

Setting $\beta = k = 1$, and defining $\chi := \sum_{j} x_j$, we rewrite the dynamics as:
\begin{equation} \label{eq:um-special}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - \chi \right) \frac{1}{\tau} \\
        x_i &\rightarrow \max(x_i, 0) .
    \end{split}
\end{equation}
We conceptualize $\chi$ as a single `meta state-variable' that, based on the value of each $\rho_i$, will change each corresponding $x_i$.
% For instance, we know that $\chi > \rho_i \iff \frac{{\partial x}_i}{\partial t} < 0$.
% This tells us that all $x_i$ will decrease until they are bounded by $0 \le x_i \le \rho_i$.
For instance, if $i$ is the index of the winner, then $x_i$ is necessarily only stable when $\chi = \rho_i \iff \frac{{\partial x}_i}{\partial t} = 0$.
Assuming stability, $\chi = \rho_i > \rho_j$ for all $j \ne i$, and thus each $x_j$ necessarily has a negative derivative.
Consequently, all losers $x_j$ will decrease to 0 and stabilize there due to rectification (and then $\chi = \rho_i = x_i$ holds as anticipated).

We also remark that if $\beta \ne 1$ then the derivatives are no longer sorted by their inputs, and in fact the order will depend on the current state (for instance, it will depend on the previous winner if the inputs were just altered). Consequently, if $\beta < 1$, then not all losers will necessarily go to zero, and if $\beta > 1$, then the previous winner may persist.

\section{Independent Accumulator Model Analysis}

The model dynamics for the independent accumulator (IA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
        x_{1,i} &\rightarrow \max(x_{1,i}, 0) ,
    \end{split}
\end{equation}
where $\bar{x}_{2, i} := \Theta(x_{2,i} - \vartheta)$ is defined by the Heaviside function shifted by $\vartheta$.
We now justify our choice of $\bar{\beta} = 2$ from the text. % Fixing $\lambda = 1$, $\tau_1 = \tau_2$.

\subsection{Effect of $\bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1}$}

Suppose index $i$ is a loser.
We know that $\bar{x}_{2,i} \le 1$, and $\sum_{j \ne i} \bar{x}_{2,j} \ge 1$, since the Heaviside is bounded above by 1, and some other $j \ne i$ has surpassed its threshold by becoming the winner.
Thus,
\begin{align}
 \frac{{\partial x}_{1,i}}{\partial t} \le \lambda \rho_i \frac{1}{\tau_1} + \left( 1 - \bar{\beta} \right) \frac{1}{\tau_2} < 0 \quad \iff \quad \bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1} ,
\end{align}
which implies that we must enforce the latter condition on $\bar{\beta}$ in order to ensure that all losers go to zero. 
In the text, $\lambda = 1$, $\tau_1 = \tau_2$, and $\max_i\{\rho_i\} < 1$ $\implies \bar{\beta} = 2$ will suffice.

\end{document}

### 2017-01-20 doc/paper/paper.tex
Added IA parameters to table

@@
         LCA time constant & $\tau = \SI{0.1}{\second}$ \\
-        LCA recurrency parameters & $k = \beta = 1$ \\
+        LCA recurrent parameters & $k = \beta = 1$ \\
         IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
@@
         IA threshold & $\vartheta = 0.8$ \\
+        IA recurrent parameters & $\lambda = 1, \bar{\beta} = 2$ \\
         Recurrent synaptic time constant & $\tau_{\mathrm{s}} 

### 2017-01-20 doc/paper/paper.tex
Format with one sentence per line.

@@
 \usepackage{apacite}
+\usepackage{xcolor}  % for \textcolor
 
-\title{TODO title}
+\newcommand{\todo}[1]{\textbf{\textsc{\textcolor{blue}{(TODO\@: #1)}}}}
+
+\title{A Spiking Independent Accumulator Model for Winner-Take-All}
 
 \author{{\large \bf Jan Gosmann (jgosmann@uwaterloo.ca)} \\
-  %Department of Psychology, 1202 W. Johnson Street \\
-  %Madison, WI 53706 USA
-  \AND{\large \bf Aaron Voelker (TODO)} \\
-  \AND{\large \bf Chris Eliasmith (TODO)}
-  %Department of Educational Psychology, 1025 W. Johnson Street \\
-  %Madison, WI 53706 USA}
+  {\large \bf Aaron R.
+Voelker (arvoelke@uwaterloo.ca)} \\
+  {\large \bf Chris Eliasmith (celiasmith@uwaterloo.ca)} \\
+  Centre for Theoretical Neuroscience, University of Waterloo \\
+  Waterloo, ON, Canada N2L 3G1
 }
@@
 \begin{abstract}
-    TODO
+The winner-take-all (WTA) mechanism is an important component of many cognitive models.
+\todo{Flesh this out a bit}
+We first provide a novel spiking implementation of the well-known leaky competing accumulator (LCA) model, by mapping its dynamics onto a population-level representation.
+We then propose a two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
+Our findings suggest that while the LCA network can rapidly adapt to new winners, the IA network is better suited for stable decision making in the presence of noise.
 
-\textbf{Keywords:} TODO add your choice of indexing terms or keywords; kindly 
-use a
-semicolon; between each term
+\textbf{Keywords:} Neural Engineering Framework; Nengo; winner-take-all; 
+decision making; mutual inhibition; neural competition; dynamical systems
 \end{abstract}
@@
 \section{Introduction}
-Winner-take-all (WTA) mechanisms are often employed in cognitive 
-models~\cite<e.g.,>{oreilly1998}.  A WTA mechanism receives a $d$-dimensional 
-input of utility values for $d$ different choices. The output is supposed to be 
-larger than zero for the dimension with highest utility and zero for all other 
-inputs.
+Winner-take-all (WTA) mechanisms are often employed in cognitive models~\cite<e.g.,>{oreilly1998}.
+A WTA mechanism receives a $d$-dimensional input of utility values for $d$ different choices.
+The output is supposed to be larger than zero for the dimension with highest utility and zero for all other inputs.
+\todo{Say some obvious things, such as the role of WTA in decision making?}
 
-A large body of literature exists examining the optimality of WTA mechanisms and 
-their consistency with neurobiological and psychological 
-data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.  Here, however, we will 
-investigate the suitability of two different WTA mechanisms in the context of 
-large-scale cognitive modelling with spiking neurons on a set of benchmarks that 
-are more normative in nature.  The first mechanism is an implementation of the 
-leaky, competing accumulator model by~\citeA{usher2001}.  It has been widely 
-used, for example in versions of the Temporal Context 
-Model~\cite{sederberg2008}, and some of our models~\cite<e.g.,>{kajic2017}. We 
-will compare this to an independent accumulator model with a second thresholding 
-layer with recurrent connections to the first layer.  In both cases we are 
-especially interested in situations with more than two choices ($d > 2$).
+A large body of literature exists examining the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
+Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
+In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of benchmarks that
+are normative in nature.
+The first mechanism is an implementation of the leaky, competing accumulator model by~\citeA{usher2001}.
+It has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and some of our models~\cite<e.g.,>{kajic2017}.
+\todo{How does the latter implementation differ from the implementation here?}
+The second mechanism is our proposed independent accumulator (IA) model, which involves a second thresholding layer that is recurrently connected to a primary integrating layer.
+For both mechanisms we are interested in decision-making tasks involving more than two choices ($d > 2$). \todo{Misplaced sentence.}
 
-For the implementation of these models we use the Neural Engineering 
-Framework~\cite<NEF;>{eliasmith2003} which allows us to directly implement the 
-prescribed dynamics with spiking neurons. The NEF has been used in a wide range 
-of models, including the largest functional brain model 
-Spaun~\cite{eliasmith2012}.  We will give a short introduction to the NEF first, 
-then describe the implementation of the two WTA mechanisms. Then we give the 
-results on a number of metrics, followed by a discussion.
+To implement these models, we use the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} to map some prescribed dynamics onto populations of spiking neurons.
+The NEF has been used for a wide variety of models, including the largest functioning simulation of the human brain~\cite{eliasmith2012}.
+We first provide a short introduction to the NEF, and then describe the implementation of the two WTA mechanisms.
+We then describe our benchmarks, and discuss some resulting implications for cognitive modelling.
 
@@
 
+\todo{Bold font for vectors}
+
 \subsection{The Neural Engineering Framework}
-We employ the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} which 
-allows us to implement equations describing the model dynamics in spiking neural 
-networks based on three principles: \emph{representation}, 
+We employ the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} which allows us to implement equations describing the model dynamics in spiking neural networks based on three principles: \emph{representation},
 \emph{transformation}, and \emph{dynamics}.
@@
 \subsubsection{Principle 1: Representation}
-The representation of a value $x(t)$ with a population of neurons is defined by 
-the encoding and decoding. The encoding converting the value $x$ into a spike 
-train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
+The representation of a value $x(t)$ with a population of neurons is defined by the encoding and decoding.
+The encoding converting the value $x$ into a spike train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
 \begin{equation}
@@
 \end{equation}
-where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current and 
-$G_i$ is the neuron non-linearity. Here, we use spiking, leaky 
-integrate-and-fire neurons as $G_i$.
-
-Decoding weights $d_i$ are used to decode a value $\hat x(t)$ from such 
-a population of neurons with
+where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current and $G_i$ is the neuron non-linearity.
+Here, we use spiking, leaky integrate-and-fire neurons as $G_i$.
+Decoding weights $d_i$ are used to decode a value $\hat x(t)$ from such a population of neurons with
 \begin{equation}
@@
 \end{equation}
-where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(1/\tau_{\mathrm{s}})$ is an exponential 
-synaptic filter with time constant $\tau_{\mathrm{s}}$.  The decoding weights 
-are obtained with a least-squares optimization of the error $E_x = \abs{x 
-    - \hat{x}}$.
-
-For the transmission of a value from one population to another, the connection 
-weights are given by
+where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponential synaptic filter with time constant $\tau_{\mathrm{s}}$.
+The decoding weights are obtained with a least-squares optimization of the error $E_x = \abs{x     - \hat{x}}$.
+For the transmission of a value from one population to another, the connection weights are given by
 \begin{equation}
@@
 By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} 
-= \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be 
-approximated in the connections between neural populations.
+= \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be approximated in the connections between neural populations.
 
 \subsubsection{Principle 3: Dynamics}
-TODO
-
-\subsection{Leaky, competing accumulator model}
-We implement the widely used, leaky, competing accumulator (LCA) model proposed 
-by~\citeA{usher2001}.  The dynamics for the state variables $x_i,\ i < N$, where 
-$N$ is the number of choices, are given by:
+TODO \subsection{Leaky, competing accumulator model}
+We implement the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
+The dynamics for the state variables $x_i,\ i < N$, where $N$ is the number of choices, are given by:
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 \end{equation}
-where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
-inhibition, and $\tau$ the time constant.
+where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time constant.
 We set $k = \beta = 1$, since this will guarantee that the winning state converges to the value of its input, while the losing states converge to zero.
 Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).
-
-Equation~\ref{eqn:usher-mcclelland} can easily be implemented with the NEF by 
-using one population of neurons for each $x_i$.  We believe this implementation 
-to be novel as it it does not treat the $x_i$ as neural firing rates, rather the 
-neural firing rates are weighted by the decoding weights to precisely implement 
-the stated dynamics. As such the model equations do not impose restrictions on 
-the neuron model or requires to lump the neurons into a single population firing 
-rate. This allows us to use biologically more realistic neurons while at the 
-same time adhering to the dynamics prescribed by the model.  
+Equation~\ref{eqn:usher-mcclelland} can easily be implemented with the NEF by using one population of neurons for each $x_i$.
+We believe this implementation to be novel as it it does not treat the $x_i$ as neural firing rates, rather the neural firing rates are weighted by the decoding weights to precisely implement the stated dynamics.
+As such the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
+This allows us to use biologically more realistic neurons while at the same time adhering to the dynamics prescribed by the model.
 Figure~\ref{fig:usher-mcclelland} shows an example output.
@@
 \subsection{Independent accumulator model}
-The other investigated winner-take-all mechanism is an independent accumulator 
-(IA) model, i.e.~there is no interaction like mutual inhibition among the 
-accumulators. Compared to prior similar models (TODO refs), however, we add 
-a second layer of independent, non-recurrent populations that get input from the 
-first layer in a one to one projection. We decode the shifted Heaviside function 
-$\bar{x}_{2,i} = \Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ is 
-a threshold value controlling how much evidence needs to be accumulated to 
-produce an output.
-The Heaviside decoded output of layer 2 projects back to layer 1 to add 
+The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model.
+We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator.
+To enable competition, we add a second thresholding layer that will project back to self-excite and mutually-inhibit the first layer.
+We now provide the details of each layer~(Fig.~\todo{network diagram}).
+The first layer consists of a separate integrator population (i.e., accumulator) for each input.
+The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
+From the second layer, we decode the shifted Heaviside function $\bar{x}_{2,i} = \Theta(x_{2,i} - \vartheta)$ where $\vartheta = 0.8$ is a threshold value controlling how much evidence needs to be accumulated to produce an output.
+The Heaviside decoded output of layer 2 projects back to layer 1 to add <<<<<<< HEAD
 $\bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$.
-For $\bar{\beta} = 2$ (see supplementary analysis), the correct choice will self-excite while all other state variables will be 
-suppressed once one of the accumulators reaches the threshold $\vartheta$.  The 
-dynamics are described by the following equations:
+For $\bar{\beta} = 2$ (see supplementary analysis), the correct choice will self-excite while all other state variables will be suppressed once one of the accumulators reaches the threshold $\vartheta$.
+The dynamics are described by the following equations:
 \begin{equation}
@@
 
-Instead of controlling the threshold $\vartheta$, in the context of the NEF, it 
-is more convenient to keep $\vartheta$ fixed and scale the input with the 
-$\lambda$ parameter. Mathematically both approaches are equivalent. We set 
-$\lambda = 1$ where not noted otherwise. As the LCA model does not have 
-a threshold parameter, we do not introduce the input scaling $\lambda$ in that 
-model.  Figure~\ref{fig:indacc} shows an example of the model dynamics.
+Instead of controlling the threshold $\vartheta$, in the context of the NEF, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter.
+Mathematically both approaches are equivalent.
+We set $\lambda = 1$ where not noted otherwise.
+As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
+Figure~\ref{fig:indacc} shows an example of the model dynamics.
 \begin{figure}
@@
         dimensions. The vector of inputs is given by (0.8, 0.7, 0.6).
+        \todo{Put next to (or below) first figure.}
     }\label{fig:indacc}
@@
 
-\subsection{Metrics}
+\subsection{Benchmarks}
 To test and compare the two WTA mechanisms we provide an input of $\rho_i 
 = u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
-$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
-$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
-loss of generality, the first state variable receives the strongest input and 
-all other state variables receive input that is smaller by $s$. We chose this 
-input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
-decrease and the effective number of choices to decide between would decrease  
-As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
-long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
-both WTA models we use 200 neurons for each dimensions. In the IA network this 
-are split as 150 neurons for each layer 1 population and 50 neurons for each 
-layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
+$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and $\eta_i$ Gaussian white noise with standard deviation $\sigma$.
+Thus, without loss of generality, the first state variable receives the strongest input and all other state variables receive input that is smaller by $s$.
+We chose this input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will decrease and the effective number of choices to decide between would decrease As $s \rightarrow 0$ the problem gets more difficult.
+We will use $u = 1$ as long as not indicated otherwise and set the number of dimension to $d = 10$.
+In both WTA models we use 200 neurons for each dimensions.
+In the IA network this are split as 150 neurons for each layer 1 population and 50 neurons for each layer 2 population.
+Further parameters are summarized in Table~\ref{tbl:params}.
 \begin{table}
@@
 
-To evaluate the two mechanisms on this input, we use a number of metrics. First 
-we determine whether the model is able to form a clear decision at all within 
-a second of simulated time. To count as a clear decision, at least one output 
-needs to stay above 0.15 for the time interval
-$]\SI{1}{\second}, \SI{2}{\second}]$. % chktex 10
-This lower bound was chosen to ensure that noise on a zero output is not 
-mistaken as a non-zero output.  Furthermore, we require that the largest output 
-will be the largest output for all of the time interval or in other words the 
-decision does not change during that time interval.
-
-This does not take into account whether the winning output actually corresponds 
-to the strongest input, but sometimes it can be more desirable to produce 
-a clear decision than actually finding the strongest input in all instances. In 
-other situations, though, the correctness of the decision might be of higher 
-importance. We consider a trial correct if the model forms a clear decision and 
-the largest output corresponds to the largest input. All remaining metrics will 
-be calculated on the subset of trials with a clear decision.
-
-The time it takes to form a decision can be relevant too.  We define the 
-decision time as how long it takes to fulfill the conditions of a clear 
-decision.
-
-These metrics cover the basic performance of the WTA mechanisms. When using 
-a WTA mechanism within larger cognitive models, the exact magnitude of the 
-outputs can be important. Ideally, the output would be 1 for the winner and zero 
-for all other outputs.\footnote{Technically, the winner output could be scaled 
-    to any magnitude. We use 1 here as it is most convenient to work with.} The 
-LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being 
-the largest input. We define the \emph{winner error} $E_1$ as the difference of 
-the winner output from $u$ for the LCA model, as the difference from 1 for the 
-IA model and, for both models, the \emph{runner-up error} $E_2$ as the 
-difference of second largest output from 
-0 (negative values treated as 0). We use the average output values of the time 
-  interval
+To evaluate the two mechanisms on this input, we use a number of separate metrics.
+First we determine whether the model is able to form a clear decision at all within a second of simulated time.
+To count as a clear decision, at least one output needs to stay above 0.15 for the time interval
+$[\SI{1}{\second}, \SI{2}{\second}]$. % chktex 10
+This lower bound was chosen to ensure that noise on a zero output is not mistaken as a non-zero output.
+Furthermore, we require that the largest output will be the largest output for all of the time interval or in other words the decision does not change during that time interval.
+This does not take into account whether the winning output actually corresponds to the strongest input, but sometimes it can be more desirable to produce a clear decision than actually finding the strongest input in all instances.
+In other situations, though, the correctness of the decision might be of higher importance.
+We consider a trial correct if the model forms a clear decision and the largest output corresponds to the largest input.
+All remaining metrics will be calculated on the subset of trials with a clear decision.
+The time it takes to form a decision can be relevant too.
+We define the decision time as how long it takes to fulfill the conditions of a clear decision.
+These metrics cover the basic performance of the WTA mechanisms.
+When using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
+Ideally, the output would be 1 for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled     to any magnitude.
+We use 1 here as it is most convenient to work with.} The LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being the largest input.
+We define the \emph{winner error} $E_1$ as the difference of the winner output from $u$ for the LCA model, as the difference from 1 for the IA model and, for both models, the \emph{runner-up error} $E_2$ as the difference of second largest output from 0 (negative values treated as 0).
+We use the average output values of the time   interval
  $]\SI{1}{\second}, \SI{2}{\second}]$ % chktex 10
 to calculate these error values as the values fluctuate over time.
-
-These two metrics only look at the final output averaged over time, but the 
-model can produce transient outputs before the final decision is achieved.  
-Within the context of a larger model, this can be a problem as the transient 
-output could already be interpreted as a decision. Thus, we define $E_{2,\max}$ 
+These two metrics only look at the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
+Within the context of a larger model, this can be a problem as the transient output could already be interpreted as a decision.
+Thus, we define $E_{2,\max}$ 
 as the highest output of a non-winning output during the whole simulation.
@@
 \section{Results}
-We find that the ability to reach a clear decision depends on the magnitude of 
-the highest input for both networks. This is not surprising. In the LCA model 
-the output magnitude will be determined by the input magnitude of the largest 
-input.  As such the largest input needs to be above 0.15 to fulfill the 
-requirements. For the independent accumulator model the input has to be large 
-enough to reach the integration threshold within the time limit. By increasing 
-the input scaling $\lambda$ or the time limit one could get a clear decision for 
-smaller inputs within the time limit. We further find that the IA model is 
-independent of the input noise and target separation for all tested parameters.  
+We find that the ability to reach a clear decision depends on the magnitude of the highest input for both networks.
+This is not surprising.
+In the LCA model the output magnitude will be determined by the input magnitude of the largest input.
+As such the largest input needs to be above 0.15 to fulfill the requirements.
+For the independent accumulator model the input has to be large enough to reach the integration threshold within the time limit.
+By increasing the input scaling $\lambda$ or the time limit one could get a clear decision for smaller inputs within the time limit.
+We further find that the IA model is independent of the input noise and target separation for all tested parameters.
 This is not the case for the LCA model as shown in Figure~\ref{fig:decisions} 
-where the fraction of trials without a clear decision increases with noise and 
-smaller target separation.
+where the fraction of trials without a clear decision increases with noise and smaller target separation.
 \begin{figure}
@@
 
-However, when considering the correctness of the decisions (see 
-Fig.~\ref{fig:correct}) the LCA model is doing better. We can alleviate that 
-difference to some degree by reducing the input scaling to $\lambda = 0.2$, but 
-perform still worse for some combinations of input noise and target separation 
-when staying below the time limit. This in some part due to a systematic bias 
-for certain dimensions introduced in the second layer of the IA model. In the 
-NEF the neuron gain and bias parameters are usually picked from random 
-distributions. As such the layer 2 populations will become active at slightly 
-different thresholds. By using identical layer 2 populations, i.e.~identical 
-gain and bias parameters for each population, this bias can be eliminated and 
-the IA model performs better than the LCA model in most instances.
+However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA model is doing better.
+We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but perform still worse for some combinations of input noise and target separation when staying below the time limit.
+This in some part due to a systematic bias for certain dimensions introduced in the second layer of the IA model.
+In the NEF the neuron gain and bias parameters are usually picked from random distributions.
+As such the layer 2 populations will become active at slightly different thresholds.
+By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA model performs better than the LCA model in most instances.
 \begin{figure*}
@@
 
-The time required to reach a decision in the LCA model depends mostly on the 
-target separation and amount of noise on the input (see Fig.~\ref{fig:time}), 
-the magnitude of the largest input is of minor influence. Also, the confidence 
-intervals indicate a larger variance in the decision times with less target 
-separation and more input noise. In contrast to that, in the IA model the scaled 
-magnitude of the largest input is the most important factor.  Depending on this 
-magnitude the network can either be faster or slower than the LCA network, but 
-it will need more time to achieve the same fraction of correct responses.  There 
-is also a slight influence of target separation and input noise with an 
-interaction of these two parameters.
+The time required to reach a decision in the LCA model depends mostly on the target separation and amount of noise on the input (see Fig.~\ref{fig:time}), 
+the magnitude of the largest input is of minor influence.
+Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
+In contrast to that, in the IA model the scaled magnitude of the largest input is the most important factor.
+Depending on this magnitude the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
+There is also a slight influence of target separation and input noise with an interaction of these two parameters.
 \begin{figure*}
@@
 
-The output of the IA model matches almost perfectly the specifications of 
-producing an output of 1 for the winner and 0 for all other dimensions.  This is 
-not the case for the LCA model (see Fig.~\ref{fig:error}).  For small target 
-separations the output of the winner will stay below $u$ and this will get worse 
-with increased noise. Furthermore, the LCA model will have residual outputs of 
-non-winning choices under noisy conditions and with small target separations.
+The output of the IA model matches almost perfectly the specifications of producing an output of 1 for the winner and 0 for all other dimensions.
+This is not the case for the LCA model (see Fig.~\ref{fig:error}).
+For small target separations the output of the winner will stay below $u$ and this will get worse with increased noise.
+Furthermore, the LCA model will have residual outputs of non-winning choices under noisy conditions and with small target separations.
 \begin{figure*}
@@
 
-Finally, looking at the transient responses both models might produce outputs of 
-non-winning choices (see Fig.~\ref{fig:transient}). For the LCA model these 
-increase with noise on the input and, for small target separation, can approach 
-the final output of the winning dimensions. For the IA model, transient outputs 
-are smaller in noisy conditions, but can be higher than for the LCA model in 
-less noisy conditions.  The magnitude of such transient responses is reduced by 
-decreasing the input scaling.
+Finally, looking at the transient responses both models might produce outputs of non-winning choices (see Fig.~\ref{fig:transient}).
+For the LCA model these increase with noise on the input and, for small target separation, can approach the final output of the winning dimensions.
+For the IA model, transient outputs are smaller in noisy conditions, but can be higher than for the LCA model in less noisy conditions.
+The magnitude of such transient responses is reduced by decreasing the input scaling.
 \begin{figure*}
@@
 \section{Discussion}
-We find neither of the two networks to perform better on all metrics, but rather 
-they are suited for slightly different things. The leaky, competing accumulator 
-model is better at quickly determining the correct winner. However, under noisy 
-conditions it can end up not producing a clear output at all and thus failing to 
-produce a decision.  The independent accumulator model might not be as quick or 
-find the correct winner as often, but given enough time it will eventually 
-arrive at a decision and produce a clear output.
-
-The LCA network is especially suited for situations where a decision needs to be 
-continuously adjusted. The prescribed dynamics essentially try to output what 
-the currently largest input is considering some smoothing over time. This makes 
-it quick to respond to changes of the input, but can also lead to random 
-switching outputs due to noise. In comparison, the IA model is more suited in 
-situations where a discrete sequence of decisions is required.  During the 
-initial phase the model will just integrate evidence without any output and 
-after making a decision, it is necessary to reset the model by inhibiting all 
-layer 1 neurons. This limits the how quickly successive decisions can be made, 
-but at the same time, once a decision is made, the network provides a stable 
-output.
-
-There are also certain considerations to be made when integrating these networks 
-into larger neural or cognitive models. This integration is easy for the IA 
-model as it provides a clear output. The output of the winning choice is also 
-always close to one, independent of the input, which makes it easy to detect 
-when the decision has been made and processing can continue. This is problematic 
-in the LCA model where we get a fluctuating output before the final decision and 
-the magnitude of the output depends on the input magnitude. This makes it 
-problematic to use a fixed threshold to detect the decision. Furthermore, 
-transient responses of non-winning dimensions can get close to the final output 
-of the winning dimension in the LCA model.
-
-Part of the reason why the independent accumulator model produces less correct 
-responses is the systematic bias introduced in the second layer. By eliminating 
-this bias through identical ensembles the correctness of the model is increased 
-considerably. However, this would require a very precise tuning of the neurons 
-that might not be biologically plausible.
-
-One critique of non-leaky accumulator models is that their ability to 
-discriminate the largest input increases indefinitely with time (TODO~ref) and 
-that there is no sensible stopping criterion. However, this assumes that the 
-time to reach a decision has no cost. If that time has a cost, the cost of 
-spending more time on the decision will at some point exceed the gain by making 
-a correct decision. Furthermore, this argument assumes integration with perfect 
-accuracy. But in a neural network resources are limited, as such the range and 
-accuracy of values that can be represented in a neural population is limited.  
+We find neither of the two networks to perform better on all benchmarks, but rather they are suited for slightly different purposes.
+The leaky, competing accumulator model is better at quickly determining the correct winner.
+However, under noisy conditions it can end up not producing a clear output at all and thus failing to produce a decision.
+The independent accumulator model might not be as quick or find the correct winner as often, but given enough time it will eventually arrive at a decision and produce a clear output.
+The LCA network is especially suited for situations where a decision needs to be continuously adjusted.
+The prescribed dynamics essentially try to output what the currently largest input is considering some smoothing over time.
+This makes it quick to respond to changes in the input, but can also lead to randomly switching outputs due to noise.
+In comparison, the IA model is better suited for situations where a discrete sequence of decisions is required.
+After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
+Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
+This limits how quickly successive decisions can be made.
+On the other hand, once a decision is made, the network provides a stable output.
+There are also certain considerations to be made when integrating these networks into larger neural or cognitive models.
+This integration is easy for the IA model as it provides a clear output.
+The output of the winning choice is also always close to one, independent of the input, which makes it easy to detect when the decision has been made and processing can continue.
+This is problematic in the LCA model where we get a fluctuating output before the final decision and the magnitude of the output depends on the input magnitude.
+This makes it problematic to use a fixed threshold to detect the decision.
+Furthermore, 
+transient responses of non-winning dimensions can get close to the final output of the winning dimension in the LCA model.
+Part of the reason why the independent accumulator model produces less correct responses is the systematic bias introduced in the second layer.
+By eliminating this bias through identical ensembles the correctness of the model is increased considerably.
+However, this would require a very precise tuning of the neurons that might not be biologically plausible.
+One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time (TODO~ref) and that there is no sensible stopping criterion.
+However, this assumes that the time to reach a decision has no cost.
+If that time has a cost, the cost of spending more time on the decision will at some point exceed the gain by making a correct decision.
+Furthermore, this argument assumes integration with perfect accuracy.
+But in a neural network resources are limited, as such the range and accuracy of values that can be represented in a neural population is limited.
 At some point this would counterbalance any additional evidence.
-
-We did not investigate the biological plausibility here because this has been 
-done before for different WTA networks.  Also, the implementation in spiking 
-neurons ensures a certain level of biological plausibility. We also did not look 
-at at the influence of the number of dimensions $d$ in detail, but qualitatively 
-the results will stay the same. For higher $d$, we expect less correct responses 
-as each additional dimensions adds a chance that this dimension will win out due 
-to noise.
-
+We did not investigate the biological plausibility here because this has been done before for different WTA networks.
+Also, the implementation in spiking neurons ensures a certain level of biological plausibility.
+We also did not look at at the influence of the number of dimensions $d$ in detail, but qualitatively the results will stay the same.
+For higher $d$, we expect less correct responses as each additional dimensions adds a chance that this dimension will win out due to noise.
 TODO\@: looking only at cases where a decision could be made within the results, 
@@
 \section{Notes}
-Simulation source code and additional analysis results are available at 
-\url{https://github.com/ctn-waterloo/cogsci17-decide}.  These have not been peer 
-reviewed.
+Simulation source code and additional analysis results are available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
+These have not been peer reviewed.
 
 \section{Acknowledgments}
-TODO anything missing here?
 This work was supported by the Canada Research Chairs program,
-the NSERC Discovery grant 261453, Air Force Office of Scientific Research grant 
-FA8655-13-1-3084, CFI and OIT\@.  % chktex 8
+the NSERC Discovery grant 261453, Air Force Office of Scientific Research grant FA8655-13-1-3084, CFI, OIT, and NSERC CGS-D\@.  % chktex 8
 

### 2017-01-20 doc/paper/paper.tex
Be precise about interval openness.

@@
 To count as a clear decision, at least one output needs to stay above 0.15 for the time interval
-$[\SI{1}{\second}, \SI{2}{\second}]$. % chktex 10
+$(\SI{1}{\second}, \SI{2}{\second}]$. % chktex 9
 This lower bound was chosen to ensure that noise on a zero output is not mistaken as a non-zero output.
@@
 We use the average output values of the time   interval
- $]\SI{1}{\second}, \SI{2}{\second}]$ % chktex 10
+ $(\SI{1}{\second}, \SI{2}{\second}]$ % chktex 9
 to calculate these error values as the values fluctuate over time.

### 2017-01-22 doc/paper/paper.tex
Finishing methods; edit consistency/simplicity throughout

@@
 \todo{Flesh this out a bit}
-We first provide a novel spiking implementation of the well-known leaky competing accumulator (LCA) model, by mapping its dynamics onto a population-level representation.
+We provide a novel spiking implementation of the well-known leaky, competing accumulator (LCA) model, by mapping the dynamics onto a population-level representation.
 We then propose a two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
@@
 \section{Introduction}
-Winner-take-all (WTA) mechanisms are often employed in cognitive models~\cite<e.g.,>{oreilly1998}.
-A WTA mechanism receives a $d$-dimensional input of utility values for $d$ different choices.
-The output is supposed to be larger than zero for the dimension with highest utility and zero for all other inputs.
-\todo{Say some obvious things, such as the role of WTA in decision making?}
+
+The winner-take-all (WTA) mechanism is a component that selects the largest value among a number of possible inputs.
+More specifically, the input is a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, and the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
+This mechanism is regularly employed in cognitive models of decision making, which must select the most important action to take at any given moment in time~\cite<e.g.,>{oreilly1998}. 
+\todo{Cite survey or cite other examples}
 
@@
 Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
-In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of benchmarks that
-are normative in nature.
-The first mechanism is an implementation of the leaky, competing accumulator model by~\citeA{usher2001}.
-It has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and some of our models~\cite<e.g.,>{kajic2017}.
-\todo{How does the latter implementation differ from the implementation here?}
-The second mechanism is our proposed independent accumulator (IA) model, which involves a second thresholding layer that is recurrently connected to a primary integrating layer.
-For both mechanisms we are interested in decision-making tasks involving more than two choices ($d > 2$). \todo{Misplaced sentence.}
+In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of benchmarks that are normative in nature.
+The first mechanism is an implementation of the {\it leaky, competing accumulator} (LCA) model by~\citeA{usher2001}.
+It has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in some of our models~\cite<e.g.,>{kajic2017}.
+\todo{Add sentence somewhere differentiating our implementation from the latter implementation}
+The second mechanism is our proposed {\it independent accumulator} (IA) model, which involves a second thresholding layer that is recurrently connected to a primary integrating layer.
+For both mechanisms we are interested in decision-making tasks involving more than two choices ($d > 2$).
+\todo{Misplaced sentence / unimportant here}
 
-To implement these models, we use the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} to map some prescribed dynamics onto populations of spiking neurons.
+To implement each model, we use the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} to map their dynamics onto populations of spiking neurons.
 The NEF has been used for a wide variety of models, including the largest functioning simulation of the human brain~\cite{eliasmith2012}.
-We first provide a short introduction to the NEF, and then describe the implementation of the two WTA mechanisms.
-We then describe our benchmarks, and discuss some resulting implications for cognitive modelling.
+We provide a short introduction to the NEF, describe our implementation of the two WTA mechanisms, present our benchmarks, and finally discuss some resulting implications for cognitive modelling.
 
@@
 
-\todo{Bold font for vectors}
-
 \subsection{The Neural Engineering Framework}
-We employ the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} which allows us to implement equations describing the model dynamics in spiking neural networks based on three principles: \emph{representation},
-\emph{transformation}, and \emph{dynamics}.
+The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method of mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
+We now summarize the relevant aspects of this framework, ordered by its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.
 
 \subsubsection{Principle 1: Representation}
-The representation of a value $x(t)$ with a population of neurons is defined by the encoding and decoding.
-The encoding converting the value $x$ into a spike train or instantaneous firing rate $a_i(t)$ for neuron $i$ is given by
+We define the representation of a scalar value $x(t)$ by an encoding and decoding with respect to some population of neurons.
+The encoding of $x(t)$ into a spike train $a_i(t)$ for neuron $i$ is given by:
 \begin{equation}
-    a_i(t) = G_i\left[\alpha_i x(t) + J_i^{\mathrm{bias}}\right]
+    a_i(t) = G_i\left[\alpha_i x(t) + J_i^{\mathrm{bias}}\right] ,
 \end{equation}
-where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current and $G_i$ is the neuron non-linearity.
-Here, we use spiking, leaky integrate-and-fire neurons as $G_i$.
-Decoding weights $d_i$ are used to decode a value $\hat x(t)$ from such a population of neurons with
+where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
+Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$.
+Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
 \begin{equation}
-    \hat x(t) = \sum_i d_i \left[a_i(t) * h(t)\right]
+    \hat x(t) = \sum_i d_i \left[(a_i * h)(t)\right] ,
 \end{equation}
-where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponential synaptic filter with time constant $\tau_{\mathrm{s}}$.
-The decoding weights are obtained with a least-squares optimization of the error $E_x = \abs{x     - \hat{x}}$.
-For the transmission of a value from one population to another, the connection weights are given by
+where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
+The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x     - \hat{x}}$.
+For the transmission of a value from one population to another, the connection weights are given by:
 \begin{equation}
@@
 By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} 
-= \abs{f(x) - \hat x}$ arbitrary linear and non-linear functions $f(x)$ can be approximated in the connections between neural populations.
+= \abs{f(x) - \hat x}$ arbitrary linear and nonlinear functions $f(x)$ can be approximated in the connections between neural populations.
 
 \subsubsection{Principle 3: Dynamics}
-TODO \subsection{Leaky, competing accumulator model}
+Given some nonlinear dynamics for the state variable $x(t)$:
+\begin{equation} \label{eqn:nonlinear-system}
+    \frac{\partial x}{\partial t} = g(x) ,
+\end{equation}
+we can map these dynamics onto a recurrent transformation, by harnessing the synaptic filter used in Principle 1.
+In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys (\ref{eqn:nonlinear-system}).
+
+\subsection{Leaky, competing accumulator model}
 We implement the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics for the state variables $x_i,\ i < N$, where $N$ is the number of choices, are given by:
+The dynamics for each state variable $x_i(t),\ i < d$, where $d$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
 \begin{equation} \label{eqn:usher-mcclelland}
     \begin{split}
-        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
-        x_i &\rightarrow \max(x_i, 0) ,
+        \frac{{\partial x}_i}{\partial t} = \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau}, \quad x_i &\ge 0,
     \end{split}
 \end{equation}
-where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time constant.
-We set $k = \beta = 1$, since this will guarantee that the winning state converges to the value of its input, while the losing states converge to zero.
+where $\rho_i$ is each external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time-constant.
+This model essentially integrates each input $\rho_i$ with a leak term ($- kx_i$), minus competition from every other variable ($\beta \sum_{j \neq i} x_j$).
+Supposing $\rho_i > \rho_j$ for all $j \ne i$, a WTA mechanism should indicate that $i$ is the winning choice.
+Setting $k = \beta = 1$ will guarantee that the winning state $x_i$ converges to the value of the largest input $\rho_i$, while the losing states $x_j$ ($j \ne i$) converge to zero.
 Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).
-Equation~\ref{eqn:usher-mcclelland} can easily be implemented with the NEF by using one population of neurons for each $x_i$.
-We believe this implementation to be novel as it it does not treat the $x_i$ as neural firing rates, rather the neural firing rates are weighted by the decoding weights to precisely implement the stated dynamics.
-As such the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
-This allows us to use biologically more realistic neurons while at the same time adhering to the dynamics prescribed by the model.
-Figure~\ref{fig:usher-mcclelland} shows an example output.
+
+We implement (\ref{eqn:usher-mcclelland}) with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
+By appropriately selecting the gain and bias parameters from Principle~1, we ensure that each state variable is rectified ($x_i \ge 0$) as required.
+We believe this implementation is novel as it it does not interpret each $x_i$ as a distinct neural firing rate, but rather as a population-level representation distributed across any number of spiking neurons.
+In effect, heterogeneous spike trains are weighted by optimal decoding weights to precisely implement the stated dynamics.
+%As such, the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
+This allows us to attain greater biological realism without altering the dynamics prescribed by (\ref{eqn:usher-mcclelland}).
+
 \begin{figure}
@@
     \includegraphics{figures/usher-mcclelland}
-    \caption{Example time course of the state variables in the leaky, competing 
-        accumulator model with three dimensions. The vector of inputs is given 
-        by $(0.8, 0.7, 0.6)$.}\label{fig:usher-mcclelland}
+    \caption{ \label{fig:usher-mcclelland}
+        Example time course of the state variables in the LCA network with three choices.
+        The vector of inputs is given by $(0.8, 0.7, 0.6)$.
+    }
 \end{figure}
@@
 To enable competition, we add a second thresholding layer that will project back to self-excite and mutually-inhibit the first layer.
-We now provide the details of each layer~(Fig.~\todo{network diagram}).
-The first layer consists of a separate integrator population (i.e., accumulator) for each input.
-The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
-From the second layer, we decode the shifted Heaviside function $\bar{x}_{2,i} = \Theta(x_{2,i} - \vartheta)$ where $\vartheta = 0.8$ is a threshold value controlling how much evidence needs to be accumulated to produce an output.
-The Heaviside decoded output of layer 2 projects back to layer 1 to add <<<<<<< HEAD
-$\bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$.
-For $\bar{\beta} = 2$ (see supplementary analysis), the correct choice will self-excite while all other state variables will be suppressed once one of the accumulators reaches the threshold $\vartheta$.
-The dynamics are described by the following equations:
+We now provide the details of each layer.
+\todo{Network diagram?}
+
+The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ i < d$.
+The second layer consists of independent, non-recurrent, populations that receive input from the first layer in a one-to-one fashion.
+From the second layer, we decode the function $\bar{x}_i := \Theta(x_i - \vartheta)$ where $\Theta$ is the Heaviside function, and $\vartheta = 0.8$ is a fixed threshold value that determines how much evidence needs to be accumulated to produce an output.
+The Heaviside decoded output of layer 2 projects back to layer 1 to add $\bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j$ to the input of $x_i$.
+Since intuitively the largest input will accumulate the fastest, once this reaches the threshold $\vartheta$ it will self-excite and inhibit all other state variables.
+Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
+This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}):
 \begin{equation}
     \begin{split}
-        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
-            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
-        x_{1,i} &\rightarrow \max(x_{1,i}, 0) .
+        \frac{{\partial x}_i}{\partial t} = \lambda \rho_i \frac{1}{\tau_1} + \left( 
+            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} , \quad x_i &\ge 0 .
     \end{split}
 \end{equation}
+We set $\lambda = 1$ to be consistent with the LCA model.
+% should we mention that we use Principle 3 to implement each integrator
+% should we say anything about how the thresholding population works?
 
-Instead of controlling the threshold $\vartheta$, in the context of the NEF, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter.
-Mathematically both approaches are equivalent.
-We set $\lambda = 1$ where not noted otherwise.
-As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
-Figure~\ref{fig:indacc} shows an example of the model dynamics.
+%Instead of controlling the threshold $\vartheta$, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter -- mathematically this is equivalent.
+% ^ this isn't quit equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
+% it would be equivalent to scale \tau_1 inversely with \lambda
+% also I think this point isn't too important?
+%As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
 \begin{figure}
@@
     \includegraphics{figures/indacc}
-    \caption{Example time course of the state variables $x_{1,i}$ and decoded 
-        output $\bar{x}_{2,i}$ in the independent accumulator model with three 
-        dimensions. The vector of inputs is given by (0.8, 0.7, 0.6).
+    \caption{ \label{fig:indacc}
+        Example time course of the state variables $x_i$ and decoded output $\bar{x}_i$ in the IA network with three choices.
+        The vector of inputs is given by (0.8, 0.7, 0.6).
         \todo{Put next to (or below) first figure.}
-    }\label{fig:indacc}
+    }
 \end{figure}
@@
 \subsection{Benchmarks}
-To test and compare the two WTA mechanisms we provide an input of $\rho_i 
-= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
-$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and $\eta_i$ Gaussian white noise with standard deviation $\sigma$.
-Thus, without loss of generality, the first state variable receives the strongest input and all other state variables receive input that is smaller by $s$.
-We chose this input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will decrease and the effective number of choices to decide between would decrease As $s \rightarrow 0$ the problem gets more difficult.
-We will use $u = 1$ as long as not indicated otherwise and set the number of dimension to $d = 10$.
-In both WTA models we use 200 neurons for each dimensions.
-In the IA network this are split as 150 neurons for each layer 1 population and 50 neurons for each layer 2 population.
-Further parameters are summarized in Table~\ref{tbl:params}.
+To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the strongest input, 
+$s > 0$ the target separation to all other inputs, $\delta$ the Kronecker delta, and $\eta_i$ Gaussian (white) noise with standard deviation $\sigma$.
+Thus, without loss of generality, the first state variable receives the strongest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
+We chose this input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will decrease and the effective number of choices to decide between would decrease.
+\todo{I don't understand the previous sentence}
+As $s \rightarrow 0$ the problem becomes more difficult.
+We will use $u = 1$ unless indicated otherwise, and set the number of choices to $d = 10$.
+In both WTA models we use 200 neurons per choice.
+In the IA network this is split into 150 neurons for each layer 1 population, and 50 neurons for each layer 2 population.
+All remaining network parameters are summarized in Table~\ref{tbl:params}.
 \begin{table}
@@
     \begin{tabular}{ll}
-        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
+        LCA time-constant & $\tau = \SI{0.1}{\second}$ \\
         LCA recurrent parameters & $k = \beta = 1$ \\
-        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
-        IA feed-back time constant & $\tau_2 = \SI{0.1}{\second}$ \\
+        IA accumulation time-constant & $\tau_1 = \SI{0.1}{\second}$ \\
+        IA feedback time-constant & $\tau_2 = \SI{0.1}{\second}$ \\
         IA threshold & $\vartheta = 0.8$ \\
         IA recurrent parameters & $\lambda = 1, \bar{\beta} = 2$ \\
-        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
+        Recurrent synaptic time-constant & $\tau_{\mathrm{s}} 
         = \SI{0.1}{\second}$ \\
-        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
+        Feed-forward synaptic time-constant & $\tau_{\mathrm{s}} 
         = \SI{0.005}{\second}$ \\
-        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
+        Output decoding synaptic time-constant & $\tau_{\mathrm{s}} 
         = \SI{0.01}{\second}$
@@
 To evaluate the two mechanisms on this input, we use a number of separate metrics.
-First we determine whether the model is able to form a clear decision at all within a second of simulated time.
-To count as a clear decision, at least one output needs to stay above 0.15 for the time interval
-$(\SI{1}{\second}, \SI{2}{\second}]$. % chktex 9
-This lower bound was chosen to ensure that noise on a zero output is not mistaken as a non-zero output.
-Furthermore, we require that the largest output will be the largest output for all of the time interval or in other words the decision does not change during that time interval.
-This does not take into account whether the winning output actually corresponds to the strongest input, but sometimes it can be more desirable to produce a clear decision than actually finding the strongest input in all instances.
-In other situations, though, the correctness of the decision might be of higher importance.
-We consider a trial correct if the model forms a clear decision and the largest output corresponds to the largest input.
-All remaining metrics will be calculated on the subset of trials with a clear decision.
-The time it takes to form a decision can be relevant too.
-We define the decision time as how long it takes to fulfill the conditions of a clear decision.
-These metrics cover the basic performance of the WTA mechanisms.
-When using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
-Ideally, the output would be 1 for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled     to any magnitude.
-We use 1 here as it is most convenient to work with.} The LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being the largest input.
-We define the \emph{winner error} $E_1$ as the difference of the winner output from $u$ for the LCA model, as the difference from 1 for the IA model and, for both models, the \emph{runner-up error} $E_2$ as the difference of second largest output from 0 (negative values treated as 0).
-We use the average output values of the time   interval
- $(\SI{1}{\second}, \SI{2}{\second}]$ % chktex 9
-to calculate these error values as the values fluctuate over time.
+First, we determine whether the model is able to form a clear decision at all within a second of simulated time.
+To be counted as `clear', at least one output must remain above 0.15 across the time interval $(\SI{1}{\second}, \SI{2}{\second}]$. % chktex 9
+This lower bound of 0.15 was chosen to ensure that noise on a zero output is not mistaken for a non-zero output.
+Note this requires that the decision does not change throughout the time interval.
+This does not take into account whether the winning output actually corresponds to the strongest input, but for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
+In other situations, though, the correctness of the decision may be of higher importance.
+Thus, we consider a trial `correct' if the model forms a clear decision, and the largest output corresponds to the true largest input.
+
+We now describe a number of metrics that will be calculated on the subset of trials that contain a clear decision.
+% The time it takes to form a decision can be relevant too.
+It is important to consider the speed at which the network can make decisions.
+We therefore define the `decision time' as the length of time it takes to fulfil the conditions of a clear decision.
+%These metrics cover the basic performance of the WTA mechanisms.
+Likewise, when using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
+Ideally, the output would be one for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled to any magnitude.
+We use $1$ for convenience.}
+\todo{Have you tried decoding a threshold (say $\Theta(x_i - 0.15)$) off the LCA network?}
+The LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being the largest input.
+We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
+We use the average output values of the time   interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).
 These two metrics only look at the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
 Within the context of a larger model, this can be a problem as the transient output could already be interpreted as a decision.
-Thus, we define $E_{2,\max}$ 
-as the highest output of a non-winning output during the whole simulation.
+Thus, we define $E_{2,\max}$ as the `highest output of a losing choice' during the whole simulation.
 
@@
 This is not surprising.
-In the LCA model the output magnitude will be determined by the input magnitude of the largest input.
-As such the largest input needs to be above 0.15 to fulfill the requirements.
-For the independent accumulator model the input has to be large enough to reach the integration threshold within the time limit.
+In the LCA network the output magnitude will be determined by the input magnitude of the largest input.
+As such the largest input needs to be above 0.15 to fulfil the requirements.
+For the IA network, the input has to be large enough to reach the integration threshold within the time limit.
 By increasing the input scaling $\lambda$ or the time limit one could get a clear decision for smaller inputs within the time limit.
-We further find that the IA model is independent of the input noise and target separation for all tested parameters.
-This is not the case for the LCA model as shown in Figure~\ref{fig:decisions} 
-where the fraction of trials without a clear decision increases with noise and smaller target separation.
+We further find that the IA network is independent of the input noise and target separation for all tested parameters.
+This is not the case for the LCA network where the fraction of trials without a clear decision increases with noise and smaller target separation (see Fig.~\ref{fig:decisions}).
 \begin{figure}
@@
     \includegraphics{figures/decisions}
-    \caption{Fraction of trials with a clear decision for different input noise 
-        standard deviations $\sigma$ and target separations $s$ for the LCA 
-        model. Error bars denote bootstrapped 95\% confidence intervals.  The 
-        grey horizontal line shows the optimum.}\label{fig:decisions}
+    \caption{ \label{fig:decisions}
+        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
+        Error bars denote bootstrapped 95\% confidence intervals.
+        The grey horizontal line shows the optimum.
+    }
 \end{figure}
 
-However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA model is doing better.
+However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network is doing better.
 We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but perform still worse for some combinations of input noise and target separation when staying below the time limit.
-This in some part due to a systematic bias for certain dimensions introduced in the second layer of the IA model.
+This in some part due to a systematic bias for certain choices introduced in the second layer of the IA network.
 In the NEF the neuron gain and bias parameters are usually picked from random distributions.
 As such the layer 2 populations will become active at slightly different thresholds.
-By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA model performs better than the LCA model in most instances.
+By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs better than the LCA network in most instances.
 \begin{figure*}
@@
     \includegraphics{figures/correct}
-    \caption{Fraction of correct trials for different input noise standard 
-        deviations $\sigma$, target separations $s$, and models.  Error bars 
-        denote bootstrapped 95\% confidence intervals. The grey horizontal line 
-        shows the optimum.}\label{fig:correct}
+    \caption{ \label{fig:correct}
+        Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
+        Error bars denote bootstrapped 95\% confidence intervals.
+        The grey horizontal line shows the optimum.
+    }
 \end{figure*}
 
-The time required to reach a decision in the LCA model depends mostly on the target separation and amount of noise on the input (see Fig.~\ref{fig:time}), 
-the magnitude of the largest input is of minor influence.
+The time required to reach a decision in the LCA network depends mostly on the target separation and amount of noise on the input (see Fig.~\ref{fig:time}), the magnitude of the largest input is of minor influence.
 Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
-In contrast to that, in the IA model the scaled magnitude of the largest input is the most important factor.
+In contrast to that, in the IA network the scaled magnitude of the largest input is the most important factor.
 Depending on this magnitude the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
@@
     \includegraphics{figures/time}
-    \caption{Mean decision times for different input noise standard deviations 
-        $\sigma$ and target separations $s$ for the LCA and IA model. For the IA 
-        model $u = 0.2$ is shown which shows the interaction of target 
-        separation and input noise most clearly. Error bars denote bootstrapped 
-        95\% confidence intervals.  The grey horizontal lines show the 
-        optimum.}\label{fig:time}
+    \caption{ \label{fig:time}
+        Mean decision times for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
+        For the IA network $u = 0.2$ is shown which shows the interaction of target separation and input noise most clearly.
+        Error bars denote bootstrapped 95\% confidence intervals.
+        The grey horizontal lines show the optimum.
+    }
 \end{figure*}
 
-The output of the IA model matches almost perfectly the specifications of producing an output of 1 for the winner and 0 for all other dimensions.
-This is not the case for the LCA model (see Fig.~\ref{fig:error}).
+The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices.
+This is not the case for the LCA network (see Fig.~\ref{fig:error}).
 For small target separations the output of the winner will stay below $u$ and this will get worse with increased noise.
-Furthermore, the LCA model will have residual outputs of non-winning choices under noisy conditions and with small target separations.
+Furthermore, the LCA network will have residual outputs of losing choices under noisy conditions and with small target separations.
 \begin{figure*}
@@
     \includegraphics{figures/error}
-    \caption{Error on outputs for different input noise standard deviations 
-        $\sigma$ and target separations $s$ for the LCA model.  Error bars 
-        denote bootstrapped 95\% confidence intervals. The grey horizontal lines 
-        show the optimum.}\label{fig:error}
+    \caption{ \label{fig:error}
+        Error on outputs for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
+        Error bars denote bootstrapped 95\% confidence intervals.
+        The grey horizontal lines show the optimum.
+    }
 \end{figure*}
 
-Finally, looking at the transient responses both models might produce outputs of non-winning choices (see Fig.~\ref{fig:transient}).
-For the LCA model these increase with noise on the input and, for small target separation, can approach the final output of the winning dimensions.
-For the IA model, transient outputs are smaller in noisy conditions, but can be higher than for the LCA model in less noisy conditions.
+Finally, looking at the transient responses both models might produce outputs of losing choices (see Fig.~\ref{fig:transient}).
+For the LCA network these increase with noise on the input and, for small target separation, can approach the final output of the winning choices.
+For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions.
 The magnitude of such transient responses is reduced by decreasing the input scaling.
@@
     \includegraphics{figures/transient}
-    \caption{Highest transient response of non-winning dimensions for different 
-        input noise standard deviations $\sigma$ and target separations $s$ for 
-        the LCA and IA model. Error bars denote bootstrapped 95\% confidence 
-        intervals. The grey horizontal lines show the 
-        optimum.}\label{fig:transient}
+    \caption{ \label{fig:transient}
+        Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
+        Error bars denote bootstrapped 95\% confidence intervals.
+        The grey horizontal lines show the optimum.
+    }
 \end{figure*}
@@
 \section{Discussion}
-We find neither of the two networks to perform better on all benchmarks, but rather they are suited for slightly different purposes.
-The leaky, competing accumulator model is better at quickly determining the correct winner.
-However, under noisy conditions it can end up not producing a clear output at all and thus failing to produce a decision.
-The independent accumulator model might not be as quick or find the correct winner as often, but given enough time it will eventually arrive at a decision and produce a clear output.
+We discover that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
+For instance, the LCA network determines the correct winner more quickly.
+However, under noisy conditions it may not produce a clear output at all, and thus fails to make a decision.
+The IA network might not be as quick or find the correct winner as often, but given enough time it will eventually arrive at a decision and produce a clear output.
 The LCA network is especially suited for situations where a decision needs to be continuously adjusted.
@@
 This makes it quick to respond to changes in the input, but can also lead to randomly switching outputs due to noise.
-In comparison, the IA model is better suited for situations where a discrete sequence of decisions is required.
+In comparison, the IA network is better suited for situations where a discrete sequence of decisions is required.
 After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
@@
 There are also certain considerations to be made when integrating these networks into larger neural or cognitive models.
-This integration is easy for the IA model as it provides a clear output.
+This integration is easy for the IA network as it provides a clear output.
 The output of the winning choice is also always close to one, independent of the input, which makes it easy to detect when the decision has been made and processing can continue.
-This is problematic in the LCA model where we get a fluctuating output before the final decision and the magnitude of the output depends on the input magnitude.
+This is problematic in the LCA network, where we get a fluctuating output before the final decision and the magnitude of the output depends on the input magnitude.
 This makes it problematic to use a fixed threshold to detect the decision.
-Furthermore, 
-transient responses of non-winning dimensions can get close to the final output of the winning dimension in the LCA model.
-Part of the reason why the independent accumulator model produces less correct responses is the systematic bias introduced in the second layer.
+Furthermore, transient responses of losing choices can get close to the final output of the winning choice in the LCA network.
+Part of the reason why the IA network produces less correct responses is the systematic bias introduced in the second layer.
 By eliminating this bias through identical ensembles the correctness of the model is increased considerably.
 However, this would require a very precise tuning of the neurons that might not be biologically plausible.
-One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time (TODO~ref) and that there is no sensible stopping criterion.
+One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time \todo{~ref} and that there is no sensible stopping criterion.
 However, this assumes that the time to reach a decision has no cost.
@@
 We also did not look at at the influence of the number of dimensions $d$ in detail, but qualitatively the results will stay the same.
-For higher $d$, we expect less correct responses as each additional dimensions adds a chance that this dimension will win out due to noise.
-TODO\@: looking only at cases where a decision could be made within the results, 
-include a number of parameters and github url.
+For higher $d$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
+\todo{looking only at cases where a decision could be made within the results, include a number of parameters and github url}
 
 \section{Notes}
-Simulation source code and additional analysis results are available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
-These have not been peer reviewed.
+Source code and supplementary analysis is available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
+%These have not been peer reviewed.
 

### 2017-01-22 doc/paper/supplementary.tex
Finishing methods; edit consistency/simplicity throughout

@@
         \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
-        x_i &\rightarrow \max(x_i, 0) .
+        x_i &\ge 0 .
     \end{split}
@@
 
-Setting $\beta = k = 1$, and defining $\chi := \sum_{j} x_j$, we rewrite the dynamics as:
+Setting $\beta = k = 1$, and defining $\chi := \sum_j x_j$, we rewrite the dynamics as:
 \begin{equation} \label{eq:um-special}
@@
         \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - \chi \right) \frac{1}{\tau} \\
-        x_i &\rightarrow \max(x_i, 0) .
+        x_i &\ge 0.
     \end{split}
@@
     \begin{split}
-        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
-            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
-        x_{1,i} &\rightarrow \max(x_{1,i}, 0) ,
+        \frac{{\partial x}_i}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
+            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} \\
+        x_i &\ge 0 ,
     \end{split}
 \end{equation}
-where $\bar{x}_{2, i} := \Theta(x_{2,i} - \vartheta)$ is defined by the Heaviside function shifted by $\vartheta$.
+where $\bar{x}_i := \Theta(x_i - \vartheta)$ is defined by the Heaviside function $\Theta$ shifted by $\vartheta$.
 We now justify our choice of $\bar{\beta} = 2$ from the text. % Fixing $\lambda = 1$, $\tau_1 = \tau_2$.
@@
 Suppose index $i$ is a loser.
-We know that $\bar{x}_{2,i} \le 1$, and $\sum_{j \ne i} \bar{x}_{2,j} \ge 1$, since the Heaviside is bounded above by 1, and some other $j \ne i$ has surpassed its threshold by becoming the winner.
+We know that $\bar{x}_i \le 1$, and $\sum_{j \ne i} \bar{x}_j \ge 1$, since the Heaviside is bounded above by 1, and some other $j \ne i$ has surpassed its threshold by becoming the winner.
 Thus,
 \begin{align}
- \frac{{\partial x}_{1,i}}{\partial t} \le \lambda \rho_i \frac{1}{\tau_1} + \left( 1 - \bar{\beta} \right) \frac{1}{\tau_2} < 0 \quad \iff \quad \bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1} ,
+ \frac{{\partial x}_i}{\partial t} \le \lambda \max_i\{\rho_i\} \frac{1}{\tau_1} + \left( 1 - \bar{\beta} \right) \frac{1}{\tau_2} < 0 \quad \iff \quad \bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1} ,
 \end{align}
-which implies that we must enforce the latter condition on $\bar{\beta}$ in order to ensure that all losers go to zero. 
-In the text, $\lambda = 1$, $\tau_1 = \tau_2$, and $\max_i\{\rho_i\} < 1$ $\implies \bar{\beta} = 2$ will suffice.
+which implies that it suffices to enforce the latter condition on $\bar{\beta}$ in order to ensure that all losers go to zero. 
+In the text, $\lambda = 1$, $\tau_1 = \tau_2$, and $\max_i\{\rho_i\} < 1$ $\implies \bar{\beta} = 2$ is sufficient.
 

### 2017-01-22 doc/paper/paper.tex
LaTeX consistency, and NEF sentence rewrite

@@
 The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method of mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
-We now summarize the relevant aspects of this framework, ordered by its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.
+We now describe the aspects of this framework that are relevant to this work, by summarizing its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.
 
@@
 \subsubsection{Principle 2: Transformation}
-By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} 
-= \abs{f(x) - \hat x}$ arbitrary linear and nonlinear functions $f(x)$ can be approximated in the connections between neural populations.
+By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} = \abs{f(x) - \hat x}$, arbitrary linear and nonlinear functions $f(x)$ can be approximated in the connections between neural populations.
 

### 2017-01-22 doc/paper/paper.tex
Intro iteration / fixup

@@
 
-The winner-take-all (WTA) mechanism is a component that selects the largest value among a number of possible inputs.
-More specifically, the input is a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, and the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
-This mechanism is regularly employed in cognitive models of decision making, which must select the most important action to take at any given moment in time~\cite<e.g.,>{oreilly1998}. 
+The winner-take-all (WTA) mechanism is a network that selects the largest value among a number of possible inputs.
+More precisely, given a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
+This mechanism is regularly employed as a component of cognitive models involving decision making, in which the most useful action is selected to drive behaviour~\cite<e.g.,>{oreilly1998}. 
 \todo{Cite survey or cite other examples}

### 2017-01-23 doc/paper/supplementary.tex
LaTeX consistency, and NEF sentence rewrite
Fix article.

--- 2017-01-20 doc/paper/supplementary.tex
@@
 When $k = 1$, this is commonly referred to as a first-order lowpass filter with time-constant $\tau$.
-This effect of this filter in the time-domain is a convolution with the exponentially decaying function $h(t) := \tau^{-1} \exp\left( -t / \tau \right)$.
+The effect of this filter in the time-domain is a convolution with the exponentially decaying function $h(t) := \tau^{-1} \exp\left( -t / \tau \right)$.
 More generally, when $k > 0$, this has the transfer function:

### 2017-01-23 doc/paper/supplementary.tex
Fix article.

--- 2017-01-22 doc/paper/supplementary.tex
@@
     \begin{split}
-        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
-        x_i &\ge 0 .
+        \frac{{\partial x}_i}{\partial t} = \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau}, \quad x_i \ge 0 .
     \end{split}
@@
     \begin{split}
-        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - \chi \right) \frac{1}{\tau} \\
-        x_i &\ge 0.
+        \frac{{\partial x}_i}{\partial t} = \left(\rho_i - \chi \right) \frac{1}{\tau}, \quad x_i \ge 0.
     \end{split}
@@
     \begin{split}
-        \frac{{\partial x}_i}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
-            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} \\
-        x_i &\ge 0 ,
+        \frac{{\partial x}_i}{\partial t} = \lambda \rho_i \frac{1}{\tau_1} + \left( 
+            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2}, \quad x_i \ge 0 ,
     \end{split}

### 2017-01-23 doc/paper/paper.tex
bunch of comments/edits

@@
 \todo{Flesh this out a bit}
-We provide a novel spiking implementation of the well-known leaky, competing accumulator (LCA) model, by mapping the dynamics onto a population-level representation.
-We then propose a two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
+Here we compare two biologically plausible, spiking neuron
+implementations of different WTA mechanisms. 
+We first provide a novel spiking implementation of the well-known leaky, competing accumulator (LCA) model, by mapping the dynamics onto a population-level representation.
+We then propose a new two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
 Our findings suggest that while the LCA network can rapidly adapt to new winners, the IA network is better suited for stable decision making in the presence of noise.
@@
 
-The winner-take-all (WTA) mechanism is a network that selects the largest value among a number of possible inputs.
+Winner-take-all (WTA) networks provide a mechanism that selects the largest value among a number of possible inputs.
 More precisely, given a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving decision making, in which the most useful action is selected to drive behaviour~\cite<e.g.,>{oreilly1998}. 
+This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{oreilly1998}.
 \todo{Cite survey or cite other examples}
@@
 Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
-In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of benchmarks that are normative in nature.
-The first mechanism is an implementation of the {\it leaky, competing accumulator} (LCA) model by~\citeA{usher2001}.
-It has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in some of our models~\cite<e.g.,>{kajic2017}.
-\todo{Add sentence somewhere differentiating our implementation from the latter implementation}
-The second mechanism is our proposed {\it independent accumulator} (IA) model, which involves a second thresholding layer that is recurrently connected to a primary integrating layer.
+In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
+The first mechanism we consider is an implementation of the {\it leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
+The LCA model has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test \todo{not sure this is the right paper} models~\cite<e.g.,>{kajic2017}.
+\todo{Add sentence somewhere differentiating our implementation from the latter implementation.  ce: only if it's fairly different}
+The second mechanism we consider is the {\it independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
+
 For both mechanisms we are interested in decision-making tasks involving more than two choices ($d > 2$).
-\todo{Misplaced sentence / unimportant here}
+\todo{Misplaced sentence / unimportant here...
+ce: or flesh this out; can we say more about the nature of the tasks we're looking at...
+d>2 and d<10?
+what kind of speed do we want, etc?
+or move this all later}
 
-To implement each model, we use the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} to map their dynamics onto populations of spiking neurons.
-The NEF has been used for a wide variety of models, including the largest functioning simulation of the human brain~\cite{eliasmith2012}.
-We provide a short introduction to the NEF, describe our implementation of the two WTA mechanisms, present our benchmarks, and finally discuss some resulting implications for cognitive modelling.
+To implement each model, we use the Neural Engineering Framework~\cite<NEF;>{eliasmith2003} to map the model's dynamics onto populations of spiking neurons.
+In the remainder of the paper, we provide a short introduction to the NEF, describe our implementation of the two WTA mechanisms, present our benchmarks, and finally discuss some resulting implications for cognitive modelling.
 
@@
 \begin{equation}
-    a_i(t) = G_i\left[\alpha_i x(t) + J_i^{\mathrm{bias}}\right] ,
+    a_i(t) = G_i\left[\alpha_i e x(t) + J_i^{\mathrm{bias}}\right] ,
 \end{equation}
-where $\alpha_i$ is a gain factor, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
-Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$.
+where $\alpha_i$ is a gain factor, $e$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
+Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and choose the encoders randomly.
 Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
@@
 \begin{equation}
-    W_{ij} = \alpha_j d_i \text{.}
+    W_{ij} = \alpha_j e_j d_i \text{.}
 \end{equation}
@@
 we can map these dynamics onto a recurrent transformation, by harnessing the synaptic filter used in Principle 1.
-In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys (\ref{eqn:nonlinear-system}).
+In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys Equation~\ref{eqn:nonlinear-system}.
 
 \subsection{Leaky, competing accumulator model}
-We implement the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics for each state variable $x_i(t),\ i < d$, where $d$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
+Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
+The dynamics for each state variable $x_i(t),\ i < D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 
-We implement (\ref{eqn:usher-mcclelland}) with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
+We implement Equation~\ref{eqn:usher-mcclelland} with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
 By appropriately selecting the gain and bias parameters from Principle~1, we ensure that each state variable is rectified ($x_i \ge 0$) as required.
-We believe this implementation is novel as it it does not interpret each $x_i$ as a distinct neural firing rate, but rather as a population-level representation distributed across any number of spiking neurons.
+We believe this implementation is novel as it does not interpret each $x_i$ as a distinct neural firing rate, but rather as a population-level representation distributed across any number of spiking neurons.
 In effect, heterogeneous spike trains are weighted by optimal decoding weights to precisely implement the stated dynamics.
@@
 This allows us to attain greater biological realism without altering the dynamics prescribed by (\ref{eqn:usher-mcclelland}).
+\todo{distributing the states across neurons would be yet another implementation; maybe worth mentioning in the discussion...as that might be even more bio-plausible}
 
@@
 The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model.
-We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator.
-To enable competition, we add a second thresholding layer that will project back to self-excite and mutually-inhibit the first layer.
+We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator, unlike in the LCA model which has direct competition between states.
+To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
 We now provide the details of each layer.
@@
 
-The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ i < d$.
-The second layer consists of independent, non-recurrent, populations that receive input from the first layer in a one-to-one fashion.
+The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ i < D$.
+The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
 From the second layer, we decode the function $\bar{x}_i := \Theta(x_i - \vartheta)$ where $\Theta$ is the Heaviside function, and $\vartheta = 0.8$ is a fixed threshold value that determines how much evidence needs to be accumulated to produce an output.
@@
 %Instead of controlling the threshold $\vartheta$, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter -- mathematically this is equivalent.
-% ^ this isn't quit equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
+% ^ this isn't quite equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
 % it would be equivalent to scale \tau_1 inversely with \lambda
@@
 To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the strongest input, 
-$s > 0$ the target separation to all other inputs, $\delta$ the Kronecker delta, and $\eta_i$ Gaussian (white) noise with standard deviation $\sigma$.
+$s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
 Thus, without loss of generality, the first state variable receives the strongest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
-We chose this input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will decrease and the effective number of choices to decide between would decrease.
-\todo{I don't understand the previous sentence}
-As $s \rightarrow 0$ the problem becomes more difficult.
-We will use $u = 1$ unless indicated otherwise, and set the number of choices to $d = 10$.
+We chose this input because, as $\rho_i \rightarrow 0$, the influence of input $\rho_i$ will decrease and the effective number of choices to decide between  decreases.
+\todo{I don't understand the previous sentence; ce: changed it a bit, but am also unsure}
+As $s \rightarrow 0$ the problem becomes more difficult because the utilities of the choices are closer together.
+We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
 In both WTA models we use 200 neurons per choice.
-In the IA network this is split into 150 neurons for each layer 1 population, and 50 neurons for each layer 2 population.
+In the IA network this is split into 150 neurons for each layer 1 population and 50 neurons for each layer 2 population.
 All remaining network parameters are summarized in Table~\ref{tbl:params}.
@@
 
-To evaluate the two mechanisms on this input, we use a number of separate metrics.
-First, we determine whether the model is able to form a clear decision at all within a second of simulated time.
+To evaluate the two mechanisms on the previously defined input, we use a number of separate metrics.
+First, we determine whether the model is able to form a clear decision within one second.
 To be counted as `clear', at least one output must remain above 0.15 across the time interval $(\SI{1}{\second}, \SI{2}{\second}]$. % chktex 9
 This lower bound of 0.15 was chosen to ensure that noise on a zero output is not mistaken for a non-zero output.
-Note this requires that the decision does not change throughout the time interval.
+Note that this metric requires that the decision does not change throughout the time interval.
 This does not take into account whether the winning output actually corresponds to the strongest input, but for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
@@
 \todo{Have you tried decoding a threshold (say $\Theta(x_i - 0.15)$) off the LCA network?}
-The LCA dynamics, however, prescribe an output of $u$ for the winner with $u$ being the largest input.
+The LCA dynamics, however, prescribe an output of $u$ for the winner, with $u$ being the largest input.
 We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
-We use the average output values of the time   interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).
-These two metrics only look at the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
-Within the context of a larger model, this can be a problem as the transient output could already be interpreted as a decision.
+We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).
+These two metrics only consider the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
+Within the context of a larger model, this can be a problem as the transient output could be prematurely interpreted as a decision.
 Thus, we define $E_{2,\max}$ as the `highest output of a losing choice' during the whole simulation.
@@
 For the IA network, the input has to be large enough to reach the integration threshold within the time limit.
-By increasing the input scaling $\lambda$ or the time limit one could get a clear decision for smaller inputs within the time limit.
-We further find that the IA network is independent of the input noise and target separation for all tested parameters.
+By increasing the input scaling $\lambda$, or the time limit, one could get a clear decision for smaller inputs within the time limit.
+We further find that the IA network is independent of the input noise and target separation for all tested parameters.\todo{but how does it do?
+can you put a single line on figure 3 to show it, so we can see the comparison to LCA?
+something visual would be good.}
 This is not the case for the LCA network where the fraction of trials without a clear decision increases with noise and smaller target separation (see Fig.~\ref{fig:decisions}).
@@
 
-However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network is doing better.
-We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but perform still worse for some combinations of input noise and target separation when staying below the time limit.
-This in some part due to a systematic bias for certain choices introduced in the second layer of the IA network.
+However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network does better with the default parameters.
+We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but the IA network still performs worse for some combinations of input noise and target separation when staying below the time limit.
+This is part due in part to a systematic bias for certain choices introduced in the second layer of the IA network.
 In the NEF the neuron gain and bias parameters are usually picked from random distributions.
@@
 By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs better than the LCA network in most instances.
+\todo{label fig 4 with a, b,c d and refer to those letters in the discussion above}
 \begin{figure*}
@@
 
-The time required to reach a decision in the LCA network depends mostly on the target separation and amount of noise on the input (see Fig.~\ref{fig:time}), the magnitude of the largest input is of minor influence.
+The time required to reach a decision in the LCA network depends mostly on the target separation and the amount of noise on the input (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}), the magnitude of the largest input is of minor influence.
 Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
@@
 
-The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices.
-This is not the case for the LCA network (see Fig.~\ref{fig:error}).
-For small target separations the output of the winner will stay below $u$ and this will get worse with increased noise.
+The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices \todo{a line on the LCA graph would help here too}.
+This is not the case for the LCA network (see Fig.~\ref{fig:error}\todo{again a and b}).
+For small target separations, the output of the winner will stay below $u$ and this will get worse with increased noise.
 Furthermore, the LCA network will have residual outputs of losing choices under noisy conditions and with small target separations.
@@
 \section{Discussion}
-We discover that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
+We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
 For instance, the LCA network determines the correct winner more quickly.
@@
 The IA network might not be as quick or find the correct winner as often, but given enough time it will eventually arrive at a decision and produce a clear output.
-The LCA network is especially suited for situations where a decision needs to be continuously adjusted.
-The prescribed dynamics essentially try to output what the currently largest input is considering some smoothing over time.
+
+Furthermore, the LCA network is especially well-suited for situations where a decision needs to be continuously adjusted.
+The prescribed dynamics essentially try to output whatever the currently largest input is, while performing some smoothing over time.
 This makes it quick to respond to changes in the input, but can also lead to randomly switching outputs due to noise.
-In comparison, the IA network is better suited for situations where a discrete sequence of decisions is required.
+
+In contrast, the IA network is better suited for situations where a discrete sequence of decisions is required.
 After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
@@
 On the other hand, once a decision is made, the network provides a stable output.
-There are also certain considerations to be made when integrating these networks into larger neural or cognitive models.
-This integration is easy for the IA network as it provides a clear output.
+
+When integrating these networks into larger neural or cognitive models, the two models present different challenges.
+This integration is simpler for the IA network because the IA network provides a clear output.
 The output of the winning choice is also always close to one, independent of the input, which makes it easy to detect when the decision has been made and processing can continue.
-This is problematic in the LCA network, where we get a fluctuating output before the final decision and the magnitude of the output depends on the input magnitude.
+In contrast, detecting a decision is more problematic in the LCA network, where  a fluctuating output is often generated before the final decision, and the magnitude of the output depends on the input magnitude.
 This makes it problematic to use a fixed threshold to detect the decision.
-Furthermore, transient responses of losing choices can get close to the final output of the winning choice in the LCA network.
+Furthermore, transient responses of losing choices can get close to the final output of the winning choice in the LCA network, making detection more difficult.
+
 Part of the reason why the IA network produces less correct responses is the systematic bias introduced in the second layer.
@@
 However, this would require a very precise tuning of the neurons that might not be biologically plausible.
+
 One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time \todo{~ref} and that there is no sensible stopping criterion.
 However, this assumes that the time to reach a decision has no cost.
-If that time has a cost, the cost of spending more time on the decision will at some point exceed the gain by making a correct decision.
+If time-to-decision has a cost, it will at some point exceed the gain achieved from making a correct decision.
 Furthermore, this argument assumes integration with perfect accuracy.
-But in a neural network resources are limited, as such the range and accuracy of values that can be represented in a neural population is limited.
+But in a neural network resources are limited. As such the range and accuracy of values that can be represented in a neural population is limited.
 At some point this would counterbalance any additional evidence.
-We did not investigate the biological plausibility here because this has been done before for different WTA networks.
+
+We did not investigate the biological plausibility of these mechanisms in detail because this has been done before for different WTA networks \todo{ref???}.
 Also, the implementation in spiking neurons ensures a certain level of biological plausibility.
-We also did not look at at the influence of the number of dimensions $d$ in detail, but qualitatively the results will stay the same.
-For higher $d$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
+We also did not look at at the influence of the number of dimensions $D$ in detail, but qualitatively the results will stay the same.
+For higher $D$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
 \todo{looking only at cases where a decision could be made within the results, include a number of parameters and github url}

### 2017-01-23 doc/paper/paper.tex
Use different style to refer to equations.
I prefer it, seems easier to read to me. But I could be swayed.

--- 2017-01-22 doc/paper/paper.tex
@@
 we can map these dynamics onto a recurrent transformation, by harnessing the synaptic filter used in Principle 1.
-In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys (\ref{eqn:nonlinear-system}).
+In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys Equation~\ref{eqn:nonlinear-system}.
 
@@
 
-We implement (\ref{eqn:usher-mcclelland}) with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
+We implement Equation~\ref{eqn:usher-mcclelland} with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
 By appropriately selecting the gain and bias parameters from Principle~1, we ensure that each state variable is rectified ($x_i \ge 0$) as required.
@@
 %As such, the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
-This allows us to attain greater biological realism without altering the dynamics prescribed by (\ref{eqn:usher-mcclelland}).
+This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
 

### 2017-01-24 doc/paper/paper.tex
Change equation reference.
Edit IA model description.

--- 2017-01-23 doc/paper/paper.tex
@@
 %As such, the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
-This allows us to attain greater biological realism without altering the dynamics prescribed by (\ref{eqn:usher-mcclelland}).
+This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
 \todo{distributing the states across neurons would be yet another implementation; maybe worth mentioning in the discussion...as that might be even more bio-plausible}
@@
 To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
-We now provide the details of each layer.
+We now provide the details of each layer, again implemented with the principles of the NEF.
 \todo{Network diagram?}
@@
     \begin{split}
-        \frac{{\partial x}_i}{\partial t} = \lambda \rho_i \frac{1}{\tau_1} + \left( 
+        \frac{{\partial x}_i}{\partial t} = \rho_i \frac{1}{\tau_1} + \left( 
             \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} , \quad x_i &\ge 0 .
@@
 \end{equation}
-We set $\lambda = 1$ to be consistent with the LCA model.
-% should we mention that we use Principle 3 to implement each integrator
 % should we say anything about how the thresholding population works?

### 2017-01-24 doc/paper/paper.tex
Edit input description.

@@
 Thus, without loss of generality, the first state variable receives the strongest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
-We chose this input because, as $\rho_i \rightarrow 0$, the influence of input $\rho_i$ will decrease and the effective number of choices to decide between  decreases.
-\todo{I don't understand the previous sentence; ce: changed it a bit, but am also unsure}
+Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
 As $s \rightarrow 0$ the problem becomes more difficult because the utilities of the choices are closer together.
 We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
+Further, we chose noise variance increments large enough to observe how the networks start to fail performing their task.
 In both WTA models we use 200 neurons per choice.

### 2017-01-24 doc/paper/paper.tex
Fix italics.

@@
 In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
-The first mechanism we consider is an implementation of the {\it leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
+The first mechanism we consider is an implementation of the \emph{leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
 The LCA model has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test \todo{not sure this is the right paper} models~\cite<e.g.,>{kajic2017}.
 \todo{Add sentence somewhere differentiating our implementation from the latter implementation.  ce: only if it's fairly different}
-The second mechanism we consider is the {\it independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
+The second mechanism we consider is the \emph{independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
 

### 2017-01-24 doc/paper/paper.tex
Fix misplaced figure label commands.

@@
     \includegraphics{figures/usher-mcclelland}
-    \caption{ \label{fig:usher-mcclelland}
+    \caption{
         Example time course of the state variables in the LCA network with three choices.
         The vector of inputs is given by $(0.8, 0.7, 0.6)$.
-    }
+    }\label{fig:usher-mcclelland}
 \end{figure}
@@
     \includegraphics{figures/indacc}
-    \caption{ \label{fig:indacc}
+    \caption{
         Example time course of the state variables $x_i$ and decoded output $\bar{x}_i$ in the IA network with three choices.
@@
         \todo{Put next to (or below) first figure.}
-    }
+    }\label{fig:indacc}
 \end{figure}
@@
     \includegraphics{figures/decisions}
-    \caption{ \label{fig:decisions}
+    \caption{
         Fraction of trials with a clear decision for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
@@
         The grey horizontal line shows the optimum.
-    }
+    }\label{fig:decisions}
 \end{figure}
@@
     \includegraphics{figures/correct}
-    \caption{ \label{fig:correct}
+    \caption{
         Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
@@
         The grey horizontal line shows the optimum.
-    }
+    }\label{fig:correct}
 \end{figure*}
@@
     \includegraphics{figures/time}
-    \caption{ \label{fig:time}
+    \caption{
         Mean decision times for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
@@
         The grey horizontal lines show the optimum.
-    }
+    }\label{fig:time}
 \end{figure*}
@@
     \includegraphics{figures/error}
-    \caption{ \label{fig:error}
+    \caption{
         Error on outputs for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
@@
         The grey horizontal lines show the optimum.
-    }
+    }\label{fig:error}
 \end{figure*}
@@
     \includegraphics{figures/transient}
-    \caption{ \label{fig:transient}
+    \caption{
         Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
@@
         The grey horizontal lines show the optimum.
-    }
+    }\label{fig:transient}
 \end{figure*}

### 2017-01-24 doc/paper/paper.tex
Fix chktex warnings.

@@
 To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
-We now provide the details of each layer, again implemented with the principles of the NEF.
+We now provide the details of each layer, again implemented with the principles of the NEF\@.
 \todo{Network diagram?}
@@
 We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
-We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).
+We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).  % chktex 9
 These two metrics only consider the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.

### 2017-01-24 doc/paper/paper.tex
Fix encoder index.

@@
 \begin{equation}
-    a_i(t) = G_i\left[\alpha_i e x(t) + J_i^{\mathrm{bias}}\right] ,
+    a_i(t) = G_i\left[\alpha_i e_i x(t) + J_i^{\mathrm{bias}}\right] ,
 \end{equation}
-where $\alpha_i$ is a gain factor, $e$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
+where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
 Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and choose the encoders randomly.

### 2017-01-24 doc/paper/paper.tex
Rewriting for new results.
I still need to include the new plots. Also the paragraph about
timing still needs some adjustments.

@@
 This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
-\todo{distributing the states across neurons would be yet another implementation; maybe worth mentioning in the discussion...as that might be even more bio-plausible}
 
@@
 \end{equation}
+Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence will be integrated.
+Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which is equivalent due to the leak-free integration.
 % should we say anything about how the thresholding population works?
@@
 First, we determine whether the model is able to form a clear decision within one second.
-To be counted as `clear', at least one output must remain above 0.15 across the time interval $(\SI{1}{\second}, \SI{2}{\second}]$. % chktex 9
+To be counted as `clear', at least one output must remain above 0.15 across the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ while all other outputs remain below this threshold. % chktex 9
 This lower bound of 0.15 was chosen to ensure that noise on a zero output is not mistaken for a non-zero output.
@@
 
-We now describe a number of metrics that will be calculated on the subset of trials that contain a clear decision.
-% The time it takes to form a decision can be relevant too.
-It is important to consider the speed at which the network can make decisions.
+We use two additional benchmarks on the set of all trials with a clear decision.
+First, it is important to consider the speed at which the network can make decisions.
 We therefore define the `decision time' as the length of time it takes to fulfil the conditions of a clear decision.
-%These metrics cover the basic performance of the WTA mechanisms.
-Likewise, when using a WTA mechanism within larger cognitive models, the exact magnitude of the outputs can be important.
-Ideally, the output would be one for the winner and zero for all other outputs.\footnote{Technically, the winner output could be scaled to any magnitude.
-We use $1$ for convenience.}
-\todo{Have you tried decoding a threshold (say $\Theta(x_i - 0.15)$) off the LCA network?}
-The LCA dynamics, however, prescribe an output of $u$ for the winner, with $u$ being the largest input.
-We define the `winner error' $E_1$ as the difference of the winner output from $u$ for the LCA network, as the difference from one for the IA network and, for both models, the `runner-up error' $E_2$ as the difference of second largest output from zero (with negative values treated as zero).
-We use the average output values over the time interval $(\SI{1}{\second}, \SI{2}{\second}]$ to calculate these error values (since these values fluctuate over time).  % chktex 9
-These two metrics only consider the final output averaged over time, but the model can produce transient outputs before the final decision is achieved.
-Within the context of a larger model, this can be a problem as the transient output could be prematurely interpreted as a decision.
-Thus, we define $E_{2,\max}$ as the `highest output of a losing choice' during the whole simulation.
+Second, the correctness metric only considers the final averaged output during a time interval.
+It is possible for a network to produce transient outputs before the final decision is reached.
+In the context of a larger model, this can become a problem because the transient output might be prematurely interpreted as a decision.
+Thus, we define $E_{\max}$ as the `highest output of a losing choice' during the whole simulation.
 
 \section{Results}
-We find that the ability to reach a clear decision depends on the magnitude of the highest input for both networks.
-This is not surprising.
-In the LCA network the output magnitude will be determined by the input magnitude of the largest input.
-As such the largest input needs to be above 0.15 to fulfil the requirements.
-For the IA network, the input has to be large enough to reach the integration threshold within the time limit.
-By increasing the input scaling $\lambda$, or the time limit, one could get a clear decision for smaller inputs within the time limit.
-We further find that the IA network is independent of the input noise and target separation for all tested parameters.\todo{but how does it do?
-can you put a single line on figure 3 to show it, so we can see the comparison to LCA?
-something visual would be good.}
-This is not the case for the LCA network where the fraction of trials without a clear decision increases with noise and smaller target separation (see Fig.~\ref{fig:decisions}).
+We find that the ability to form a clear decision of the LCA network decreases with more noise and less target separation (see Fig.~\ref{fig:decisions}).
+The best performance is achieved with a medium baseline of $u=0.6$.
+A higher baseline makes it more likely that runner-ups will exceed the 0.15 threshold, especially wit ha small target separation.
+With a small baseline, on the other hand, even the winner can be unable to exceed the threshold in the presence of noise.
+In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points fall on the grey line).
 \begin{figure}
@@
 
-However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network does better with the default parameters.
-We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but the IA network still performs worse for some combinations of input noise and target separation when staying below the time limit.
-This is part due in part to a systematic bias for certain choices introduced in the second layer of the IA network.
+Interestingly, in 99.97\% of successful decisions, the correct winner was determined by the LCA network.
+Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
+While always reaching a decision, the decisions of the IA network are not always correct (see Fig.~\ref{fig:correct}).
+Overall, the IA performance tends to worse for a high baseline, but better for a low baseline.
+We can greatly improve the IA performance by increasing $\tau_1$ which effectively adjusts the threshold $\vartheta$.
+This will, however, make the network slower to decide.
+A further improvement is possible by eliminating a systematic bias introduced in the second layer of the IA network.
 In the NEF the neuron gain and bias parameters are usually picked from random distributions.
 As such the layer 2 populations will become active at slightly different thresholds.
-By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs better than the LCA network in most instances.
+By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better.
 \todo{label fig 4 with a, b,c d and refer to those letters in the discussion above}
@@
 
-The time required to reach a decision in the LCA network depends mostly on the target separation and the amount of noise on the input (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}), the magnitude of the largest input is of minor influence.
-Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
-In contrast to that, in the IA network the scaled magnitude of the largest input is the most important factor.
-Depending on this magnitude the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
+The time required to reach a decision in the LCA network depends mostly on the baseline and target separation (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}).
+Similarly, in the IA network the magnitude of the largest input is also the most important factor.
+Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
 There is also a slight influence of target separation and input noise with an interaction of these two parameters.
+\todo{this might need some rewriting given new results}
 \begin{figure*}
@@
     }\label{fig:time}
-\end{figure*}
-
-The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices \todo{a line on the LCA graph would help here too}.
-This is not the case for the LCA network (see Fig.~\ref{fig:error}\todo{again a and b}).
-For small target separations, the output of the winner will stay below $u$ and this will get worse with increased noise.
-Furthermore, the LCA network will have residual outputs of losing choices under noisy conditions and with small target separations.
-\begin{figure*}
-    \centering
-    \includegraphics{figures/error}
-    \caption{
-        Error on outputs for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
-        Error bars denote bootstrapped 95\% confidence intervals.
-        The grey horizontal lines show the optimum.
-    }\label{fig:error}
 \end{figure*}
@@
 We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
-For instance, the LCA network determines the correct winner more quickly.
-However, under noisy conditions it may not produce a clear output at all, and thus fails to make a decision.
-The IA network might not be as quick or find the correct winner as often, but given enough time it will eventually arrive at a decision and produce a clear output.
+For instance, the LCA network determines the correct winner more quickly and given a conclusive decision was made it is almost always the correct decision.
+However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
+This can be problematic in situations were it is better or required to make a decision even though it might not be the best choice.
+The IA network might not be as quick or find the correct winner as often depending on the choice of $\tau_1$, but given enough time it will eventually arrive at a decision and produce a clear output.
 
@@
 
-When integrating these networks into larger neural or cognitive models, the two models present different challenges.
-This integration is simpler for the IA network because the IA network provides a clear output.
-The output of the winning choice is also always close to one, independent of the input, which makes it easy to detect when the decision has been made and processing can continue.
-In contrast, detecting a decision is more problematic in the LCA network, where  a fluctuating output is often generated before the final decision, and the magnitude of the output depends on the input magnitude.
-This makes it problematic to use a fixed threshold to detect the decision.
-Furthermore, transient responses of losing choices can get close to the final output of the winning choice in the LCA network, making detection more difficult.
+Both models might produce a transient response that can be problematic in detecting when the decision has been made as it might be interpreted as the decision.
+This is of special relevance when integrating the networks in larger cognitive models.
+For the LCA network this behaviour is inherent.
+There will always be an initial rise of all state variables that receive input before the mutual inhibition grows strong enough to push them back to zero.
+In the IA network, however, this is mostly a matter of choosing an appropriate $\tau_1$.
 
@@
 However, this would require a very precise tuning of the neurons that might not be biologically plausible.
+
+Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.
+This is directly supported by the NEF, but we chose to leave this to future work to keep the current analysis free from potential interactions of the state variables introduced by such a distributed representation.
+
+It is worth to highlight, that one can transform one model into the other with a few steps.
+By setting $\tau = \tau_1$, $k = -\tau/\tau_2$, and $\beta = \bar{\beta}\tau/\tau_2$ we obtain almost identical model equations.
+The only remaining difference is the added Heaviside non-linearity on the state variables.
+Nevertheless, the behaviour of the two models is quite distinct.
 
@@
 For higher $D$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
-\todo{looking only at cases where a decision could be made within the results, include a number of parameters and github url}
 

### 2017-01-24 doc/paper/paper.tex
Be more explicit about range of indices.

@@
 Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics for each state variable $x_i(t),\ i < D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
+The dynamics for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 
-The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ i < D$.
+The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
 The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.

### 2017-01-25 cogsci17_decide/trial.py
Update decision/correctness metrics.
Also remove winner_err and runnerup_err.

@@ -59,18 +59,18 @@ class DecisionTrial(pytry.NengoTrial):
         if runnerup >= winner:
             runnerup += 1
 
+        threshold = 0.15
         decided = (
-            np.all(ss_data[:, winner] > 0.2) and
-            np.all(ss_data[:, winner] - ss_data[:, runnerup] > 0.))
+            np.all(ss_data[:, winner] > threshold) and
+            np.all(ss_data[:, runnerup] <= threshold))
         correct = decided and np.all(np.argmax(ss_data, axis=1) == 0)
         t = np.nan
         if decided:
             risen = np.flatnonzero(
-                sim.data[self.probe][:, winner] > .15)
+                sim.data[self.probe][:, winner] > threshold)
             if len(risen) > 0:
                 fall = np.flatnonzero(
-                    sim.data[self.probe][:, winner] -
-                    np.max(sim.data[self.probe], axis=1) < .0)
+                    np.max(sim.data[self.probe], axis=1) <= threshold)
                 idx = risen[0]
                 if np.any(fall > idx):
                     idx = fall[-1]
@@ -83,7 +83,5 @@ class DecisionTrial(pytry.NengoTrial):
             decided=decided,
             correct=correct,
             t=t,
-            winner_err=np.max(smoothed) - 1.,
-            runnerup_err=max(0., np.max(smoothed[mask])),
             runnerup_highest_err=max(0., np.max(sim.data[self.probe][:, mask]))
         )

### 2017-01-25 doc/paper/paper.tex
Add IA network sketch.
fixup! Add IA network sketch.

@@
 \subsection{Independent accumulator model}
-The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model.
+The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model (Figure~\ref{fig:ia-sketch}).
 We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator, unlike in the LCA model which has direct competition between states.
@@
 We now provide the details of each layer, again implemented with the principles of the NEF\@.
-\todo{Network diagram?}
+\begin{figure}
+    \centering
+    \includegraphics{figures/ia-sketch}
+    \caption{\todo{caption}}\label{fig:ia-sketch}
+\end{figure}
 

### 2017-01-26 doc/paper/paper.tex
Add new plots.
Edits to results and discussion.

@@
 Further, we chose noise variance increments large enough to observe how the networks start to fail performing their task.
+This allows us to figure out which functions are performed more robustly by each network.
 In both WTA models we use 200 neurons per choice.
@@
 We find that the ability to form a clear decision of the LCA network decreases with more noise and less target separation  (see Fig.~\ref{fig:decisions}).
+Also, the baseline has an important influence.
+For a small baseline of $u=0.2$ the winner will mostly not exceed the 0.15 threshold with noise present.
 The best performance is achieved with a medium baseline of $u=0.6$.
-A higher baseline makes it more likely that runner-ups will exceed the 0.15 threshold, especially wit ha small target separation.
-With a small baseline, on the other hand, even the winner can be unable to exceed the threshold in the presence of noise.
+A higher baseline makes it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
 In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points fall on the grey line).
-\begin{figure}
+\begin{figure*}
     \centering
@@
     \caption{
-        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
+        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$, target separations $s$, and input baselines $u$ for the LCA network.
         Error bars denote bootstrapped 95\% confidence intervals.
         The grey horizontal line shows the optimum.
+        It coincides with the performance of the IA network.
     }\label{fig:decisions}
-\end{figure}
+\end{figure*}
 
-Interestingly, in 99.97\% of successful decisions, the correct winner was determined by the LCA network.
+Interestingly, for all successful decisions the correct winner was determined by the LCA network.
 Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
 While always reaching a decision, the decisions of the IA network are not always correct (see Fig.~\ref{fig:correct}).
-Overall, the IA performance tends to worse for a high baseline, but better for a low baseline.
-We can greatly improve the IA performance by increasing $\tau_1$ which effectively adjusts the threshold $\vartheta$.
-This will, however, make the network slower to decide.
-A further improvement is possible by eliminating a systematic bias introduced in the second layer of the IA network.
+Overall, the IA performance tends to be worse for a high baseline, but better for a low baseline (Fig.~\ref{fig:correct}a,b).
+We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which effectively adjusts the threshold $\vartheta$ (Fig.~\ref{fig:correct}c).
+This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
+For a low baseline of $u=0.2$ this makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
+A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
 In the NEF the neuron gain and bias parameters are usually picked from random distributions.
 As such the layer 2 populations will become active at slightly different thresholds.
-By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better.
-\todo{label fig 4 with a, b,c d and refer to those letters in the discussion above}
+By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
 \begin{figure*}
@@
 
-The time required to reach a decision in the LCA network depends mostly on the baseline and target separation (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}).
-Similarly, in the IA network the magnitude of the largest input is also the most important factor.
+The time required to reach a decision in the LCA network depends mostly on the baseline and target separation (see Fig.~\ref{fig:time}a).
+The level of noise only had a minor influence and was averaged over.
+Similarly, in the IA network the baseline is also the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
 Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
-There is also a slight influence of target separation and input noise with an interaction of these two parameters.
-\todo{this might need some rewriting given new results}
+There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
 \begin{figure*}
@@
     \caption{
-        Mean decision times for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
-        For the IA network $u = 0.2$ is shown which shows the interaction of target separation and input noise most clearly.
+        (a) Mean decision times for different baselines $u$ and target separations $s$ for the LCA.
+        (b) For the IA network $u = 0.2$ (solid) and $u = 1.0$ (dashed) are shown for different noise standard deviations $s$ and target separations $s$.
         Error bars denote bootstrapped 95\% confidence intervals.
-        The grey horizontal lines show the optimum.
     }\label{fig:time}
@@
 Finally, looking at the transient responses both models might produce outputs of losing choices (see Fig.~\ref{fig:transient}).
-For the LCA network these increase with noise on the input and, for small target separation, can approach the final output of the winning choices.
-For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions.
-The magnitude of such transient responses is reduced by decreasing the input scaling.
+For the LCA network the magnitude of the transient response mainly increases with the amount of noise (Fig.~\ref{fig:transient}a).
+For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions with small target separations.
+The magnitude of such transient responses is reduced by decreasing by adjusting $\tau_1$ to 0.5.
 \begin{figure*}
@@
 We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
-For instance, the LCA network determines the correct winner more quickly and given a conclusive decision was made it is almost always the correct decision.
+For instance, the LCA network can determine the correct winner more quickly and given a conclusive decision was made, it is always picks the correct winner.
 However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
 This can be problematic in situations were it is better or required to make a decision even though it might not be the best choice.
-The IA network might not be as quick or find the correct winner as often depending on the choice of $\tau_1$, but given enough time it will eventually arrive at a decision and produce a clear output.
+The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
 

### 2017-01-26 doc/paper/paper.tex
Address remaining inline todos.

@@
 The winner-take-all (WTA) mechanism is an important component of many cognitive models.
-\todo{Flesh this out a bit}
+For example, it can be used to decide among multiple choices or direct attention to important parts of a visual scene.
 Here we compare two biologically plausible, spiking neuron
@@
 More precisely, given a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{oreilly1998}.
-\todo{Cite survey or cite other examples}
+This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{itti1998,standage2005}.
 
@@
 The first mechanism we consider is an implementation of the \emph{leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
-The LCA model has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test \todo{not sure this is the right paper} models~\cite<e.g.,>{kajic2017}.
-\todo{Add sentence somewhere differentiating our implementation from the latter implementation.  ce: only if it's fairly different}
+The LCA model and variants have been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test models~\cite<e.g.,>{kajic2017}.
 The second mechanism we consider is the \emph{independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
-
-For both mechanisms we are interested in decision-making tasks involving more than two choices ($d > 2$).
-\todo{Misplaced sentence / unimportant here...
-ce: or flesh this out; can we say more about the nature of the tasks we're looking at...
-d>2 and d<10?
-what kind of speed do we want, etc?
-or move this all later}
 
@@
 Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
+The dynamics for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}a):
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
-
-\begin{figure}
+\begin{figure}[t]
     \centering
-    \includegraphics{figures/usher-mcclelland}
+    \includegraphics{figures/usher-mcclelland}\\
+    \vspace*{.3cm}
+    \includegraphics{figures/indacc}
     \caption{
@@
         The vector of inputs is given by $(0.8, 0.7, 0.6)$.
-    }\label{fig:usher-mcclelland}
+    }\label{fig:usher-mcclelland}\label{fig:indacc}
 \end{figure}
@@
     \includegraphics{figures/ia-sketch}
-    \caption{\todo{caption}}\label{fig:ia-sketch}
+    \caption{
+        Independent accumulator network.
+        Neural populations are denoted by circles labeled with their represented state variable.
+        Arrows denote excitatory connections, while lines ending in circles denote inhibitory connections.
+    }\label{fig:ia-sketch}
 \end{figure}
@@
 Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
-This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}):
+This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}b):
 \begin{equation}
@@
 % should we say anything about how the thresholding population works?
-
-%Instead of controlling the threshold $\vartheta$, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter -- mathematically this is equivalent.
-% ^ this isn't quite equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
-% it would be equivalent to scale \tau_1 inversely with \lambda
-% also I think this point isn't too important?
-%As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
-\begin{figure}
-    \centering
-    \includegraphics{figures/indacc}
-    \caption{
-        Example time course of the state variables $x_i$ and decoded output $\bar{x}_i$ in the IA network with three choices.
-        The vector of inputs is given by (0.8, 0.7, 0.6).
-        \todo{Put next to (or below) first figure.}
-    }\label{fig:indacc}
-\end{figure}
 
@@
 
-One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time \todo{~ref} and that there is no sensible stopping criterion.
+One critique of non-leaky accumulator models is that their ability to discriminate the largest input increases indefinitely with time~\cite{usher2001} and that there is no sensible stopping criterion.
 However, this assumes that the time to reach a decision has no cost.
@@
 
-We did not investigate the biological plausibility of these mechanisms in detail because this has been done before for different WTA networks \todo{ref???}.
+We did not investigate the biological plausibility of these mechanisms in detail because this has been done before for different WTA networks~\cite{gold2007,smith2004}.
 Also, the implementation in spiking neurons ensures a certain level of biological plausibility.

### 2017-01-26 doc/paper/paper.tex
Bunch of edits.

@@
 \begin{abstract}
-The winner-take-all (WTA) mechanism is an important component of many cognitive models.
-For example, it can be used to decide among multiple choices or direct attention to important parts of a visual scene.
+Winner-take-all (WTA) mechanisms are an important component of many cognitive models.
+For example, they can be used to decide among multiple choices or direct attention to important parts of a visual scene.
 Here we compare two biologically plausible, spiking neuron
@@
 Winner-take-all (WTA) networks provide a mechanism that selects the largest value among a number of possible inputs.
-More precisely, given a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{itti1998,standage2005}.
+More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.
+the ``winner'') and zero for all others.
+This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour, and selective attention~\cite<e.g.,>{itti1998,standage2005}.
 
@@
 \end{equation}
-where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
-Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and choose the encoders randomly.
+where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural non-linearity.
+Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
 Decoding weights $d_i$ are then used to approximate the represented value $\hat x(t)$ from the activity of the population of neurons by:
@@
 Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}a):
+The dynamics (cp.~Fig.~\ref{fig:usher-mcclelland}a) for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by:
 \begin{equation} \label{eqn:usher-mcclelland}
@@
     \caption{
-        Example time course of the state variables in the LCA network with three choices.
+        Example time course of the state variables in the LCA (top) and IA network (bottom) with three choices.
         The vector of inputs is given by $(0.8, 0.7, 0.6)$.
@@
 \subsection{Independent accumulator model}
-The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model (Figure~\ref{fig:ia-sketch}).
+The other WTA mechanism that we investigate is our proposed independent accumulator (IA) model (see Fig.~\ref{fig:ia-sketch}).
 We use the term `independent' to refer to the fact that there are no direct interactions between each accumulator, unlike in the LCA model which has direct competition between states.
@@
         Arrows denote excitatory connections, while lines ending in circles denote inhibitory connections.
+        The second layer computes $\bar{x}_i := \Theta(x_i - \vartheta)$.
     }\label{fig:ia-sketch}
@@
 
-The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
+The first layer consists of a separate integrator population (i.e. accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
 The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
@@
 Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
-This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}b):
+This is summarized more precisely by the following dynamics (cp.~Fig.~\ref{fig:indacc}b):
 \begin{equation}
@@
 \end{equation}
-Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence will be integrated.
-Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which is equivalent due to the leak-free integration.
+Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence needs to be integrated.
+Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which has a comparable effect due to the leak-free integration.
 % should we say anything about how the thresholding population works?
@@
 Thus, without loss of generality, the first state variable receives the strongest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
+It is important to note that $u$ does not only determine the size of the strongest input, but also the general baseline of inputs.
 Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
@@
 We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
-Further, we chose noise variance increments large enough to observe how the networks start to fail performing their task.
-This allows us to figure out which functions are performed more robustly by each network.
+Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets incearsingly difficult.
+This allows us to determine which functions are performed more robustly by each network.
 In both WTA models we use 200 neurons per choice.
@@
         LCA time-constant & $\tau = \SI{0.1}{\second}$ \\
-        LCA recurrent parameters & $k = \beta = 1$ \\
-        IA accumulation time-constant & $\tau_1 = \SI{0.1}{\second}$ \\
+        LCA recurrency parameters & $k = \beta = 1$ \\
+        IA accumulation time-constant & $\tau_1 = \SI{0.1}{\second},\ \SI{0.5}{\second}$ \\
         IA feedback time-constant & $\tau_2 = \SI{0.1}{\second}$ \\
         IA threshold & $\vartheta = 0.8$ \\
-        IA recurrent parameters & $\lambda = 1, \bar{\beta} = 2$ \\
+        IA recurrency parameters & $\bar{\beta} = 2$ \\
         Recurrent synaptic time-constant & $\tau_{\mathrm{s}} 
@@
 In the context of a larger model, this can become a problem because the transient output might be prematurely interpreted as a decision.
-Thus, we define $E_{\max}$ as the `highest output of a losing choice' during the whole simulation.
+Thus, we define $E_{\mathrm{trans}}$ as the `highest output of a losing choice' during the whole simulation.
 
@@
 We find that the ability to form a clear decision of the LCA network decreases with more noise and less target separation  (see Fig.~\ref{fig:decisions}).
-Also, the baseline has an important influence.
-For a small baseline of $u=0.2$ the winner will mostly not exceed the 0.15 threshold with noise present.
-The best performance is achieved with a medium baseline of $u=0.6$.
-A higher baseline makes it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
-In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points fall on the grey line).
+Also, the magnitude of the inputs has an important influence.
+For a small inputs with $u=0.2$ the winner will mostly not exceed the 0.15 threshold with noise present.
+The best performance is achieved with medium inputs with $u=0.6$.
+Higher inputs make it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
+In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points would fall on the grey line).
 \begin{figure*}
@@
 Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
-While always reaching a decision, the decisions of the IA network are not always correct (see Fig.~\ref{fig:correct}).
-Overall, the IA performance tends to be worse for a high baseline, but better for a low baseline (Fig.~\ref{fig:correct}a,b).
-We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which effectively adjusts the threshold $\vartheta$ (Fig.~\ref{fig:correct}c).
+While always reaching a decision, the decisions of the IA network are not always correct.
+Overall, the IA performance tends to be worse for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
+We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
 This improves the IA performance to be above the LCA performance for high baselines, but it will also increase the decisions times of the IA network.
-For a low baseline of $u=0.2$ this makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
+For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
 A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
@@
 
-The time required to reach a decision in the LCA network depends mostly on the baseline and target separation (see Fig.~\ref{fig:time}a).
+The time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation (see Fig.~\ref{fig:time}a).
 The level of noise only had a minor influence and was averaged over.
-Similarly, in the IA network the baseline is also the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
-Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
+In the IA network the strongest input is the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
+Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time with a $\tau_1$ that achieves the same fraction of correct responses.
 There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
@@
 
-Finally, looking at the transient responses both models might produce outputs of losing choices (see Fig.~\ref{fig:transient}).
+Finally, looking at the transient responses both models might produce outputs of losing choices.
 For the LCA network the magnitude of the transient response mainly increases with the amount of noise (Fig.~\ref{fig:transient}a).
 For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions with small target separations.
-The magnitude of such transient responses is reduced by decreasing by adjusting $\tau_1$ to 0.5.
+The magnitude of such transient responses is reduced by adjusting $\tau_1$ to 0.5.
 \begin{figure*}
@@
 We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
-For instance, the LCA network can determine the correct winner more quickly and given a conclusive decision was made, it is always picks the correct winner.
+For instance, the LCA network can determine the correct winner more quickly and given that a conclusive decision was made, it is always picks the correct winner.
 However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
@@
 The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
+In addition, the IA network is easily extendable to dynamically control the speed of decisions by feeding in a dynamic bias to the layer 2 populations.
 
@@
 Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
-This limits how quickly successive decisions can be made.
+This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
 On the other hand, once a decision is made, the network provides a stable output.
 
-Both models might produce a transient response that can be problematic in detecting when the decision has been made as it might be interpreted as the decision.
-This is of special relevance when integrating the networks in larger cognitive models.
+Both models might produce a transient response that can be problematic in detecting when the decision has been made as the transient output might be interpreted as the decision.
+This is of special relevance when incorporating the networks in larger cognitive models.
 For the LCA network this behaviour is inherent.
@@
 
+We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is out of the scope of this paper.
+Also, the implementation in spiking neurons ensures a certain level of biological plausibility.
 Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.
@@
 Furthermore, this argument assumes integration with perfect accuracy.
-But in a neural network resources are limited. As such the range and accuracy of values that can be represented in a neural population is limited.
+But in a neural network resources are limited.
+As such the range and accuracy of values that can be represented in a neural population is bounded.
 At some point this would counterbalance any additional evidence.
 
-We did not investigate the biological plausibility of these mechanisms in detail because this has been done before for different WTA networks~\cite{gold2007,smith2004}.
-Also, the implementation in spiking neurons ensures a certain level of biological plausibility.
 We also did not look at at the influence of the number of dimensions $D$ in detail, but qualitatively the results will stay the same.

### 2017-01-26 doc/paper/paper.tex
Remove systematic bias stuff.

@@
 In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points would fall on the grey line).
-\begin{figure*}
+\begin{figure*}[t]
     \centering
@@
 For a low baseline with $u=0.2$, it makes the IA network unable to decide within the allocated time frame, but given more time it would still reach a decision.
-A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
-In the NEF the neuron gain and bias parameters are usually picked from random distributions.
-As such the layer 2 populations will become active at slightly different thresholds.
-By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
-\begin{figure*}
+%A further improvement to the IA network is possible by eliminating a systematic bias introduced in the second layer of the IA network.
+%In the NEF the neuron gain and bias parameters are usually picked from random distributions.
+%As such the layer 2 populations will become active at slightly different thresholds.
+%By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
+\begin{figure*}[t]
     \centering
@@
 There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
-\begin{figure*}
+\begin{figure*}[t]
     \centering
@@
 
-Part of the reason why the IA network produces less correct responses is the systematic bias introduced in the second layer.
-By eliminating this bias through identical ensembles the correctness of the model is increased considerably.
-However, this would require a very precise tuning of the neurons that might not be biologically plausible.
+%Part of the reason why the IA network produces less correct responses is the systematic bias introduced in the second layer.
+%By eliminating this bias through identical ensembles the correctness of the model is increased considerably.
+%However, this would require a very precise tuning of the neurons that might not be biologically plausible.
 

### 2017-01-26 doc/paper/paper.tex
Update figures and captions.

@@
     \caption{
-        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$, target separations $s$, and input baselines $u$ for the LCA network.
+        Fraction of trials with a clear decision for the LCA network.
+        Each plot shows data for a different input magnitude $u$.
         Error bars denote bootstrapped 95\% confidence intervals.
@@
     \caption{
-        Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
+        Fraction of correct trials for the IA network.  
+        Each plot shows data for a different combination of input magnitude $u$ and integration time constant $\tau_1$.
         Error bars denote bootstrapped 95\% confidence intervals.
@@
     \caption{
-        (a) Mean decision times for different baselines $u$ and target separations $s$ for the LCA.
-        (b) For the IA network $u = 0.2$ (solid) and $u = 1.0$ (dashed) are shown for different noise standard deviations $s$ and target separations $s$.
+        Left: mean decision times for the LCA network. Shown data is averaged over all noise levels as it only had minor influence on the decision times.
+        Right: mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
         Error bars denote bootstrapped 95\% confidence intervals.
@@
     \caption{
-        Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
+        Transient response (highest output of losing choices) for the LCA and IA network.
         Error bars denote bootstrapped 95\% confidence intervals.

### 2017-01-26 doc/paper/paper.tex
Fix chktex warnings.

@@
 Winner-take-all (WTA) networks provide a mechanism that selects the largest value among a number of possible inputs.
-More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.
-the ``winner'') and zero for all others.
+More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.~the ``winner'') and zero for all others.
 This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour, and selective attention~\cite<e.g.,>{itti1998,standage2005}.
@@
 
-The first layer consists of a separate integrator population (i.e. accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
+The first layer consists of a separate integrator population (i.e.~accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
 The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
@@
 The level of noise only had a minor influence and was averaged over.
-In the IA network the strongest input is the most important factor (dashed vs. solid lines in Fig.~\ref{fig:time}b).
+In the IA network the strongest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
 Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time with a $\tau_1$ that achieves the same fraction of correct responses.

### 2017-01-29 doc/paper/paper.tex
Some more edits.

@@
 More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.~the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour, and selective attention~\cite<e.g.,>{itti1998,standage2005}.
+This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour, and selective attention~\cite<e.g.,>{oreilly1998,itti1998,standage2005}.
 
@@
 We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
-Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets incearsingly difficult.
+Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets increasingly difficult.
 This allows us to determine which functions are performed more robustly by each network.
@@
     \caption{
-        Fraction of trials with a clear decision for the LCA network.
+        Fraction of trials with a clear decision for the LCA network (also matches exactly the fraction of correct trials).
         Each plot shows data for a different input magnitude $u$.
         Error bars denote bootstrapped 95\% confidence intervals.
-        The grey horizontal line shows the optimum.
-        It coincides with the performance of the IA network.
+        The grey horizontal line shows the optimum and coincides with the performance of the IA network.
     }\label{fig:decisions}
@@
 In the IA network the strongest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
-Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time with a $\tau_1$ that achieves the same fraction of correct responses.
+Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses.
 There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
@@
 For instance, the LCA network can determine the correct winner more quickly and given that a conclusive decision was made, it is always picks the correct winner.
-However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
+However, under highly noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
 This can be problematic in situations were it is better or required to make a decision even though it might not be the best choice.
 The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
-In addition, the IA network is easily extendable to dynamically control the speed of decisions by feeding in a dynamic bias to the layer 2 populations.
+This also enables it to react to small inputs.
+In addition, the IA network is easily extendable to dynamically control the speed of decisions by feeding in a dynamic bias to the layer 2 populations that effectively adjusts the $\vartheta$ threshold.
 
@@
 We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is out of the scope of this paper.
-Also, the implementation in spiking neurons ensures a certain level of biological plausibility.
+The implementation in spiking neurons, however, ensures a certain level of biological plausibility.
+Also, given specific evidence for one network, we cannot exclude the possibility that the other network is not employed for different tasks or in different brain areas.
 Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.
@@
 
-It is worth to highlight, that one can transform one model into the other with a few steps.
-By setting $\tau = \tau_1$, $k = -\tau/\tau_2$, and $\beta = \bar{\beta}\tau/\tau_2$ we obtain almost identical model equations.
-The only remaining difference is the added Heaviside non-linearity on the state variables.
-Nevertheless, the behaviour of the two models is quite distinct.
+We also did not look at at the influence of the number of dimensions $D$ in detail.
+For higher $D$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
+But apart from that, we expect the qualitative results to stay the same.
+With just two choices ($D=2$) the decision problem can get a lot easier as the sum of losing inputs is guaranteed to be below the magnitude of the winner.
+As this case is less general we did not consider it here.
 
@@
 
-We also did not look at at the influence of the number of dimensions $D$ in detail, but qualitatively the results will stay the same.
-For higher $D$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
+Finally, it is worth to highlight the mathematical relatedness of the two models.
+One can transform one model into the other with a few steps.
+By setting $\tau = \tau_1$, $k = -\tau/\tau_2$, and $\beta = \bar{\beta}\tau/\tau_2$ we obtain almost identical model equations.
+The only remaining difference is the added Heaviside non-linearity on the state variables.
+Nevertheless, the behaviour of the two models is quite distinct.
 

### 2017-01-29 doc/paper/paper.tex
More edits for succinctness / clarity / consistency

@@
 \author{{\large \bf Jan Gosmann (jgosmann@uwaterloo.ca)} \\
-  {\large \bf Aaron R.
-Voelker (arvoelke@uwaterloo.ca)} \\
+  {\large \bf Aaron R. Voelker (arvoelke@uwaterloo.ca)} \\
   {\large \bf Chris Eliasmith (celiasmith@uwaterloo.ca)} \\
@@
 
-\begin{abstract}
+\begin{abstract}  % 150 word limit
 Winner-take-all (WTA) mechanisms are an important component of many cognitive models.
-For example, they can be used to decide among multiple choices or direct attention to important parts of a visual scene.
-Here we compare two biologically plausible, spiking neuron
-implementations of different WTA mechanisms. 
+For example, they can be used to decide between multiple choices and to selectively direct attention.
+Here we compare two biologically plausible, spiking neural WTA mechanisms. 
 We first provide a novel spiking implementation of the well-known leaky, competing accumulator (LCA) model, by mapping the dynamics onto a population-level representation.
-We then propose a new two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
+We then propose a two-layer spiking independent accumulator (IA) model, and compare its performance against the LCA network on a variety of WTA benchmarks.
 Our findings suggest that while the LCA network can rapidly adapt to new winners, the IA network is better suited for stable decision making in the presence of noise.
 
-\textbf{Keywords:} Neural Engineering Framework; Nengo; winner-take-all; 
-decision making; mutual inhibition; neural competition; dynamical systems
+\textbf{Keywords:} Neural Engineering Framework; Nengo; winner-take-all; decision making; mutual inhibition; neural competition; dynamical systems
 \end{abstract}
@@
 
-Winner-take-all (WTA) networks provide a mechanism that selects the largest value among a number of possible inputs.
-More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.~the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving decision making, in which the action with the highest utility is selected to drive behaviour, and selective attention~\cite<e.g.,>{oreilly1998,itti1998,standage2005}.
+Winner-take-all (WTA) networks are mechanisms that select the largest value among a number of possible inputs.
+More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.,~the ``winner'') and zero for all others.
+This mechanism is regularly employed as a component of cognitive models involving selective attention~\cite<e.g.,>{itti1998,standage2005} and decision making -- in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{oreilly1998}.
 
-A large body of literature exists examining the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
+A large body of literature examines the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
 Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
@@
 The LCA model and variants have been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test models~\cite<e.g.,>{kajic2017}.
-The second mechanism we consider is the \emph{independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
+The second mechanism we consider is the \emph{independent accumulator} (IA) model that we propose here, which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
 
@@
 \end{equation}
-where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural non-linearity.
+where $\alpha_i$ is a gain factor, $e_i$ is an encoder that determines a neuron's tuning curve, $J_i^{\mathrm{bias}}$ a bias current, and $G_i \left[ \cdot \right]$ is the neural nonlinearity.
 Here, we use spiking, leaky integrate-and-fire (LIF) neurons for $G_i \left[ \cdot \right]$, and set the encoders to one.
@@
 \subsubsection{Principle 3: Dynamics}
-Given some nonlinear dynamics for the state variable $x(t)$:
+Given some desired nonlinear dynamics for the state variable $x(t)$:
 \begin{equation} \label{eqn:nonlinear-system}
@@
 \end{equation}
-we can map these dynamics onto a recurrent transformation, by harnessing the synaptic filter used in Principle 1.
+we can map these dynamics onto a recurrent transformation, by harnessing the synaptic filter mentioned in Principle 1.
 In particular, for the exponentially decaying $h(t)$ we may apply Principle 2 to the recurrent transformation $f(x) = \tau_s g(x) + x$ to ensure that $x(t)$ obeys Equation~\ref{eqn:nonlinear-system}.
@@
 \subsection{Leaky, competing accumulator model}
-Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics (cp.~Fig.~\ref{fig:usher-mcclelland}a) for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by:
+Using the principles of the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
+The dynamics (see~Fig.~\ref{fig:usher-mcclelland}a) for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by:
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 \end{equation}
-where $\rho_i$ is each external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time-constant.
+where $\rho_i$ is each external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the integration time-constant.
 This model essentially integrates each input $\rho_i$ with a leak term ($- kx_i$), minus competition from every other variable ($\beta \sum_{j \neq i} x_j$).
 Supposing $\rho_i > \rho_j$ for all $j \ne i$, a WTA mechanism should indicate that $i$ is the winning choice.
-Setting $k = \beta = 1$ will guarantee that the winning state $x_i$ converges to the value of the largest input $\rho_i$, while the losing states $x_j$ ($j \ne i$) converge to zero.
-Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).
+Setting $k = \beta = 1$ will guarantee that the winning state $x_i$ converges to the value of the largest input $\rho_i$, while each losing state $x_j$ ($j \ne i$) converges to zero.
+Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviours (see supplementary analysis).
 
@@
     \caption{
-        Example time course of the state variables in the LCA (top) and IA network (bottom) with three choices.
-        The vector of inputs is given by $(0.8, 0.7, 0.6)$.
+        \todo{Bottom-left missing time axis label.}
+        Example time course of the state variables in the LCA (top) and IA (bottom) networks with three choices ($D~=~3$).
+        The vector of inputs is $\left[ 0.8, 0.7, 0.6 \right]$.
     }\label{fig:usher-mcclelland}\label{fig:indacc}
@@
 To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
-We now provide the details of each layer, again implemented with the principles of the NEF\@.
+We now provide the details of each layer -- again implemented using the principles of the NEF\@.
 \begin{figure}
@@
     \caption{
-        Independent accumulator network.
-        Neural populations are denoted by circles labeled with their represented state variable.
+        \todo{Use LaTeX font in figure?}
+        Independent accumulator (IA) network.
+        Neural populations are denoted by circles labelled with their represented state variable.
         Arrows denote excitatory connections, while lines ending in circles denote inhibitory connections.
@@
 
-The first layer consists of a separate integrator population (i.e.~accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
+The first layer consists of a separate integrator population (i.e.,~accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
 The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
@@
 Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
-This is summarized more precisely by the following dynamics (cp.~Fig.~\ref{fig:indacc}b):
+This is summarized more precisely by the following dynamics (see~Fig.~\ref{fig:indacc}b):
 \begin{equation}
@@
 \end{equation}
-Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence needs to be integrated.
-Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which has a comparable effect due to the leak-free integration.
+Notably, this takes on the form of Equation~\ref{eqn:usher-mcclelland} after substituting $\tau = \tau_1$, $k = -\tau_1/\tau_2$, and $\beta = \bar{\beta}\tau_1/\tau_2$, with the only remaining difference being the Heaviside nonlinearity applied to the state feedback.
+In contrast to the LCA model, the Heaviside threshold $\vartheta$ is a free parameter that controls how much evidence needs to be integrated before enabling any competition between states.
+Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead, which has a comparable effect due to the leak-free integration.
 % should we say anything about how the thresholding population works?
@@
     \caption{
-        Fraction of trials with a clear decision for the LCA network (also matches exactly the fraction of correct trials).
+        Fraction of trials with a clear decision for the LCA network (which also exactly matches the fraction of correct trials).
         Each plot shows data for a different input magnitude $u$.
         Error bars denote bootstrapped 95\% confidence intervals.
-        The grey horizontal line shows the optimum and coincides with the performance of the IA network.
+        The grey horizontal line indicates the optimum, which coincides with the performance of the IA network.
     }\label{fig:decisions}
@@
 %As such the layer 2 populations will become active at slightly different thresholds.
-%By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
+%By using identical layer 2 populations, i.e.,~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
 \begin{figure*}[t]
@@
         Error bars denote bootstrapped 95\% confidence intervals.
-        The grey horizontal line shows the optimum.
+        The grey horizontal line indicates the optimum.
     }\label{fig:correct}
@@
     \caption{
-        Left: mean decision times for the LCA network. Shown data is averaged over all noise levels as it only had minor influence on the decision times.
-        Right: mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
+        (Left) Mean decision times for the LCA network.
+        Shown data is averaged across all noise levels, since noise had minimal effect on decision times.
+        (Right) Mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
+        \todo{Move (dashed) and (solid) from title to legend?)}
         Error bars denote bootstrapped 95\% confidence intervals.
@@
 We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
-For instance, the LCA network can determine the correct winner more quickly and given that a conclusive decision was made, it is always picks the correct winner.
-However, under highly noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
-This can be problematic in situations were it is better or required to make a decision even though it might not be the best choice.
+For instance, the LCA network can determine the correct winner more quickly, and, given that a conclusive decision was made, it always selects the correct winner.
+However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
+This can be problematic for cognitive models that require the network to make a decision (even when it may be incorrect).
 The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
-This also enables it to react to small inputs.
-In addition, the IA network is easily extendable to dynamically control the speed of decisions by feeding in a dynamic bias to the layer 2 populations that effectively adjusts the $\vartheta$ threshold.
+This is a direct consequence of the thresholding on the state feedback, which prevents competition from occurring until a sufficient amount of evidence has accumulated.
+This also enables the IA network to react to small inputs.
+In addition, the IA network is easily extendible to dynamically control the speed of decisions, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.
 
-Furthermore, the LCA network is especially well-suited for situations where a decision needs to be continuously adjusted.
-The prescribed dynamics essentially try to output whatever the currently largest input is, while performing some smoothing over time.
-This makes it quick to respond to changes in the input, but can also lead to randomly switching outputs due to noise.
+On the other hand, the LCA network is especially well-suited for situations where a decision needs to be continuously adjusted.
+The dynamics constantly push the winning state variable to the magnitude of the largest input, while adapting to input changes along a time-scale of $\tau$.
+This makes it quick to respond to changes in the input for smaller $\tau$, but leads to randomly switching outputs due to noise.
 
@@
 This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
-On the other hand, once a decision is made, the network provides a stable output.
+However, once a decision is made, the network provides a stable output.
 
-Both models might produce a transient response that can be problematic in detecting when the decision has been made as the transient output might be interpreted as the decision.
+Both models might produce a transient response that may be interpreted as a decision, which can make the detection of decisions problematic.
 This is of special relevance when incorporating the networks in larger cognitive models.
-For the LCA network this behaviour is inherent.
-There will always be an initial rise of all state variables that receive input before the mutual inhibition grows strong enough to push them back to zero.
-In the IA network, however, this is mostly a matter of choosing an appropriate $\tau_1$.
+For the LCA network, the transient behaviour is inherent to its design; there will always be an initial rise of all state variables (that receive input) before the mutual inhibition grows strong enough to push them back to zero.
+In the IA network, however, such transient responses may be avoided by choosing appropriate $\tau_1$ and $\vartheta$.
 
@@
 
-We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is out of the scope of this paper.
-The implementation in spiking neurons, however, ensures a certain level of biological plausibility.
+We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is outside the scope of this paper.
+The implementation in spiking neurons, however, ensures a certain level of biological plausibility and more readily permits comparisons with neural data.
 Also, given specific evidence for one network, we cannot exclude the possibility that the other network is not employed for different tasks or in different brain areas.
@@
 We also did not look at at the influence of the number of dimensions $D$ in detail.
-For higher $D$, we expect less accuracy since each additional choice has a baseline chance to win due to noise.
-But apart from that, we expect the qualitative results to stay the same.
-With just two choices ($D=2$) the decision problem can get a lot easier as the sum of losing inputs is guaranteed to be below the magnitude of the winner.
-As this case is less general we did not consider it here.
+For higher $D$, we see reduced accuracy since each additional choice has a baseline chance to win due to noise.
+Nevertheless, the qualitative results stay the same.
+% With the specific case of only two choices ($D=2$) the decision problem becomes fundamentally easier, since the sum of losing inputs is guaranteed to be below the magnitude of the winner.
+% As this case is less general we did not consider it here.
 
@@
 At some point this would counterbalance any additional evidence.
-
-Finally, it is worth to highlight the mathematical relatedness of the two models.
-One can transform one model into the other with a few steps.
-By setting $\tau = \tau_1$, $k = -\tau/\tau_2$, and $\beta = \bar{\beta}\tau/\tau_2$ we obtain almost identical model equations.
-The only remaining difference is the added Heaviside non-linearity on the state variables.
-Nevertheless, the behaviour of the two models is quite distinct.
+\todo{End on a more finalizing note.}
 

### 2017-01-30 doc/paper/paper.tex
Tidy up and some filler suggestions

@@
 \end{equation}
-Notably, this takes on the form of Equation~\ref{eqn:usher-mcclelland} after substituting $\tau = \tau_1$, $k = -\tau_1/\tau_2$, and $\beta = \bar{\beta}\tau_1/\tau_2$, with the only remaining difference being the Heaviside nonlinearity applied to the state feedback.
-In contrast to the LCA model, the Heaviside threshold $\vartheta$ is a free parameter that controls how much evidence needs to be integrated before enabling any competition between states.
-Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead, which has a comparable effect due to the leak-free integration.
-% should we say anything about how the thresholding population works?
+Notably, this takes the form of Equation~\ref{eqn:usher-mcclelland} after substituting $\tau = \tau_1$, $k = -\tau_1/\tau_2$, and $\beta = \bar{\beta}\tau_1/\tau_2$, with the only remaining difference being the Heaviside nonlinearity applied to the state feedback.
+Thus, in contrast to the continual competition occurring in the LCA model, the threshold $\vartheta$ is a free parameter that controls how much evidence needs to be integrated before enabling any competition between states.
+Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$, which has a comparable effect due to the leak-free integration.
+\todo{Put in more implementation details? e.g., how the thresholding population works, and why certain design choices were made?}
 
 \subsection{Benchmarks}
-To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the strongest input, 
-$s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
-Thus, without loss of generality, the first state variable receives the strongest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
-It is important to note that $u$ does not only determine the size of the strongest input, but also the general baseline of inputs.
+To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the largest input, $s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
+Thus, without loss of generality, the first state variable receives the largest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
+It is important to note that $u$ does not only determine the size of the largest input, but also the general baseline of inputs.
 Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
@@
 Note that this metric requires that the decision does not change throughout the time interval.
-This does not take into account whether the winning output actually corresponds to the strongest input, but for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
+This does not take into account whether the winning output actually corresponds to the largest input, but for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
 In other situations, though, the correctness of the decision may be of higher importance.
@@
 The level of noise only had a minor influence and was averaged over.
-In the IA network the strongest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
+In the IA network the largest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
 Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses.
@@
     \caption{
+        \todo{Can you make it so that the left / right subfigures are aligned with the left / right columns? Currently the left subfigure stretches over the center dividing line.}
         (Left) Mean decision times for the LCA network.
@@
         (Right) Mean decision times for the IA network with input magnitude $u = 0.2$ (solid) and $u = 1$ (dashed).
-        \todo{Move (dashed) and (solid) from title to legend?)}
         Error bars denote bootstrapped 95\% confidence intervals.
@@
 However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
-This can be problematic for cognitive models that require the network to make a decision (even when it may be incorrect).
+This can be problematic for cognitive models that must form a clear decision (even when it may be incorrect).
 The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
@@
 
-On the other hand, the LCA network is especially well-suited for situations where a decision needs to be continuously adjusted.
+The LCA network is especially well-suited for situations where a decision needs to be continuously adjusted.
 The dynamics constantly push the winning state variable to the magnitude of the largest input, while adapting to input changes along a time-scale of $\tau$.
@@
 Both models might produce a transient response that may be interpreted as a decision, which can make the detection of decisions problematic.
-This is of special relevance when incorporating the networks in larger cognitive models.
+This is of special relevance when incorporating the networks into larger cognitive models.
 For the LCA network, the transient behaviour is inherent to its design; there will always be an initial rise of all state variables (that receive input) before the mutual inhibition grows strong enough to push them back to zero.
@@
 We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is outside the scope of this paper.
+\todo{I think if this were to become a journal article, then these are the sorts of connections that reviewers would be most interested in seeing.
+And so it might be worth touching more on what we could look into?
+For example, the distinct predictions that each model would make regarding patterns of activity during decision making tasks.}
 The implementation in spiking neurons, however, ensures a certain level of biological plausibility and more readily permits comparisons with neural data.
@@
 However, this assumes that the time to reach a decision has no cost.
-If time-to-decision has a cost, it will at some point exceed the gain achieved from making a correct decision.
+If time-to-decision has a cost, then it will at some point exceed the gain achieved from making a correct decision.
 Furthermore, this argument assumes integration with perfect accuracy.
-But in a neural network resources are limited.
-As such the range and accuracy of values that can be represented in a neural population is bounded.
-At some point this would counterbalance any additional evidence.
-\todo{End on a more finalizing note.}
+But, with networks built using the NEF, the representation of each state variable has limited precision, and so an ideal trade-off must be found.
+\todo{End on a more finalizing note. We should try to make it clear how in the end this has advanced the field. Why is this work important, where does this leave us, etc.}
 

### 2017-01-30 doc/paper/paper.tex
Fixup

@@
 \subsection{Benchmarks}
-To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the largest input, $s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
+To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the magnitude of the largest input, $s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
 Thus, without loss of generality, the first state variable receives the largest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.

### 2017-01-30 doc/paper/paper.tex
next round of edits

@@
 
-\title{A Spiking Independent Accumulator Model for Winner-Take-All}
+\title{A Spiking Independent Accumulator Model for Winner-Take-All Networks
+\todo{I put 'networks', but am not sure that's the right word, but it seems some word
+needs to go there... 'computations', 'decisions'? WTA is usually an adjective}}
 
@@
 Winner-take-all (WTA) mechanisms are an important component of many cognitive models.
-For example, they can be used to decide between multiple choices and to selectively direct attention.
+For example, they are often used to decide between multiple choices or to selectively direct attention.
 Here we compare two biologically plausible, spiking neural WTA mechanisms. 
@@
 
-Winner-take-all (WTA) networks are mechanisms that select the largest value among a number of possible inputs.
+Winner-take-all (WTA) networks are mechanisms that select the largest value among a number of inputs.
 More precisely, given a $D$-dimensional vector corresponding to the non-negative utility of $D$ different choices, the desired output is positive for the dimension with highest utility (i.e.,~the ``winner'') and zero for all others.
-This mechanism is regularly employed as a component of cognitive models involving selective attention~\cite<e.g.,>{itti1998,standage2005} and decision making -- in which the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{oreilly1998}.
+This mechanism is regularly employed as a component of cognitive models involving selective attention~\cite<e.g.,>{itti1998,standage2005} and decision making, where the action with the highest utility is selected to drive behaviour~\cite<e.g.,>{oreilly1998}.
 
 A large body of literature examines the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
-Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
-In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
+Here, we investigate the suitability of two different WTA mechanisms in the context of neurally plausible cognitive modelling.
+In particular, we map each mechanism onto a network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
 The first mechanism we consider is an implementation of the \emph{leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
@@
 \subsection{The Neural Engineering Framework}
-The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method of mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
+The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method for mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
 We now describe the aspects of this framework that are relevant to this work, by summarizing its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.
@@
 The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
+\todo{do you actually use absolute value?  should these be double bars?}
 For the transmission of a value from one population to another, the connection weights are given by:
@@
 Thus, without loss of generality, the first state variable receives the largest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
-It is important to note that $u$ does not only determine the size of the largest input, but also the general baseline of inputs.
-Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
-As $s \rightarrow 0$ the problem becomes more difficult because the utilities of the choices are closer together.
-We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
-Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets increasingly difficult.
-This allows us to determine which functions are performed more robustly by each network.
+It is important to note that $u$ not only determines the size of the largest input, but also the general baseline of inputs.
+Since all of the runner-ups have equal magnitude, this represents the most difficult scenario for the networks, where all potential choices must be considered.
+As $s \rightarrow 0$ the problem also becomes more difficult because the utilities of the choices are closer together.
+We use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
+Further, we increment the noise variance to highlight successes and failures as the task gets increasingly difficult with more noise.
+This allows us to determine which functions are performed robustly by each network.
 In both WTA models we use 200 neurons per choice.
@@
 Note that this metric requires that the decision does not change throughout the time interval.
-This does not take into account whether the winning output actually corresponds to the largest input, but for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
+This does not take into account whether the winning output actually corresponds to the largest input. 
+However, for some models it is more desirable to produce a clear incorrect decision than an unstable incorrect decision.
 In other situations, though, the correctness of the decision may be of higher importance.
 Thus, we consider a trial `correct' if the model forms a clear decision, and the largest output corresponds to the true largest input.  
+Measurement of correct trials forms our second benchmark.
 
@@
 Higher inputs make it more likely that runner-ups will exceed the 0.15 threshold, especially with a small target separation.
-In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points would fall on the grey line).
+In contrast to the LCA network, the IA network manages to form a clear decision in every trial (not explicitly shown in Figure~\ref{fig:decisions}, but all data points fall on the grey line).
 \begin{figure*}[t]
@@
 
-Interestingly, for all successful decisions the correct winner was determined by the LCA network.
-Thus, a plot of correct trials looks virtually identical to Figure~\ref{fig:decisions}.
-While always reaching a decision, the decisions of the IA network are not always correct.
-Overall, the IA performance tends to be worse for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
+Interestingly, for all clear decisions the correct winner was determined by the LCA network.
+Thus, a plot of correct trials looks identical to Figure~\ref{fig:decisions}, with slightly different error bars.
+While always reaching a clear decision, the decisions of the IA network are not always correct.
+Overall, the IA performance tends to be worse than LCA \todo{is that what you meant?} for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
 We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
@@
 
-The time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation (see Fig.~\ref{fig:time}a).
-The level of noise only had a minor influence and was averaged over.
+As shown in Fig.~\ref{fig:time}a, the time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation.
+The level of noise only has a minor influence and is averaged over.\todo{not sure what this 'averaged over' is refering to}
 In the IA network the largest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).
-Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses.
-There is also a slight influence of target separation and input noise with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
+Depending on this magnitude, the network can either be faster or slower than the LCA network, but it will need more time given a value of $\tau_1$ that achieves the same fraction of correct responses as the LCA network.
+There is also a slight influence of target separation and input noise, with an interaction of these two parameters (solid lines in Fig.~\ref{fig:time}).
 \begin{figure*}[t]
@@
 
-Finally, looking at the transient responses both models might produce outputs of losing choices.
+Finally, looking at the transient responses indicates that both models might produce outputs of losing choices.
 For the LCA network the magnitude of the transient response mainly increases with the amount of noise (Fig.~\ref{fig:transient}a).
 For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions with small target separations.
-The magnitude of such transient responses is reduced by adjusting $\tau_1$ to 0.5.
+The magnitude of such transient responses is reduced by adjusting $\tau_1$ to 0.5, at the cost of a slower decision.
 \begin{figure*}
@@
 This also enables the IA network to react to small inputs.
-In addition, the IA network is easily extendible to dynamically control the speed of decisions, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.
+In addition, the IA network is easily extendible to allow dynamic control the speed of decisions, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.
 
@@
 
-We did not investigate the agreement of these mechanisms with neurobiological and behavioural data because this has been done before for different WTA networks~\cite{gold2007,smith2004} and is outside the scope of this paper.
+We have not yet investigated the agreement of these mechanisms with neurobiological and behavioural data, although this has been done before for other WTA networks~\cite{gold2007,smith2004}.
 \todo{I think if this were to become a journal article, then these are the sorts of connections that reviewers would be most interested in seeing.
@@
 For example, the distinct predictions that each model would make regarding patterns of activity during decision making tasks.}
-The implementation in spiking neurons, however, ensures a certain level of biological plausibility and more readily permits comparisons with neural data.
-Also, given specific evidence for one network, we cannot exclude the possibility that the other network is not employed for different tasks or in different brain areas.
+The implementation in spiking neurons, however, provides some basic biological plausibility and more readily permits comparisons with neural data.
+Also, given specific evidence for one network does not exclude the possibility that the other network is employed for different tasks or in different brain areas.
 Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.
@@
 For higher $D$, we see reduced accuracy since each additional choice has a baseline chance to win due to noise.
-Nevertheless, the qualitative results stay the same.
+Nevertheless, the qualitative results are expected to stay the same.
 % With the specific case of only two choices ($D=2$) the decision problem becomes fundamentally easier, since the sum of losing inputs is guaranteed to be below the magnitude of the winner.
@@
 But, with networks built using the NEF, the representation of each state variable has limited precision, and so an ideal trade-off must be found.
-\todo{End on a more finalizing note. We should try to make it clear how in the end this has advanced the field. Why is this work important, where does this leave us, etc.}
+\todo{End on a more finalizing note.
+We should try to make it clear how in the end this has advanced the field.
+Why is this work important, where does this leave us, etc.
+ce: i agree with this suggestion.}
 

### 2017-01-30 doc/paper/paper.tex
gets -> becomes, further -> furthermore
Remove unnecessary non-breaking spaces.

@@
 \section{Introduction}
-
 Winner-take-all (WTA) networks are mechanisms that select the largest value among a number of inputs.
@@
 Using the principles of the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
-The dynamics (see~Fig.~\ref{fig:usher-mcclelland}a) for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by:
+The dynamics (see Fig.~\ref{fig:usher-mcclelland}a) for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by:
 \begin{equation} \label{eqn:usher-mcclelland}
@@
 
-The first layer consists of a separate integrator population (i.e.,~accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
+The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
 The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
@@
 Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
-This is summarized more precisely by the following dynamics (see~Fig.~\ref{fig:indacc}b):
+This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}b):
 \begin{equation}
@@
 We use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
-Further, we increment the noise variance to highlight successes and failures as the task gets increasingly difficult with more noise.
+Furthermore, we increment the noise variance to highlight successes and failures as the task becomes increasingly difficult with more noise.
 This allows us to determine which functions are performed robustly by each network.
@@
 %As such the layer 2 populations will become active at slightly different thresholds.
-%By using identical layer 2 populations, i.e.,~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
+%By using identical layer 2 populations, i.e., identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs even better (Fig.~\ref{fig:correct}d).
 \begin{figure*}[t]

### 2017-01-30 doc/paper/paper.tex
Fix missing time label.
Use main font in IA sketch.

@@
     \caption{
-        \todo{Bottom-left missing time axis label.}
         Example time course of the state variables in the LCA (top) and IA (bottom) networks with three choices ($D~=~3$).
@@
     \caption{
-        \todo{Use LaTeX font in figure?}
         Independent accumulator (IA) network.

### 2017-01-30 doc/paper/paper.tex
Clarifications.

@@
 While always reaching a clear decision, the decisions of the IA network are not always correct.
-Overall, the IA performance tends to be worse than LCA \todo{is that what you meant?} for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
+Overall, the IA performance tends to be worse than the LCA performance for a high input magnitude, but better for smaller inputs (Fig.~\ref{fig:correct}a,\,b).
 We can greatly improve the IA performance by increasing $\tau_1$ to \SI{0.5}{\second} which slows down the integration of evidence (Fig.~\ref{fig:correct}c).
@@
 As shown in Fig.~\ref{fig:time}a, the time required to reach a decision in the LCA network depends mostly on the size of inputs and target separation.
-The level of noise only has a minor influence and is averaged over.\todo{not sure what this 'averaged over' is refering to}
+We averaged over the different noise conditions because the noise influence on the timing was minor.
 In the IA network the largest input is the most important factor (dashed vs.\ solid lines in Fig.~\ref{fig:time}b).

### 2017-01-30 doc/paper/paper.tex
Remove todo.
Make subfigures match col width.

@@
 The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
-\todo{do you actually use absolute value?  should these be double bars?}
 For the transmission of a value from one population to another, the connection weights are given by:
@@
 \begin{figure*}[t]
-    \centering
-    \includegraphics{figures/time}
+    \includegraphics{figures/time1}
+    \hfill
+    \includegraphics{figures/time2}
     \caption{
-        \todo{Can you make it so that the left / right subfigures are aligned with the left / right columns? Currently the left subfigure stretches over the center dividing line.}
         (Left) Mean decision times for the LCA network.

### 2017-01-30 psy-tasks/task_decision.py
Parallelize.

@@ -18,7 +18,7 @@ pspace = (
     Param(seed=range(50))
 )
 
-min_items = 1
+min_items = 20
 max_jobs = None
 
 

### 2017-01-31 doc/paper/paper.tex
Add concluding remarks.

@@
 But, with networks built using the NEF, the representation of each state variable has limited precision, and so an ideal trade-off must be found.
-\todo{End on a more finalizing note.
-We should try to make it clear how in the end this has advanced the field.
-Why is this work important, where does this leave us, etc.
-ce: i agree with this suggestion.}
+
+To conclude, we investigated two spiking neural networks computing a winner-take-all function based on the leaky, competing accumulator model and a novel two-layer independent accumulator model.
+While both perform the same basic tasks, they fail on it in different ways as the task becomes more difficult with increased noise or less separation among the choices.
+From a modelling perspective, this makes each network more useful in different situations.
+The LCA model is better for continuous updating of decisions, whereas the IA network is better suited for more discrete decisions in the presence of noise.
+It is left to future work to investigate whether such two distinct mechanisms can be identified from either behavioural or neurophysiological data.
 

### 2017-01-31 doc/paper/paper.tex
A few more details on model predictions.

@@
 We have not yet investigated the agreement of these mechanisms with neurobiological and behavioural data, although this has been done before for other WTA networks~\cite{gold2007,smith2004}.
-\todo{I think if this were to become a journal article, then these are the sorts of connections that reviewers would be most interested in seeing.
-And so it might be worth touching more on what we could look into?
-For example, the distinct predictions that each model would make regarding patterns of activity during decision making tasks.}
 The implementation in spiking neurons, however, provides some basic biological plausibility and more readily permits comparisons with neural data.
-Also, given specific evidence for one network does not exclude the possibility that the other network is employed for different tasks or in different brain areas.
+In particular, the LCA networks predicts firing rates proportional to the input strength, while the IA network predicts that firing rates will rise up to a threshold for neurons in the first neurons and that neurons in the second layer will not become active before reaching this threshold.
+With regard to behavioural data, different effects for decision times are predicted as the number of choices increases:
+for the LCA network decisions get slower due to the mutual interaction, but for the IA network decisions will take less time because only a single accumulator needs to exceed the threshold.
+Nevertheless, given specific evidence for one network does not exclude the possibility that the other network is employed for different tasks or in different brain areas.
 Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.

### 2017-01-31 doc/paper/paper.tex
Change title.
Remove remaining todo.

@@
 
-\title{A Spiking Independent Accumulator Model for Winner-Take-All Networks
-\todo{I put 'networks', but am not sure that's the right word, but it seems some word
-needs to go there... 'computations', 'decisions'? WTA is usually an adjective}}
+\title{A Spiking Independent Accumulator Model for Winner-Take-All Computation}
 
@@
 Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$, which has a comparable effect due to the leak-free integration.
-\todo{Put in more implementation details? e.g., how the thresholding population works, and why certain design choices were made?}
 

### 2017-01-31 doc/paper/paper.tex
Fix en dash non-breaking space.
Remove E_max/trans.
It was used in only two places anyways.

@@
 To enable a form of competition, we add a second thresholding layer that  projects back to self-excite and mutually-inhibit the first layer.
-We now provide the details of each layer -- again implemented using the principles of the NEF\@.
+We now provide the details of each layer~-- again implemented using the principles of the NEF\@.
 \begin{figure}
@@
 In the context of a larger model, this can become a problem because the transient output might be prematurely interpreted as a decision.
-Thus, we define $E_{\mathrm{trans}}$ as the `highest output of a losing choice' during the whole simulation.
+Thus, we define it as the `highest output of a losing choice' during the whole simulation.
 

### 2017-01-31 doc/paper/paper.tex
Prefer time-constant.
Forgot important minus.

@@
 \end{equation}
-where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
+where $h(t) = \tau_{\mathrm{s}}^{-1}\exp(-t/\tau_{\mathrm{s}})$ is an exponentially decaying synaptic filter with time-constant $\tau_{\mathrm{s}}$, and $\ast$ is the convolution operator.
 The decoding weights are obtained by least-squares optimization of the error $E_x = \abs{x - \hat{x}}$.
@@
         Fraction of correct trials for the IA network.
-        Each plot shows data for a different combination of input magnitude $u$ and integration time constant $\tau_1$.
+        Each plot shows data for a different combination of input magnitude $u$ and integration time-constant $\tau_1$.
         Error bars denote bootstrapped 95\% confidence intervals.

### 2017-02-01 cogsci17_decide/networks.py
Rename networks in Python code.
Addresses #1.

Still needs renaming in Jupyter notebooks and data files.

@@ -2,7 +2,7 @@ import nengo
 import numpy as np
 
 
-def UsherMcClelland(d, n_neurons, dt):
+def LCA(d, n_neurons, dt):
     k = 1.
     beta = 1.
     tau_model = 0.1
@@ -35,7 +35,7 @@ def UsherMcClelland(d, n_neurons, dt):
     return net
 
 
-def DriftDiffusion(d, n_neurons, dt, share_thresholding_intercepts=False):
+def IA(d, n_neurons, dt, share_thresholding_intercepts=False):
     bar_beta = 2.  # should be >= 1 + max_input * tau2 / tau1
     tau_model1 = 0.1
     tau_model2 = 0.1

### 2017-02-01 cogsci17_decide/trial.py

@@ -7,7 +7,7 @@ import cogsci17_decide.networks
 
 class DecisionTrial(pytry.NengoTrial):
     def params(self):
-        self.param("network under test", network='UsherMcClelland')
+        self.param("network under test", network='LCA')
         self.param("# choices", d=10)
         self.param("# neurons per choice", N=200)
 

### 2017-02-01 psy-tasks/task_decision.py

@@ -5,10 +5,10 @@ from cogsci17_decide.trial import DecisionTrial
 pspace = (
     (
         Param(
-            network=['UsherMcClelland'],
+            network=['LCA'],
             scale=[1.],
             share_thresholding_intercepts=[False]) +
-        Param(network=['DriftDiffusion']) *
+        Param(network=['IA']) *
         Param(share_thresholding_intercepts=[False, True]) *
         Param(scale=[0.2, 1.])
     ) *

### 2017-02-01 psy-tasks/task_more_d.py
Commit final data files.

@@ -1,0 +1,26 @@
+from psyrun import Param
+
+from cogsci17_decide.trial import DecisionTrial
+
+pspace = (
+    (
+        Param(
+            network=['LCA'],
+            scale=[1.],
+            share_thresholding_intercepts=[False]) +
+        Param(network=['IA']) *
+        Param(share_thresholding_intercepts=[False]) *
+        Param(scale=[1.])
+    ) *
+    Param(baseline=[0.2, 0.6, 1.0]) *
+    Param(target_sep=[0.05, 0.1, 0.15, 0.2]) *
+    Param(noise=[0.0, 0.01, 0.02, 0.03, 0.04, 0.05]) *
+    Param(seed=range(50))
+)
+
+min_items = 20
+max_jobs = None
+
+
+def execute(**kwargs):
+    return DecisionTrial().run(d=20, **kwargs)

### 2017-02-01 doc/paper/paper.tex
Column balancing and discussion proofreading

@@
 \usepackage{xcolor}  % for \textcolor
+\usepackage{flushend}  % balance final column height
 
@@
 The implementation in spiking neurons, however, provides some basic biological plausibility and more readily permits comparisons with neural data.
-In particular, the LCA networks predicts firing rates proportional to the input strength, while the IA network predicts that firing rates will rise up to a threshold for neurons in the first neurons and that neurons in the second layer will not become active before reaching this threshold.
+In particular, the IA network predicts that the firing rates for neurons in the first layer will rise up to a threshold, and that neurons in the second layer will not become active or inhibit the first layer until reaching this threshold.
+In contrast, the LCA network predicts that the firing of any neurons will proportionately inhibit all other neurons that do not represent the same state.
 With regard to behavioural data, different effects for decision times are predicted as the number of choices increases:
-for the LCA network decisions get slower due to the mutual interaction, but for the IA network decisions will take less time because only a single accumulator needs to exceed the threshold.
-Nevertheless, given specific evidence for one network does not exclude the possibility that the other network is employed for different tasks or in different brain areas.
+for the LCA network decisions become slower due to the mutual interaction, but for the IA network decisions will take less time because only a single accumulator needs to exceed the threshold.
+Nevertheless, evidence for one network does not exclude the possibility that the other network is employed for different tasks or by different brain areas.
 Relatedly, it might be more plausible to distribute the representation of all state variables over a single population of neurons.
@@
 We also did not look at at the influence of the number of dimensions $D$ in detail.
-For higher $D$, we see reduced accuracy since each additional choice has a baseline chance to win due to noise.
-Nevertheless, the qualitative results are expected to stay the same.
+For higher $D$, we see reduced accuracy overall since each additional choice has a baseline chance to win due to noise.
+Nevertheless, the results that we discuss here are qualitatively similar.
 % With the specific case of only two choices ($D=2$) the decision problem becomes fundamentally easier, since the sum of losing inputs is guaranteed to be below the magnitude of the winner.
@@
 To conclude, we investigated two spiking neural networks computing a winner-take-all function based on the leaky, competing accumulator model and a novel two-layer independent accumulator model.
-While both perform the same basic tasks, they fail on it in different ways as the task becomes more difficult with increased noise or less separation among the choices.
-From a modelling perspective, this makes each network more useful in different situations.
+While both perform the same basic tasks, they fail in different ways as each task scales in difficulty via increased noise or less separation between choices.
+From a modelling perspective, this makes each network more useful for different situations.
 The LCA model is better for continuous updating of decisions, whereas the IA network is better suited for more discrete decisions in the presence of noise.
-It is left to future work to investigate whether such two distinct mechanisms can be identified from either behavioural or neurophysiological data.
+It is left to future work to investigate whether these two distinct mechanisms can be identified from either behavioural or neurophysiological data.
 

### 2017-02-01 setup.py
Update setup.py with dependencies.

@@ -2,12 +2,14 @@ from setuptools import find_packages, setup
 
 setup(
     name="cogsci17_decide",
-    version="0.1",
+    version="1.0",
     packages=find_packages(),
     install_requires=[
-        'nengo',
+        'matplotlib < 2.0',
+        'nengo >= 2.3, < 3.0',
         'numpy',
-        'matplotlib',
-        'pytry'
+        'pandas',
+        'pytry',
+        'seaborn',
     ]
 )

### 2017-02-01 cogsci17_decide/networks.py
Add labels to networks.

@@ -15,13 +15,13 @@ def LCA(d, n_neurons, dt):
     B = 1. / tau_model
     A = (-k * I - beta * inhibit) / tau_model
 
-    with nengo.Network() as net:
+    with nengo.Network(label="LCA") as net:
         net.input = nengo.Node(size_in=d)
         x = nengo.networks.EnsembleArray(
             n_neurons, d,
             eval_points=nengo.dists.Uniform(0., 1.),
             intercepts=nengo.dists.Uniform(0., 1.),
-            encoders=nengo.dists.Choice([[1.]]))
+            encoders=nengo.dists.Choice([[1.]]), label="state")
         nengo.Connection(x.output, x.input, transform=tau_actual * A + I,
                          synapse=tau_actual)
 
@@ -58,13 +58,13 @@ def IA(d, n_neurons, dt, share_thresholding_intercepts=False):
     assert n_neurons_x > 0
     threshold = 0.8
 
-    with nengo.Network() as net:
+    with nengo.Network(label="IA") as net:
         net.input = nengo.Node(size_in=d)
         x = nengo.networks.EnsembleArray(
             n_neurons_x, d,
             eval_points=nengo.dists.Uniform(0., 1.),
             intercepts=nengo.dists.Uniform(0., 1.),
-            encoders=nengo.dists.Choice([[1.]]))
+            encoders=nengo.dists.Choice([[1.]]), label="Layer 1")
         net.x = x
         nengo.Connection(x.output, x.input, transform=tau_actual * A1 + I,
                          synapse=tau_actual)
@@ -75,14 +75,15 @@ def IA(d, n_neurons, dt, share_thresholding_intercepts=False):
             synapse=tau_actual)
 
         with nengo.presets.ThresholdingEnsembles(0.):
-            thresholding = nengo.networks.EnsembleArray(n_neurons_threshold, d)
+            thresholding = nengo.networks.EnsembleArray(
+                n_neurons_threshold, d, label="Layer 2")
             if share_thresholding_intercepts:
                 for e in thresholding.ensembles:
                     e.intercepts = nengo.dists.Exponential(
                         0.15, 0., 1.).sample(n_neurons_threshold)
             net.output = thresholding.add_output('heaviside', lambda x: x > 0.)
 
-        bias = nengo.Node(1.)
+        bias = nengo.Node(1., label="Bias")
 
         nengo.Connection(x.output, thresholding.input, synapse=0.005)
         nengo.Connection(

### 2017-02-01 cogsci17_decide/trial.py

@@ -28,15 +28,16 @@ class DecisionTrial(pytry.NengoTrial):
 
             stimulus = p.baseline * np.ones(p.d)
             stimulus[1:] -= p.target_sep
-            stimulus_node = nengo.Node(stimulus)
+            stimulus_node = nengo.Node(stimulus, label="Input")
             nengo.Connection(stimulus_node, decide.input, synapse=None,
                              transform=p.scale)
 
             if p.noise > 0.:
                 noise_node = nengo.Node(nengo.processes.WhiteNoise(
-                    nengo.dists.Gaussian(.0, p.noise)), size_out=p.d)
+                    nengo.dists.Gaussian(.0, p.noise)), size_out=p.d,
+                    label="Noise")
             else:
-                noise_node = nengo.Node(np.zeros(p.d))
+                noise_node = nengo.Node(np.zeros(p.d), label="Noise")
             nengo.Connection(noise_node, decide.input, synapse=None,
                              transform=p.scale)
 

### 2017-02-01 doc/paper/paper.tex
Do not balance last column.
Fix plural in Notes.
Also fixes and undefull hbox.
Update network names in notebooks.
Closes #1.
Fix grammar in sentence.

@@
 \usepackage{xcolor}  % for \textcolor
-\usepackage{flushend}  % balance final column height
 
@@
     \centering
-    \includegraphics{figures/usher-mcclelland}\\
+    \includegraphics{figures/lca}\\
     \vspace*{.3cm}
-    \includegraphics{figures/indacc}
+    \includegraphics{figures/ia}
     \caption{
@@
 This also enables the IA network to react to small inputs.
-In addition, the IA network is easily extendible to allow dynamic control the speed of decisions, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.
+In addition, the IA network is easily extendible to allow dynamic control of the decision speed, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.
 
@@
 \section{Notes}
-Source code and supplementary analysis is available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
+Source code and supplementary analysis are available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
 %These have not been peer reviewed.

### 2017-04-17 doc/paper/paper.tex
Address some of the review comments.

@@
 
+Note that the layer 2 decoded output of a single choice shows more variance in the IA network (Fig.~\ref{fig:indacc}), but the separation of the output for different choices is more relevant in interpreting the output.
+
 \subsection{Benchmarks}
@@
 However, once a decision is made, the network provides a stable output.
+As an example, we intend to use the IA network in a free recall memory model where a clear response needs to be selected.
+A non-correct response in this case might still be a valid response in the context of this task and could be better than no response at all.
 
@@
 In the IA network, however, such transient responses may be avoided by choosing appropriate $\tau_1$ and $\vartheta$.
+It should be noted that other recurrently connected readout mechanisms with pooled inhibition have been proposed for at least the two choice case~\cite<e.g.>{lo2006} that produce outputs somewhat comparable to the IA network.
 

### 2017-04-17 doc/paper/paper.tex
Rewrite memory model example.

@@
 However, once a decision is made, the network provides a stable output.
-As an example, we intend to use the IA network in a free recall memory model where a clear response needs to be selected.
-A non-correct response in this case might still be a valid response in the context of this task and could be better than no response at all.
+As an example, we intend to use the IA network in a free recall memory model where a clear selection of successive responses needs to be made, but correctly identifying the single item remembered most strongly is not required.
 

### 2017-04-26 doc/paper/paper.tex
Further paper revisions.

@@
     \centering
-    \includegraphics{figures/lca}\\
+    \includegraphics[scale=0.9]{figures/lca}\\
     \vspace*{.3cm}
-    \includegraphics{figures/ia}
+    \includegraphics[scale=0.9]{figures/ia}
     \caption{
@@
     \centering
-    \includegraphics{figures/ia-sketch}
+    \includegraphics[scale=0.9]{figures/ia-sketch}
     \caption{
@@
     \centering
-    \includegraphics{figures/decisions}
+    \includegraphics[scale=0.9]{figures/decisions}
     \caption{
@@
     \centering
-    \includegraphics{figures/correct}
+    \includegraphics[scale=0.9]{figures/correct}
     \caption{
@@
 \begin{figure*}[t]
-    \includegraphics{figures/time1}
+    \includegraphics[scale=0.9]{figures/time1}
     \hfill
-    \includegraphics{figures/time2}
+    \includegraphics[scale=0.9]{figures/time2}
     \caption{
@@
     \centering
-    \includegraphics{figures/transient}
+    \includegraphics[scale=0.9]{figures/transient}
     \caption{
@@
 In the IA network, however, such transient responses may be avoided by choosing appropriate $\tau_1$ and $\vartheta$.
-It should be noted that other recurrently connected readout mechanisms with pooled inhibition have been proposed for at least the two choice case~\cite<e.g.>{lo2006} that produce outputs somewhat comparable to the IA network.
+It should be noted that other recurrently connected readout mechanisms have been proposed for the two choice case that produce bursting outputs somewhat comparable to the IA network~\cite{lo2006}.
+However, the evidence integration uses competition by means of pooled inhibition makes it more similar to the LCA than the IA network and the behaviour under highly noisy conditions is unknown.
 
@@
 In particular, the IA network predicts that the firing rates for neurons in the first layer will rise up to a threshold, and that neurons in the second layer will not become active or inhibit the first layer until reaching this threshold.
+Neurons in the macaque lateral intraparietal area give a similar step response~\cite{latimer2015}.
 In contrast, the LCA network predicts that the firing of any neurons will proportionately inhibit all other neurons that do not represent the same state.

### 2017-05-04 doc/paper/paper.tex
Minor updates to paper.

@@
 
-Note that the layer 2 decoded output of a single choice shows more variance in the IA network (Fig.~\ref{fig:indacc}), but the separation of the output for different choices is more relevant in interpreting the output.
+Note that the decoded output from layer 2 of the IA network has higher variance than the LCA network (Fig.~\ref{fig:indacc}), but the separation of the output for different choices is more relevant than the variance in interpreting the output.
 
@@
     \centering
-    \includegraphics[scale=0.9]{figures/decisions}
+    \includegraphics[scale=0.95]{figures/decisions}
     \caption{
@@
     \centering
-    \includegraphics[scale=0.9]{figures/correct}
+    \includegraphics[scale=0.95]{figures/correct}
     \caption{
@@
     \centering
-    \includegraphics[scale=0.9]{figures/transient}
+    \includegraphics[scale=0.92]{figures/transient}
     \caption{
@@
 However, once a decision is made, the network provides a stable output.
-As an example, we intend to use the IA network in a free recall memory model where a clear selection of successive responses needs to be made, but correctly identifying the single item remembered most strongly is not required.
+For example, we intend to use the IA network in a model of free recall to output a sequence of WTA responses.
+In this case, the model requires stable recall in the presence of noise, even if each response may not be the ``true'' winner.
 
@@
 It should be noted that other recurrently connected readout mechanisms have been proposed for the two choice case that produce bursting outputs somewhat comparable to the IA network~\cite{lo2006}.
-However, the evidence integration uses competition by means of pooled inhibition makes it more similar to the LCA than the IA network and the behaviour under highly noisy conditions is unknown.
+However, the evidence integration in the \citeA{lo2006} model uses competition via pooled inhibition, making it more similar to the LCA then the IA network.
 
@@
 In particular, the IA network predicts that the firing rates for neurons in the first layer will rise up to a threshold, and that neurons in the second layer will not become active or inhibit the first layer until reaching this threshold.
-Neurons in the macaque lateral intraparietal area give a similar step response~\cite{latimer2015}.
+Neurons in the macaque lateral intraparietal area exhibit a similar step response~\cite{latimer2015}.
 In contrast, the LCA network predicts that the firing of any neurons will proportionately inhibit all other neurons that do not represent the same state.

### 2017-07-12 doc/poster/poster.tex
Add Latex version of poster.

\documentclass[final]{beamer}

%\usepackage{microtype}

\usepackage[orientation=landscape,size=a0,scale=1.5]{beamerposter}
\usepackage{calc}
\usepackage{commath}
\usepackage[no-math]{fontspec}
\usepackage{mathspec}
\usepackage{nag}
\usepackage{siunitx}
\usepackage{tcolorbox}

\tcbuselibrary{raster}

\setmainfont{Noto Serif}
\setsansfont{Open Sans}
\usefonttheme[onlymath]{serif}
\setmathfont(Digits,Latin,Greek){Noto Serif}

\useinnertheme{circles}
\setbeamercolor{itemize item}{fg=black}
\setlength{\leftmargini}{.7\baselineskip}

\setbeamercolor{block title}{fg=black}
\setbeamerfont{block title}{series=\bfseries,size=\normalsize}

%gets rid of navigation symbols
\setbeamertemplate{navigation symbols}{}

\tcbset{
    boxsep=5mm, titlerule=0mm,
    colback=white, colframe=black, arc=0mm,
    fonttitle=\bfseries,
    coltitle=black, colbacktitle=white,
    halign title=center, halign=flush left
}

\title{A Spiking Independent Accumulator Model for\\Winner-Take-All Computation}
\author{Jan Gosmann, Aaron R. Voelker, Chris Eliasmith \{jgosmann, avoelke, celiasmith\}@uwaterloo.ca}
\institute{Centre for Theoretical Neuroscience, University of Waterloo <http://ctn.uwaterloo.ca>}

\begin{document}
\begin{frame}[t]
    \begin{columns}
        \begin{column}{129mm}
            \includegraphics[width=128mm]{People_brain}
        \end{column}
        \begin{column}{\paperwidth-339mm}
            \begin{center}
                {\huge\inserttitle\par}

                \vspace*{10mm}
                \insertauthor\par\insertinstitute%
            \end{center}
        \end{column}
        \begin{column}{190mm}
            \centering
            % FIXME higher resolution images
            \includegraphics[width=92.8mm]{uw_bow}\hfill
            \includegraphics[width=86.8mm]{CTN_logo}\\\vspace*{10mm}
            \includegraphics[width=187.7mm]{CNRG_BoW}
        \end{column}
        \begin{column}{20mm}
        \end{column}
    \end{columns}
    \vspace*{20mm}

    \begin{tcbraster}[raster columns=4, raster column skip=10mm, raster row skip=10mm, raster equal height=rows, raster force size=false]
        \begin{tcolorbox}[title=Motivation, add to width=-5cm]
            \begin{itemize}
                \item Investigate WTA mechanisms in the context of neurally plausible cognitive modelling
                \item Implement using spiking neurons
                \item Explore the effect of noisy inputs on stable decision making
                \item Allow for integration into larger scale networks
            \end{itemize}
        \end{tcolorbox}
        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=13cm]
            \begin{itemize}
                \item \emph{Representation} in spiking neurons defined by encoding
                    \begin{equation*}
                        a_i(t) = G_i\left[a_i e_i x(t) + J_i^{\mathrm{bias}} \right]
                        \text{ and decoding }
                        \hat{x}(t) = \sum_i d_i \left[(a_i * h)(t) \right]
                    \end{equation*}
                \item \emph{Transformation} by decoding weights $d_i$ minimizing $E_{f(x)} = \abs{f(x) - \hat{x}}$
                \item \emph{Dynamics} by recurrent transformation
                    \begin{equation*}
                        \frac{\partial x}{\partial t} = g(x) \quad\Rightarrow\quad f(x) = \tau_s g(x) + x
                    \end{equation*}
            \end{itemize}
        \end{tcolorbox}
        \begin{tcolorbox}[title=Benchmarks, add to width=-5cm]
            \begin{itemize}
                \item Ability to provide a clear output (single output above \num{0.15}, stable over at least \SI{1}{\second})
                \item Correctness (output corresponds to strongest input)
                \item Time required to reach a decision
                \item Transient outputs before final decision is reached
            \end{itemize}
        \end{tcolorbox}
        \begin{tcolorbox}[title=Conclusions, add to width=-3cm]
            \begin{itemize}
                \item The two WTA mechanisms are best suited for different purposes
                \item LCA network:
                    \begin{itemize}
                        \item Reacts more quickly
                        \item If stable decision is reached, it will be correct
                        \item Output can be unstable in noisy conditions
                    \end{itemize}
                    \item IA network: will eventually give a stable output, but it might not be the correct one
            \end{itemize}
        \end{tcolorbox}
        \begin{tcolorbox}[raster multicolumn=4,title={Leaky, Competing Accumulators (LCA)},halign title=left]
            \begin{minipage}[c][6in]{20cm}
                \vfill
                \vfill
                \begin{align*}
                    \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau},\\
                    x_i &\ge 0
                \end{align*}
                \vfill
                {\tiny Usher, M., \& McClelland, J.~L. (2001). The time course of perceptual choice: THe leaky, competing accumulator model. \textit{Psychological Review}, 108(3), 550--592.\par}
            \end{minipage}
            \hfill
            \raisebox{-0.5\height}{\includegraphics[scale=3]{lca-sketch}}
            \hfill
            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{lca}}
        \end{tcolorbox}
        \begin{tcolorbox}[raster multicolumn=4,title=Independent Accumulators,halign title=left]
            \begin{minipage}[c]{20cm}
                \begin{align*}
                    \bar{x}_i &:= \Theta(x_i - \vartheta),\\
                    \frac{{\partial x}_i}{\partial t} &= \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2},\\
                    \quad x_i &\ge 0
                \end{align*}
            \end{minipage}
            \hfill
            \raisebox{-0.5\height}{\includegraphics[scale=3]{ia-sketch}}
            \hfill
            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{ia}}
        \end{tcolorbox}
    \end{tcbraster}

\end{frame}

\end{document}

### 2017-07-17 doc/poster/poster.tex
Use vector graphics for logos in poster.
Increase poster font size.

@@
 
-\usepackage[orientation=landscape,size=a0,scale=1.5]{beamerposter}
+\usepackage[orientation=landscape,size=a0,scale=1.7]{beamerposter}
 \usepackage{calc}
@@
             \centering
-            % FIXME higher resolution images
-            \includegraphics[width=92.8mm]{uw_bow}\hfill
-            \includegraphics[width=86.8mm]{CTN_logo}\\\vspace*{10mm}
-            \includegraphics[width=187.7mm]{CNRG_BoW}
+            \raisebox{-0.5\height}{\includegraphics[trim=96.65 0 0 0,width=102.8mm]{UniversityOfWaterloo_logo_vert_cmyk}}\hfill
+            \raisebox{-0.5\height}{\includegraphics[width=86.8mm]{CTN_logo}}\\
+            \includegraphics[width=187.7mm]{cnrg_logo}
         \end{column}
@@
     \begin{tcbraster}[raster columns=4, raster column skip=10mm, raster row skip=10mm, raster equal height=rows, raster force size=false]
-        \begin{tcolorbox}[title=Motivation, add to width=-5cm]
+        \begin{tcolorbox}[title=Motivation, add to width=-2cm]
             \begin{itemize}
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=13cm]
+        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=5cm]
             \begin{itemize}
                 \item \emph{Representation} in spiking neurons defined by encoding
-                    \begin{equation*}
-                        a_i(t) = G_i\left[a_i e_i x(t) + J_i^{\mathrm{bias}} \right]
-                        \text{ and decoding }
-                        \hat{x}(t) = \sum_i d_i \left[(a_i * h)(t) \right]
-                    \end{equation*}
+                        $a_i(t) = G_i\left[a_i e_i x(t) + J_i^{\mathrm{bias}} \right]$
+                        and decoding
+                        $\hat{x}(t) = \sum_i d_i \left[(a_i * h)(t) \right]$
                 \item \emph{Transformation} by decoding weights $d_i$ minimizing $E_{f(x)} = \abs{f(x) - \hat{x}}$
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Benchmarks, add to width=-5cm]
+        \begin{tcolorbox}[title=Benchmarks, add to width=-3cm]
             \begin{itemize}
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Conclusions, add to width=-3cm]
+        \begin{tcolorbox}[title=Conclusions, add to width=0cm]
             \begin{itemize}
@@
             \hfill
-            \raisebox{-0.5\height}{\includegraphics[scale=3]{lca-sketch}}
+            \raisebox{-0.5\height}{\includegraphics[scale=2.9]{lca-sketch}}
             \hfill
@@
             \hfill
-            \raisebox{-0.5\height}{\includegraphics[scale=3]{ia-sketch}}
+            \raisebox{-0.5\height}{\includegraphics[scale=2.9]{ia-sketch}}
             \hfill

### 2017-07-17 doc/poster/poster.tex
Layout fixes.

@@
 \tcbuselibrary{raster}
+\tcbuselibrary{skins}
 
@@
 \tcbset{
-    boxsep=5mm, titlerule=0mm,
+    skin=enhanced,
+    boxsep=5mm, titlerule=0mm, titlerule style={white,line width=0mm},
     colback=white, colframe=black, arc=0mm,
@@
     \begin{tcbraster}[raster columns=4, raster column skip=10mm, raster row skip=10mm, raster equal height=rows, raster force size=false]
-        \begin{tcolorbox}[title=Motivation, add to width=-2cm]
+        \begin{tcolorbox}[adjusted title=Motivation, add to width=-2cm]
             \begin{itemize}
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Neural Engineering Framework, add to width=5cm]
+        \begin{tcolorbox}[adjusted title=Neural Engineering Framework, add to width=5cm]
             \begin{itemize}
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Benchmarks, add to width=-3cm]
+        \begin{tcolorbox}[adjusted title=Benchmarks, add to width=-3cm]
             \begin{itemize}
@@
         \end{tcolorbox}
-        \begin{tcolorbox}[title=Conclusions, add to width=0cm]
+        \begin{tcolorbox}[adjusted title=Conclusions, add to width=0cm]
             \begin{itemize}

### 2017-07-21 doc/poster/poster.tex
Fix overfull hbox in poster.
Add IA abbreviation to poster.
Update poster with meeting feedback.

@@
         \end{tcolorbox}
-        \begin{tcolorbox}[adjusted title=Benchmarks, add to width=-3cm]
+        \begin{tcolorbox}[adjusted title=Definitions, add to width=-3cm]
             \begin{itemize}
-                \item Ability to provide a clear output (single output above \num{0.15}, stable over at least \SI{1}{\second})
-                \item Correctness (output corresponds to strongest input)
-                \item Time required to reach a decision
-                \item Transient outputs before final decision is reached
+                \item \textbf{Clear:} single output above \num{0.15}, stable over at least  \SI{1}{\second}
+                \item \textbf{Correct:} output corresponds to strongest input
+                \item \textbf{Input magnitude:} Magnitude of target input
+                \item \textbf{Target separation:} Separation of target input from non-target inputs 
             \end{itemize}
@@
         \begin{tcolorbox}[raster multicolumn=4,title={Leaky, Competing Accumulators (LCA)},halign title=left]
-            \begin{minipage}[c][6in]{20cm}
+            \begin{minipage}[c][6in]{21.5cm}
                 \vfill
@@
             \hfill
+            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{lca-example}}
+            \hspace{1.5cm}
             \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{lca}}
         \end{tcolorbox}
-        \begin{tcolorbox}[raster multicolumn=4,title=Independent Accumulators,halign title=left]
-            \begin{minipage}[c]{20cm}
+        \begin{tcolorbox}[raster multicolumn=4,title=Independent Accumulators (IA),halign title=left]
+            \begin{minipage}[c]{21.5cm}
                 \begin{align*}
@@
             \hfill
+            \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{ia-example}}
+            \hspace{1.5cm}
             \raisebox{-0.5\height}{\includegraphics[trim=0 0 0 80]{ia}}
